### 2018-08-14 paper.tex
Initial commit

\documentclass[10pt, conference, compsocconf]{IEEEtran}

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\usepackage{nicefrac}
\usepackage{amsmath}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}
\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}

\begin{document}

\title{A multi-dimensional extension of the Lightweight Temporary Compression method}

\author{Bo Li, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca \vspace*{-0.5cm}}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

LTC is among the stream compression method that provides the highest 
compression rate for the lowest resource (CPU, RAM) consumption. As 
such, it makes it a very good candidate for the compression of data 
streams acquired in embedded, low-power systems such as connected 
objects, systems on module (SoMs), etc The type of data acquired on 
such systems, however, is often multi-dimensional. For instance 
accelerometers and gyroscopes usually measure variables along 3 
directions, these variables being distinct but related through the 
actual movement of the sensor. In this paper, we investigate the 
extension of LTC to higher dimensions. First, we express the algorithm 
in an arbitrary vectorial space of dimension $n$. Second, we 
instantiate it for the Euclidean and xxx distances, in spaces of 
dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC 
to the 1-dimensional version, on gyroscopic data acquired on a SoM 
device.

\section{Lightweight Temporal Compression}

Summarize existing paper.

\section{Extension to dimension $n$}

\section{Results}

\subsection{Data sets}

\subsection{Compression ratios}

\subsection{Errors}

\subsection{Memory consumption}

\section{Conclusion}

\section*{Acknowledgement}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,biblio.bib}

\end{document}

### 2018-08-30 paper.tex
Added comment
write algorithm LTC-MD

@@
 \usepackage{algorithmic}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 \usepackage{amsfonts} % for R symbol (the set of real numbers)
@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
 
+Lightweight temporal compression (LTC) is one of the linear estimation method to compress data.
+It is The first-order interpolator with two degrees of freedom(FOI-2DF) which is mentioned in ~\cite{jalaleddine1990ecg}.
+Most of linear estimation method need a predefined parameter which is the error margin (let's call $\epsilon$) in order to guarantee the difference between estimation and original data within a scope.
+
+\todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be writen}
+
 \section{Extension to dimension $n$}
 
+In practice, It's needed to transmit raw data which has multi-parameters to clients e.g.
+Accelerometer, Euler Angle and Magnetometer etc.
+LTC not work well when we transmit multi-parameters data, cause if we just implement LTC for each parameter, the difference between estimation and origin could exceed error margin which was set in advance.
+For instance, there is a data $(x, y)$ with two parameters, and using LTC for both parameter respectively.
+According to LTC method $\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the difference between estimation and original data $(x,y)$ is which is bigger than error margin predefined.
+In this case, we design a new algorithm, which is multi-parameter version of LTC, and it also work with any type of distance.
+In standard LTC method, it checks if there is overlapping part between new sector area and recorded range.
+However, in our multidimensional method, we will map every data point into same time-stamp e.g.
+$t_0$.
+It is convenient for us to calculate distance between them and check if overlapping range exists.
+we provide Multidimensional-LTC with Euclidean and Manhattan distance in below.
+\subsection{Multidimensional LTC with Manhattan distance}
+In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively.
+But we did some changes in our method.
+Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}.
+We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$.
+cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance.
+checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
+
+\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}
+
+At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
+\begin{enumerate}
+  \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
+Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
+  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
+  \item Goto 2.
+  \item output \textit{z} data point.
+  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
+  \item Goto 2.
+  \item After all, output \textit{z} data point and center of bounding box respectively.
+\end{enumerate}
+
+\subsection{Multidimensional LTC with Euclidean distance} 
+In Euclidean distance version, we also map the coming data into same time-stamp.
+The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
+In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
+In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version.
+After that, we extend the method for n-dimension.
+\begin{itemize}
+\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk.
+After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data.
+Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
+\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis.
+So In 3-dimension whether \textit{n} balls intersect need to be check.
+\end{itemize}
+
+At first, let us solve the \textit{n} disks intersect.
+We use a algorithm which is based on plane sweep and dichotomy.
+Assume a disk include center$(x,y)$ and radius $r$.
+The pseudo-code in Algorithm 1.
+\begin{algorithm}
+    \caption{whether disks intersect}
+    \begin{flushleft}
+        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
+        \textbf{Output:} $true|false$  is there a intersection\\ 
+        \textbf{function} isIntersect$(l, d, p)$
+    \end{flushleft}
+    \begin{algorithmic}[1]
+        \STATE $tmp_list \gets null$
+        \STATE $max\_x\gets d.x+d.r$
+        \STATE $min\_x\gets d.x-d.r$
+
+        \FORALL{$old\_disk$ \textbf{in} $l$}
+            \IF{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
+                \STATE \textbf{return} false
+            \ELSIF{$d \cap old\_disk \neq d$}
+                \STATE {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
+                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
+                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
+            \ENDIF
+        \ENDFOR
+        \STATE $\textbf{add } d \textbf{ into } tmp\_list$
+        \IF{$max\_x < min\_x$}
+            \STATE \textbf{return} false
+        \ENDIF
+        \WHILE{$min\_x \leqslant max\_x$}
+            \STATE $mid \gets (min\_x + max\_x)/2$
+            \STATE $max\_y \gets +\infty$
+            \STATE $min\_y \gets -\infty$
+            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
+                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
+                \IF{$P_1.y < max\_y$}
+                    \STATE $max\_y \gets p_1.y$
+                    \STATE $max\_index \gets i$
+                \ENDIF
+                \IF{$P_2.y > min\_y$}
+                    \STATE $min\_y \gets p_2.y$
+                    \STATE $min\_index \gets i$
+                \ENDIF
+            \ENDFOR
+            \IF{$max\_y >= min\_y$}
+                \STATE $p.x \gets mid$
+                \STATE $p.y \gets (max\_y+min\_y)/2$
+                \STATE $l \gets tmp\_list$
+                \STATE \textbf{return} true
+            \ENDIF
+            \STATE {Assume $P_d$ is the intersection between line of 
+            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
+            , and their common chord}
+            \IF{$P_d.x < mid$}
+                \STATE $max\_y \gets mid-1$
+            \ELSIF{$P_d.x > mid$}
+                \STATE $min\_y \gets mid+1$
+            \ENDIF
+        \ENDWHILE
+        \RETURN false
+    \end{algorithmic}
+\end{algorithm}
+
+The main idea of the algorithm is, remove the bigger disk who contains mapped coming disk.
+It maybe increase Computational efficiency in the rest of algorithm, cause mapped coming disk is the smallest one than all in list of disks.
+Then we make a bounding range for x-axis and select a x-value $mid$ by using dichotomy method in order to calculate if a point $(y, mid)$ is included all disks.
+The complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
+
+For 3-dimension, assume data point like $(x, y, z)$ also need time-stamp t, we can also use above method by selecting $x$ and $y$ with dichotomy method and then check if there are points $(mid\_x, mid\_y, z)$ included by all balls.
+It needs $O(\log^2\epsilon)$ to determine $mid\_x, mid\_y$, and $O(n)$ to traverse all balls in list and calculate $z$.
+So 3-dimensional method need $O(n \log^2\epsilon)$ totally.
+If we extend this idea for n-dimension, suppose that the coming data is $(x_1,x_2,...,x_n)$ and the mapped data is a object with center $(d_1,d_2,...d_n)$ and radius $r$.
+The pseudo-code would show like Algorithm 2.
+
+\begin{algorithm}
+    \caption{whether intersect  for n dimension}
+    \begin{flushleft}
+        \textbf{Input:} $l$ - list oebjct, $o$ - object of mapped coming data, $p$ - point will be base point\\
+        \textbf{Output:} $true|false$  is there a intersection\\
+        \textbf{function} isIntersect$(l, o, p)$
+    \end{flushleft}
+    \begin{algorithmic}[1]
+        \STATE $tmp_list \gets null$
+        \STATE $max \gets o.d\_n+o.r$
+        \STATE $min \gets o.d\_n-o.r$
+
+        \FORALL{$old\_obj$ \textbf{in} $l$}
+            \IF{$o \cap old\_obj = \emptyset$} 
+                \STATE \textbf{return} false
+            \ELSIF{$o \cap old\_obj \neq o$}
+                \STATE {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
+                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
+                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
+            \ENDIF
+        \ENDFOR
+        \STATE $\textbf{add } o \textbf{ into } tmp\_list$
+        \IF{$max < min$}
+            \STATE \textbf{return} false
+        \ENDIF
+        $p\_cp \gets p$
+        \IF{Recursive$(min, max, n, p\_cp)$}
+            \STATE $p \gets p\_cp$
+            \STATE \textbf{return} true
+        \ELSE
+            \STATE \textbf{return} false
+        \ENDIF
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+    \begin{flushleft}
+        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
+    \end{flushleft}
+    \begin{algorithmic}[1]
+        \WHILE{$left \leqslant right$}
+            \STATE $mid \gets (left + right)/2$
+            \STATE $max \gets +\infty$
+            \STATE $min \gets -\infty$
+            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
+                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
+                \IF{$P_1.d_{j-1} < max$}
+                    \STATE $max \gets p_1.d_{j-1}$
+                    \STATE $max\_index \gets i$
+                \ENDIF
+                \IF{$P_2.d_{j-1} > min$}
+                    \STATE $min \gets p_2.d_{j-1}$
+                    \STATE $min\_index \gets i$
+                \ENDIF
+            \ENDFOR
+            \IF{$max >= min$}
+                \STATE $p.d_j \gets mid$
+                \IF{Recursive$(min, max, j-1, p)$}
+                    \STATE \textbf{return} true
+                \ENDIF
+            \ENDIF
+            \STATE Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
+            \IF{$P_d.d_j < mid$}
+                \STATE $right \gets mid-1$
+            \ELSIF{$P_d.d_j > mid$}
+                \STATE $left \gets mid+1$
+            \ENDIF
+
+        \ENDWHILE
+        \RETURN false
+    \end{algorithmic}
+\end{algorithm}
+
 \section{Results}
+\todo{ result table ?}
+\subsection{Data sets}
+\todo{ my data set}
 
-\subsection{Data sets}
+The tranform rate of Neblina is 50Hz.
+\\
+5-times bicep curl from Neblina. It includes 613 data which produced in 12.28 seconds. 
+\\
+Mohamad Lateral bicep data which include 41428, produced in proximate 14 minutes.
 

### 2018-09-28 paper.tex
Updates in method description

@@
 \usepackage{amssymb}
+\usepackage{stmaryrd}
+\usepackage{amsthm}
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
 }
+\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
 
@@
 
+In practice, It's needed to transmit raw data which has 
+multi-parameters to clients e.g. Accelerometer, Euler Angle and 
+Magnetometer etc. LTC not work well when we transmit multi-parameters 
+data, cause if we just implement LTC for each parameter, the difference 
+between estimation and origin could exceed error margin which was set 
+in advance. For instance, there is a data $(x, y)$ with two parameters, 
+and using LTC for both parameter respectively. According to LTC method 
+$\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the 
+estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the 
+difference between estimation and original data $(x,y)$ is which is 
+bigger than error margin predefined. In this case, we design a new 
+algorithm, which is multi-parameter version of LTC, and it also work 
+with any type of distance. In standard LTC method, it checks if there 
+is overlapping part between new sector area and recorded range. 
+However, in our multidimensional method, we will map every data point 
+into same time-stamp e.g. $t_0$. It is convenient for us to calculate 
+distance between them and check if overlapping range exists. we provide 
+Multidimensional-LTC with Euclidean and Manhattan distance in below.
+
 \section{Lightweight Temporal Compression}
@@
 
-Lightweight temporal compression (LTC) is one of the linear estimation method to compress data.
-It is The first-order interpolator with two degrees of freedom(FOI-2DF) which is mentioned in ~\cite{jalaleddine1990ecg}.
-Most of linear estimation method need a predefined parameter which is the error margin (let's call $\epsilon$) in order to guarantee the difference between estimation and original data within a scope.
+Lightweight temporal compression (LTC) is one of the linear estimation 
+method to compress data. It is The first-order interpolator with two 
+degrees of freedom(FOI-2DF) which is mentioned in 
+~\cite{jalaleddine1990ecg}.  Most of linear estimation method need a 
+predefined parameter which is the error margin (let's call $\epsilon$) 
+in order to guarantee the difference between estimation and original 
+data within a scope.
 
@@
 
-In practice, It's needed to transmit raw data which has multi-parameters to clients e.g.
-Accelerometer, Euler Angle and Magnetometer etc.
-LTC not work well when we transmit multi-parameters data, cause if we just implement LTC for each parameter, the difference between estimation and origin could exceed error margin which was set in advance.
-For instance, there is a data $(x, y)$ with two parameters, and using LTC for both parameter respectively.
-According to LTC method $\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the difference between estimation and original data $(x,y)$ is which is bigger than error margin predefined.
-In this case, we design a new algorithm, which is multi-parameter version of LTC, and it also work with any type of distance.
-In standard LTC method, it checks if there is overlapping part between new sector area and recorded range.
-However, in our multidimensional method, we will map every data point into same time-stamp e.g.
-$t_0$.
-It is convenient for us to calculate distance between them and check if overlapping range exists.
-we provide Multidimensional-LTC with Euclidean and Manhattan distance in below.
+\subsection{General formulation}
+
+In this section we provide a distance-independent formulation of LTC in 
+dimension $n$. The formulation of LTC in~\cite{ltc} relies on the intersection
+of \emph{convex cones} in dimension $n+1$.
+
+When $n$ is higher than 1, the intersection of convex cones unwieldy to 
+formalize. Instead, we formulate LTC as an intersection test 
+between $m$ \emph{balls} of dimension 
+$n$. We formulate LTC recursively, as follows.
+
+Let $x_0 \in \mathbb{R}^n$ be the last data point transmitted by the 
+algorithm. For convenience, all the subsequent data points will be 
+expressed in the orthogonal space with origin $x_0$. Without loss of 
+generality, we assume that the data points are sampled uniformly with a 
+sampling period of 1 time unit. Let k be the number of data points 
+following $x_0$ that have been compressed.
+
+The intersection of convex cones in dimension $n+1$ can be written as follows:
+\ldots
+
+Which is equivalent to the following formulation in $\mathbb{R}^n$:
+\begin{eqnarray*}
+&& \exists \textbf{u} \in \mathbb{R}^{n} \  s.t. \  \forall i \in \llbracket 1, k \rrbracket, \quad
+\norm{i\textbf{u} - \textbf{x}_i} \leq \epsilon\\
+\Leftrightarrow && \exists \textbf{u} \in \mathbb{R}^{n} \  s.t. \  \forall i \in \llbracket 1, k \rrbracket, \quad
+\norm{\textbf{u} - \frac{1}{i}\textbf{x}_i} \leq \frac{\epsilon}{i} \\
+\Leftrightarrow && \bigcap_{i=1}^{k} {\mathcal{B}}_i \neq \O,
+\end{eqnarray*}
+where $\mathcal{B}_i 
+\subset \mathbb{R}^n$ is the ball of center $\frac{1}{i}\textbf{x}_i$ 
+and radius $\frac{\epsilon}{i}$.
+
+\subsection{Effect of the norm}
+
+It should be noted that the norm has a critical impact on the 
+compression error and ratio. For instance, using the infinity instead 
+of the Euclidean norm increases the compression error by a factor of 
+$\sqrt{n}$ in dimension $n$, and increases the compression ratio by xxx.
+
+%~ Point $k+1$ will be compressed if and only if:
+%~ \begin{eqnarray*}
+%~ && \bigcap_{i=1}^{k+1} {\mathcal{B}}_i \neq \O \\
+%~ \Leftrightarrow && {\mathcal{B}}_{k+1} \cap \bigcap_{i=1}^{k} {\mathcal{B}}_i \neq \O
+%~ \end{eqnarray*}
+
+\section{Implementation}
+Our code is available at ... (make a clean release!)
+
 \subsection{Multidimensional LTC with Manhattan distance}
@@
 checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
-
 \note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}

### 2018-09-30 paper.tex

--- 2018-08-30 paper.tex
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+%\usepackage{algpseudocode}
+
 \usepackage{amsfonts} % for R symbol (the set of real numbers)
@@
 \todo{ result table ?}
+\subsection{Experiment 1: Pilot tests on Computer}
+\begin{itemize}
+    \item Data set: 5-times bicep curl which includes 613 data; 
+                    Mohammad Lateral bicep curl which include 41428 data; 
+                    All data is collected from Neblina, with 50Hz sampling of Sensors.
+    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
+    \item Result: Result shows in table.
+    \item Conclution: 
+\end{itemize}
+
+\subsection{Experiment 1: energy reduction on the Neblina}
+\begin{itemize}
+    \item Data set: 5-times bicep curl which includes 613 data; 
+                    Mohammad Lateral bicep curl which include 41428 data; 
+                    All data is collected from Neblina, with 50Hz sampling of Sensors.
+    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
+    \item Result: Result shows in table.
+    \item Conclution: 
+\end{itemize}
+
+\section{Implementation}
+Our code is available at ... (make a clean release!)
+
+\subsection{Multidimensional LTC with Manhattan distance}
+In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively.
+But we did some changes in our method.
+Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}.
+We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$.
+cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance.
+checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
+\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}
+
+At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
+\begin{enumerate}
+  \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
+Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
+  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
+  \item Goto 2.
+  \item output \textit{z} data point.
+  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
+  \item Goto 2.
+  \item After all, output \textit{z} data point and center of bounding box respectively.
+\end{enumerate}
+
+\subsection{Multidimensional LTC with Euclidean distance} 
+In Euclidean distance version, we also map the coming data into same time-stamp.
+The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
+In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
+In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version.
+After that, we extend the method for n-dimension.
+\begin{itemize}
+\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk.
+After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data.
+Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
+\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis.
+So In 3-dimension whether \textit{n} balls intersect need to be check.
+\end{itemize}
+
+At first, let us solve the \textit{n} disks intersect.
+We use a algorithm which is based on plane sweep and dichotomy.
+Assume a disk include center$(x,y)$ and radius $r$.
+The pseudo-code in Algorithm 1.
+\begin{algorithm}
+    \caption{whether disks intersect}
+    \begin{flushleft}
+        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
+        \textbf{Output:} $true|false$  is there a intersection\\ 
+        \textbf{function} isIntersect$(l, d, p)$
+    \end{flushleft}
+    \begin{algorithmic}[1]
+        \STATE $tmp_list \gets null$
+        \STATE $max\_x\gets d.x+d.r$
+        \STATE $min\_x\gets d.x-d.r$
+
+        \FORALL{$old\_disk$ \textbf{in} $l$}
+            \IF{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
+                \STATE \textbf{return} false
+            \ELSIF{$d \cap old\_disk \neq d$}
+                \STATE {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
+                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
+                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
+            \ENDIF
+        \ENDFOR
+        \STATE $\textbf{add } d \textbf{ into } tmp\_list$
+        \IF{$max\_x < min\_x$}
+            \STATE \textbf{return} false
+        \ENDIF
+        \WHILE{$min\_x \leqslant max\_x$}
+            \STATE $mid \gets (min\_x + max\_x)/2$
+            \STATE $max\_y \gets +\infty$
+            \STATE $min\_y \gets -\infty$
+            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
+                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
+                \IF{$P_1.y < max\_y$}
+                    \STATE $max\_y \gets p_1.y$
+                    \STATE $max\_index \gets i$
+                \ENDIF
+                \IF{$P_2.y > min\_y$}
+                    \STATE $min\_y \gets p_2.y$
+                    \STATE $min\_index \gets i$
+                \ENDIF
+            \ENDFOR
+            \IF{$max\_y >= min\_y$}
+                \STATE $p.x \gets mid$
+                \STATE $p.y \gets (max\_y+min\_y)/2$
+                \STATE $l \gets tmp\_list$
+                \STATE \textbf{return} true
+            \ENDIF
+            \STATE {Assume $P_d$ is the intersection between line of 
+            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
+            , and their common chord}
+            \IF{$P_d.x < mid$}
+                \STATE $max\_y \gets mid-1$
+            \ELSIF{$P_d.x > mid$}
+                \STATE $min\_y \gets mid+1$
+            \ENDIF
+        \ENDWHILE
+        \RETURN false
+    \end{algorithmic}
+\end{algorithm}
+
+The main idea of the algorithm is, remove the bigger disk who contains mapped coming disk.
+It maybe increase Computational efficiency in the rest of algorithm, cause mapped coming disk is the smallest one than all in list of disks.
+Then we make a bounding range for x-axis and select a x-value $mid$ by using dichotomy method in order to calculate if a point $(y, mid)$ is included all disks.
+The complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
+
+For 3-dimension, assume data point like $(x, y, z)$ also need time-stamp t, we can also use above method by selecting $x$ and $y$ with dichotomy method and then check if there are points $(mid\_x, mid\_y, z)$ included by all balls.
+It needs $O(\log^2\epsilon)$ to determine $mid\_x, mid\_y$, and $O(n)$ to traverse all balls in list and calculate $z$.
+So 3-dimensional method need $O(n \log^2\epsilon)$ totally.
+If we extend this idea for n-dimension, suppose that the coming data is $(x_1,x_2,...,x_n)$ and the mapped data is a object with center $(d_1,d_2,...d_n)$ and radius $r$.
+The pseudo-code would show like Algorithm 2.
+
+\begin{algorithm}
+    \caption{whether intersect  for n dimension}
+    \begin{flushleft}
+        \textbf{Input:} $l$ - list oebjct, $o$ - object of mapped coming data, $p$ - point will be base point\\
+        \textbf{Output:} $true|false$  is there a intersection\\
+        \textbf{function} isIntersect$(l, o, p)$
+    \end{flushleft}
+    \begin{algorithmic}[1]
+        \STATE $tmp_list \gets null$
+        \STATE $max \gets o.d\_n+o.r$
+        \STATE $min \gets o.d\_n-o.r$
+
+        \FORALL{$old\_obj$ \textbf{in} $l$}
+            \IF{$o \cap old\_obj = \emptyset$} 
+                \STATE \textbf{return} false
+            \ELSIF{$o \cap old\_obj \neq o$}
+                \STATE {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
+                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
+                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
+            \ENDIF
+        \ENDFOR
+        \STATE $\textbf{add } o \textbf{ into } tmp\_list$
+        \IF{$max < min$}
+            \STATE \textbf{return} false
+        \ENDIF
+        $p\_cp \gets p$
+        \IF{Recursive$(min, max, n, p\_cp)$}
+            \STATE $p \gets p\_cp$
+            \STATE \textbf{return} true
+        \ELSE
+            \STATE \textbf{return} false
+        \ENDIF
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+    \begin{flushleft}
+        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
+    \end{flushleft}
+    \begin{algorithmic}[1]
+        \WHILE{$left \leqslant right$}
+            \STATE $mid \gets (left + right)/2$
+            \STATE $max \gets +\infty$
+            \STATE $min \gets -\infty$
+            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
+                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
+                \IF{$P_1.d_{j-1} < max$}
+                    \STATE $max \gets p_1.d_{j-1}$
+                    \STATE $max\_index \gets i$
+                \ENDIF
+                \IF{$P_2.d_{j-1} > min$}
+                    \STATE $min \gets p_2.d_{j-1}$
+                    \STATE $min\_index \gets i$
+                \ENDIF
+            \ENDFOR
+            \IF{$max >= min$}
+                \STATE $p.d_j \gets mid$
+                \IF{Recursive$(min, max, j-1, p)$}
+                    \STATE \textbf{return} true
+                \ENDIF
+            \ENDIF
+            \STATE Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
+            \IF{$P_d.d_j < mid$}
+                \STATE $right \gets mid-1$
+            \ELSIF{$P_d.d_j > mid$}
+                \STATE $left \gets mid+1$
+            \ENDIF
+
+        \ENDWHILE
+        \RETURN false
+    \end{algorithmic}
+\end{algorithm}
+
+\section{Results}
+\todo{ result table ?}
 \subsection{Data sets}
 \todo{ my data set}
+>>>>>>> f097356e5357084561a03d31cfda480c342f78a7
 
@@
 \section*{Acknowledgement}
+\begin{table}[]
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    \multicolumn{9}{|l|}{Dimension 2}                                                                                                                         \\ \hline
+    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
+    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
+    Epsilon                & 100          & 100/sqrt(2)     & 100         & 100/sqrt(2)     & 100        & 100/sqrt(2)       & 100        & 100/sqrt(2)       \\ \hline
+    Max Error              & 127.63       & 94.46           & 99.63       & =               & =          & =                 & =          & =                 \\ \hline
+    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & =               & =          & =                 & =          & =                 \\ \hline
+    Max memory Usage(heap) & 80B          & 80B             & 648B        & =               & =          & =                 & =          & =                 \\ \hline
+    processing time Usage  & 0.005        & 0.005           & 0.005       & =               & =          & =                 & =          & =                 \\ \hline
+    \end{tabular}
+\end{table}
+
+\begin{table}[]
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    \multicolumn{9}{|l|}{Dimension 3}                                                                                                                         \\ \hline
+    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
+    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
+    Epsilon                & 100          & 100/sqrt(3)     & 100         & 100/sqrt(3)     & 100        & 100/sqrt(3)       & 100        & 100/sqrt(3)       \\ \hline
+    Max Error              & 127.63       & 94.46           & 99.63       & =               & =          & =                 & =          & =                 \\ \hline
+    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & =               & =          & =                 & =          & =                 \\ \hline
+    Max memory Usage(heap) & 80B          & 80B             & 648B        & =               & =          & =                 & =          & =                 \\ \hline
+    processing time Usage  & 0.005        & 0.005           & 0.005       & =               & =          & =                 & =          & =                 \\ \hline
+    \end{tabular}
+\end{table}
 

### 2018-10-01 paper.tex
fix tex
fill tables for result

--- 2018-08-30 paper.tex
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+%\usepackage{algpseudocode}
 \usepackage{amsfonts} % for R symbol (the set of real numbers)
@@
 \todo{ result table ?}
-\subsection{Data sets}
-\todo{ my data set}
+\subsection{Experiment 1: Pilot tests on Computer}
+\begin{itemize}
+    \item Data set: 5-times bicep curl which includes 613 data; 
+                    Mohammad Lateral bicep curl which include 41428 data; 
+                    All data is collected from Neblina, with 50Hz sampling of Sensors.
+    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
+    \item Result: Result shows in table.
+    \item Conclution: 
+\end{itemize}
+
+\subsection{Experiment 1: energy reduction on the Neblina}
+\begin{itemize}
+    \item Data set: 5-times bicep curl which includes 613 data; 
+                    Mohammad Lateral bicep curl which include 41428 data; 
+                    All data is collected from Neblina, with 50Hz sampling of Sensors.
+    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
+    \item Result: Result shows in table.
+    \item Conclution: 
+\end{itemize}
 
@@
 \section*{Acknowledgement}
+\begin{table}[]
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    \multicolumn{9}{|l|}{Dimension 2}                                                                                                                         \\ \hline
+    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
+    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
+    Epsilon                & 100          & 100/sqrt(2)     & 100         & 100/sqrt(2)     & 100        & 100/sqrt(2)       & 100        & 100/sqrt(2)       \\ \hline
+    Max Error              & 127.63       & 94.46           & 99.63       & 70.47           & 140.70     & 99.73             & 99.99      & 70.71             \\ \hline
+    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%         & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ \hline
+    Max memory Usage(peak) & 80B          & 80B             & 432B        & 240B            & 80B        & 80B               & 2.1KB      & 1.3KB             \\ \hline
+    processing time Usage  & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms         & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
+    \end{tabular}
+\end{table}
+
+\begin{table}[]
+    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+    \hline
+    \multicolumn{9}{|l|}{Dimension 3}                                                                                                                         \\ \hline
+    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
+    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
+    Epsilon                & 100          & 100/sqrt(3)     & 100         & 100/sqrt(3)     & 100        & 100/sqrt(3)       & 100        & 100/sqrt(3)       \\ \hline
+    Max Error              & 141.66       & 85.40           & 99.94       & 56.89           & 168.95     & 97.01             & 99.99      & 57.73             \\ \hline
+    Compression Radio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%          & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\ \hline
+    Max memory Usage(peak) & 112B         & 112B            & 384B        & 256B            & 112B       & 112B              & 4.9KB      & 3.0KB             \\ \hline
+    processing time Usage  & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms         & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
+    \end{tabular}
+\end{table}
 

### 2018-10-01 paper.tex
add pc result

--- 2018-09-30 paper.tex
@@
 %\usepackage{algpseudocode}
-
 \usepackage{amsfonts} % for R symbol (the set of real numbers)
@@
 
-\todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be writen}
+\todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be written}
 
@@
     \begin{flushleft}
-        \textbf{Input:} $l$ - list oebjct, $o$ - object of mapped coming data, $p$ - point will be base point\\
+        \textbf{Input:} $l$ - list object, $o$ - object of mapped coming data, $p$ - point will be base point\\
         \textbf{Output:} $true|false$  is there a intersection\\
@@
                     All data is collected from Neblina, with 50Hz sampling of Sensors.
+                    Using Valgrind massif measure memory usage. And using 'gettimeofday()' function in 'sys/time.h' for measure processing time usage.
     \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
     \item Result: Result shows in table.
-    \item Conclution: 
+    \item Conclusion: From the table, The LTC-Manhattan has higher compression radio.
+But LTC-Euclidean make sure the Max Error between reconstructed data and original data under EPSILON.Compression ratios would decrease with changing EPSILON smaller.
 \end{itemize}
@@
 \begin{itemize}
-    \item Data set: 5-times bicep curl which includes 613 data; 
-                    Mohammad Lateral bicep curl which include 41428 data; 
-                    All data is collected from Neblina, with 50Hz sampling of Sensors.
-    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
-    \item Result: Result shows in table.
-    \item Conclution: 
+    \item Data set: 
+    \item Experiment Condition: 
+    \item Result: 
+    \item Conclusion: 
 \end{itemize}
 
-\section{Implementation}
-Our code is available at ... (make a clean release!)
-
-\subsection{Multidimensional LTC with Manhattan distance}
-In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively.
-But we did some changes in our method.
-Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}.
-We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$.
-cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance.
-checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
-\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}
-
-At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
-\begin{enumerate}
-  \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
-Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
-  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
-  \item Goto 2.
-  \item output \textit{z} data point.
-  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
-  \item Goto 2.
-  \item After all, output \textit{z} data point and center of bounding box respectively.
-\end{enumerate}
-
-\subsection{Multidimensional LTC with Euclidean distance} 
-In Euclidean distance version, we also map the coming data into same time-stamp.
-The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
-In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
-In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version.
-After that, we extend the method for n-dimension.
-\begin{itemize}
-\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk.
-After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data.
-Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
-\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis.
-So In 3-dimension whether \textit{n} balls intersect need to be check.
-\end{itemize}
-
-At first, let us solve the \textit{n} disks intersect.
-We use a algorithm which is based on plane sweep and dichotomy.
-Assume a disk include center$(x,y)$ and radius $r$.
-The pseudo-code in Algorithm 1.
-\begin{algorithm}
-    \caption{whether disks intersect}
-    \begin{flushleft}
-        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
-        \textbf{Output:} $true|false$  is there a intersection\\ 
-        \textbf{function} isIntersect$(l, d, p)$
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \STATE $tmp_list \gets null$
-        \STATE $max\_x\gets d.x+d.r$
-        \STATE $min\_x\gets d.x-d.r$
-
-        \FORALL{$old\_disk$ \textbf{in} $l$}
-            \IF{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
-                \STATE \textbf{return} false
-            \ELSIF{$d \cap old\_disk \neq d$}
-                \STATE {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
-                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
-                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
-            \ENDIF
-        \ENDFOR
-        \STATE $\textbf{add } d \textbf{ into } tmp\_list$
-        \IF{$max\_x < min\_x$}
-            \STATE \textbf{return} false
-        \ENDIF
-        \WHILE{$min\_x \leqslant max\_x$}
-            \STATE $mid \gets (min\_x + max\_x)/2$
-            \STATE $max\_y \gets +\infty$
-            \STATE $min\_y \gets -\infty$
-            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
-                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
-                \IF{$P_1.y < max\_y$}
-                    \STATE $max\_y \gets p_1.y$
-                    \STATE $max\_index \gets i$
-                \ENDIF
-                \IF{$P_2.y > min\_y$}
-                    \STATE $min\_y \gets p_2.y$
-                    \STATE $min\_index \gets i$
-                \ENDIF
-            \ENDFOR
-            \IF{$max\_y >= min\_y$}
-                \STATE $p.x \gets mid$
-                \STATE $p.y \gets (max\_y+min\_y)/2$
-                \STATE $l \gets tmp\_list$
-                \STATE \textbf{return} true
-            \ENDIF
-            \STATE {Assume $P_d$ is the intersection between line of 
-            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
-            , and their common chord}
-            \IF{$P_d.x < mid$}
-                \STATE $max\_y \gets mid-1$
-            \ELSIF{$P_d.x > mid$}
-                \STATE $min\_y \gets mid+1$
-            \ENDIF
-        \ENDWHILE
-        \RETURN false
-    \end{algorithmic}
-\end{algorithm}
-
-The main idea of the algorithm is, remove the bigger disk who contains mapped coming disk.
-It maybe increase Computational efficiency in the rest of algorithm, cause mapped coming disk is the smallest one than all in list of disks.
-Then we make a bounding range for x-axis and select a x-value $mid$ by using dichotomy method in order to calculate if a point $(y, mid)$ is included all disks.
-The complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
-
-For 3-dimension, assume data point like $(x, y, z)$ also need time-stamp t, we can also use above method by selecting $x$ and $y$ with dichotomy method and then check if there are points $(mid\_x, mid\_y, z)$ included by all balls.
-It needs $O(\log^2\epsilon)$ to determine $mid\_x, mid\_y$, and $O(n)$ to traverse all balls in list and calculate $z$.
-So 3-dimensional method need $O(n \log^2\epsilon)$ totally.
-If we extend this idea for n-dimension, suppose that the coming data is $(x_1,x_2,...,x_n)$ and the mapped data is a object with center $(d_1,d_2,...d_n)$ and radius $r$.
-The pseudo-code would show like Algorithm 2.
-
-\begin{algorithm}
-    \caption{whether intersect  for n dimension}
-    \begin{flushleft}
-        \textbf{Input:} $l$ - list oebjct, $o$ - object of mapped coming data, $p$ - point will be base point\\
-        \textbf{Output:} $true|false$  is there a intersection\\
-        \textbf{function} isIntersect$(l, o, p)$
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \STATE $tmp_list \gets null$
-        \STATE $max \gets o.d\_n+o.r$
-        \STATE $min \gets o.d\_n-o.r$
-
-        \FORALL{$old\_obj$ \textbf{in} $l$}
-            \IF{$o \cap old\_obj = \emptyset$} 
-                \STATE \textbf{return} false
-            \ELSIF{$o \cap old\_obj \neq o$}
-                \STATE {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
-                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
-                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
-            \ENDIF
-        \ENDFOR
-        \STATE $\textbf{add } o \textbf{ into } tmp\_list$
-        \IF{$max < min$}
-            \STATE \textbf{return} false
-        \ENDIF
-        $p\_cp \gets p$
-        \IF{Recursive$(min, max, n, p\_cp)$}
-            \STATE $p \gets p\_cp$
-            \STATE \textbf{return} true
-        \ELSE
-            \STATE \textbf{return} false
-        \ENDIF
-    \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-    \begin{flushleft}
-        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \WHILE{$left \leqslant right$}
-            \STATE $mid \gets (left + right)/2$
-            \STATE $max \gets +\infty$
-            \STATE $min \gets -\infty$
-            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
-                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
-                \IF{$P_1.d_{j-1} < max$}
-                    \STATE $max \gets p_1.d_{j-1}$
-                    \STATE $max\_index \gets i$
-                \ENDIF
-                \IF{$P_2.d_{j-1} > min$}
-                    \STATE $min \gets p_2.d_{j-1}$
-                    \STATE $min\_index \gets i$
-                \ENDIF
-            \ENDFOR
-            \IF{$max >= min$}
-                \STATE $p.d_j \gets mid$
-                \IF{Recursive$(min, max, j-1, p)$}
-                    \STATE \textbf{return} true
-                \ENDIF
-            \ENDIF
-            \STATE Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
-            \IF{$P_d.d_j < mid$}
-                \STATE $right \gets mid-1$
-            \ELSIF{$P_d.d_j > mid$}
-                \STATE $left \gets mid+1$
-            \ENDIF
-
-        \ENDWHILE
-        \RETURN false
-    \end{algorithmic}
-\end{algorithm}
-
-\section{Results}
-\todo{ result table ?}
-\subsection{Data sets}
-\todo{ my data set}
->>>>>>> f097356e5357084561a03d31cfda480c342f78a7
-
-The tranform rate of Neblina is 50Hz.
+The transform rate of Neblina is 50Hz.
 \\
@@
 \\
-Mohamad Lateral bicep data which include 41428, produced in proximate 14 minutes.
+Mohammad Lateral bicep data which include 41428, produced in proximate 14 minutes.
 
@@
     \multicolumn{9}{|l|}{Dimension 2}                                                                                                                         \\ \hline
-    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
+    Data set               & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
     Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
-    Epsilon                & 100          & 100/sqrt(2)     & 100         & 100/sqrt(2)     & 100        & 100/sqrt(2)       & 100        & 100/sqrt(2)       \\ \hline
-    Max Error              & 127.63       & 94.46           & 99.63       & =               & =          & =                 & =          & =                 \\ \hline
-    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & =               & =          & =                 & =          & =                 \\ \hline
-    Max memory Usage(heap) & 80B          & 80B             & 648B        & =               & =          & =                 & =          & =                 \\ \hline
-    processing time Usage  & 0.005        & 0.005           & 0.005       & =               & =          & =                 & =          & =                 \\ \hline
+    Epsilon                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$  & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ \hline
+    Max Error              & 127.63       & 94.46           & 99.63       & 70.47           & 140.70     & 99.73             & 99.99      & 70.71             \\ \hline
+    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%         & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ \hline
+    Max memory Usage(peak) & 80B          & 80B             & 432B        & 240B            & 80B        & 80B               & 2.1KB      & 1.3KB             \\ \hline
+    Time Usage(Total)      & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms         & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
     \end{tabular}
@@
     \multicolumn{9}{|l|}{Dimension 3}                                                                                                                         \\ \hline
-    Dataset                & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
-    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
-    Epsilon                & 100          & 100/sqrt(3)     & 100         & 100/sqrt(3)     & 100        & 100/sqrt(3)       & 100        & 100/sqrt(3)       \\ \hline
-    Max Error              & 127.63       & 94.46           & 99.63       & =               & =          & =                 & =          & =                 \\ \hline
-    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & =               & =          & =                 & =          & =                 \\ \hline
-    Max memory Usage(heap) & 80B          & 80B             & 648B        & =               & =          & =                 & =          & =                 \\ \hline
-    processing time Usage  & 0.005        & 0.005           & 0.005       & =               & =          & =                 & =          & =                 \\ \hline
+    Data set               & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
+    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
+    Epsilon                & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$  & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\ \hline
+    Max Error              & 141.66       & 85.40           & 99.94       & 56.89           & 168.95     & 97.01             & 99.99      & 57.73             \\ \hline
+    Compression Radio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%          & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\ \hline
+    Max memory Usage(peak) & 112B         & 112B            & 384B        & 256B            & 112B       & 112B              & 4.9KB      & 3.0KB             \\ \hline
+    Time Usage(Total)      & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms         & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
     \end{tabular}

### 2018-10-05 paper.tex
mass note

--- 2018-10-01 paper.tex
@@
 
+LTC会记录一个范围，from which 可以找到一条直线，代替original data，并且保证 保证度，或者 distort。 当一个新data来的时候，base data会与 data+/-EPSILON 创建一个 临时的范围， 如果这个范围与 已经记录的范围 存在 交集，那么更新已记录的范围， 如果交集为空，则transmit base data，并将，已经记录的范围的median，and current timesamp - 1 作为 base point的值和timestamp.
+以此循环。
+画个图。
+只需要 constant Memory。
+
 \todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be written}
@@
 we provide Multidimensional-LTC with Euclidean and Manhattan distance in below.
+
+\section{Implementation}
+Our code is available at ... (make a clean release!)
+
 \subsection{Multidimensional LTC with Manhattan distance}
@@
 
-\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}
+\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILON/t_i-t_0$ + bounding box length}
 
@@
 In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
-In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version.
-After that, we extend the method for n-dimension.
+画图；
+写一个3-D的例子，并解释一下 算法
+assume 有一个 3D 的数据 (x,y,z, t_n)， 会被mapping到 (....) with error sphere EPSILON/(t_n - t_1).and check if there is public intersection with list of circle which recorded.
+首先确定x的范围，C_maxX = Min=1.n(c_i.x + E/i), C_minX = Max=1.n(c_i.x - E/i), if C_maxX < C_minX, means there is no public intersection amount those circles.
+after that 使用二分法 mid_x=(C_maxX + C_minX)/2, with x=mid_x computer bounding range of y-axis, 并对y轴继续使用 二分法，在z-axis 上计算 C_minZ and C_maxZ, 如果 C_maxZ > C_minZ 说明 在x=mid_x, y=mid_y 这条线上 存在一个或多个点 在intersection amount those circles.
+so 我们可以确认 确认交集的存在，并且 把点(mid_x, mid_y, mid_z) 保存下来，以便将来更新base point.
+
+通过这个 例子 我们可以把 3-D 延伸到 n-D。
+
+In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
 \begin{itemize}
@@
 \subsection{Experiment 1: energy reduction on the Neblina}
+
+The capacity of battery in Neblina is 100mAh, and the battery usage would not change too much, because it contans others fusion method which will running when turning on the Neblina.
+In 50Hz sensor sampling rate, the average usage electric current for transmit accelerometers data is 2.0mA. It means Neblina could tranmit accelerometers data constantly in 100/2.0=50 hours.
+After compressed by LTC-Manhattan method, the average usage electric current is 1.95mA. It just extend Neblina lift abou 1.28 hours.
+But in 200Hz sampling rate. The electric before and after compression are 3.5 and 2.9 respectively. The running time of Neblina would be extended about 5.9 hours/
+
 \begin{itemize}
-    \item Data set: 
-    \item Experiment Condition: 
+    \item Data set: human activities, running, walking, jogging and work behind desk.
+    \item Experiment Condition: work with neblina.
     \item Result:

### 2018-10-05 ltc-plot.py
Started program to draw Figure

@@ -1,0 +1,14 @@
+#!/usr/bin/env python
+
+from matplotlib import pyplot as plt
+
+# shifts used in point labels
+xshift = -0.05
+yshift = 0.05
+
+plt.plot([0], [0], 'o', color='red')
+plt.plot([1], [0.5], 'o', color='blue')
+plt.annotate("$(u^k_0, y^k_0)$", xy=(0+xshift, 0+yshift))
+plt.annotate("$(u^k_1, y^k_1)$", xy=(1+xshift, 0.5+yshift))
+plt.plot()
+plt.show()

### 2018-10-05 paper.tex
Started describing original LTC algorithm

--- 2018-10-01 paper.tex
@@
 
+% Some related works from Bo's report
+
+% transmitted, received points
+
+% contributions: formalization of LTC algorithm, extension to n d, extension to any norm, open-source implementation.
+
 \section{Lightweight Temporal Compression}
 
-Summarize existing paper.
+Lightweight Temporal Compression 
+(LTC~\cite{schoellhammer2004lightweight}) approximates the data stream 
+by a piece-wise linear function of time, ensuring that the error at 
+every time-point is bounded.
 
-Lightweight temporal compression (LTC) is one of the linear estimation 
-method to compress data. It is The first-order interpolator with two 
-degrees of freedom(FOI-2DF) which is mentioned in 
-~\cite{jalaleddine1990ecg}.  Most of linear estimation method need a 
-predefined parameter which is the error margin (let's call $\epsilon$) 
-in order to guarantee the difference between estimation and original 
-data within a scope.
+\subsection{Notations}
 
-\todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be written}
+We use the following notations and assumptions to describe the LTC algorithm.
+The algorithm \emph{receives} a stream of \emph{data points} $x_i$
+at times $t_i$ ($i \in \mathbb{N}$), and it \emph{transmits} a stream of data points $\xi_i$ 
+at times $\tau_i$ ($i \in \mathbb{N}$). To simplify the notations, we assume that:
+\begin{equation*}
+\forall k \in \mathbb{N}, \  \exists ! j \in \mathbb{N} \  \xi_k = t_j
+\end{equation*}
+That is, transmission times coincide with reception times. 
+We define the \emph{centered received points} as follows:
+\begin{equation*}
+\forall k \in \mathbb{N}\ , \forall i \in \mathbb{N},\ (u^k_i, y^k_i) = (t_{j+i} - t_j, x_{j+i}), \quad \mathrm{where}\ t_j = \xi_k.
+\end{equation*}
+This definition is such that $u^k_0=0$, and $y^k_i$ is the $i^{th}$ point received
+after the $k^{th}$ transmission.
+
+\subsection{LTC algorithm}
+
+Using the notations defined previously, the original LTC algorithm is written as 
+follows:
+% define x_i (1D), (t, x_i)
+\begin{enumerate}
+\item Initialization, after $k^{th}$ transmission:
+    \begin{itemize}
+        \item Wait until first point $(u^k_1, y^k_1)$ is received.
+        \item UL $\leftarrow$ $(u^k_1, y^k_1+\epsilon)$
+        \item LL $\leftarrow$ $(u^k_1, y^k_1-\epsilon)$
+    \end{itemize}
+\item Calculate \emph{highLine} as the line connecting $(u^k_0, y^k_0)$ and UL.
+\item Calculate \emph{lowLine} as the line connecting $(u^k_0, y^k_0)$ and LL.
+\end{enumerate}
+
+ %~ is one of the linear estimation 
+%~ method to compress data. It is The first-order interpolator with two 
+%~ degrees of freedom (FOI-2DF) which is mentioned in 
+%~ ~\cite{jalaleddine1990ecg}.  Most of linear estimation method need a 
+%~ predefined parameter which is the error margin (let's call $\epsilon$) 
+%~ in order to guarantee the difference between estimation and original 
+%~ data within a scope.
+
+%~ \todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be written}
 

### 2018-10-07 ltc-plot.py
Figure for LTC

@@ -1,14 +1,67 @@
 #!/usr/bin/env python
 
 from matplotlib import pyplot as plt
+from numpy import array
 
 # shifts used in point labels
 xshift = -0.05
-yshift = 0.05
+yshift = 0.02
 
-plt.plot([0], [0], 'o', color='red')
-plt.plot([1], [0.5], 'o', color='blue')
-plt.annotate("$(u^k_0, y^k_0)$", xy=(0+xshift, 0+yshift))
-plt.annotate("$(u^k_1, y^k_1)$", xy=(1+xshift, 0.5+yshift))
+epsilon = 0.5
+size = 'x-large'
+
+x = [0, 1, 2, 3, 4, 5, 6]
+y = [0, 1, 3.2, 4, 4, 4.8, 7]
+assert(len(x) == len(y))
+
+plt.plot(x[0], y[0], 'o', color='red')
+plt.annotate("$(u^0_0, y^0_0)$", xy=(x[0]+xshift, y[0]+yshift), fontsize=size)
+plt.plot(x[1], y[1], 'o', color='blue')
+plt.annotate("$(u^0_1, y^0_1)$", xy=(x[1]+xshift, y[1]+yshift), fontsize=size)
+plt.plot(x[1], y[1]+epsilon, 'o', color='blue')
+plt.plot(x[1], y[1]-epsilon, 'o', color='blue')
+plt.plot([x[1], x[1]], [y[1]-epsilon, y[1]+epsilon], '-', color='blue')
+
+n = len(x)
+lowpoint = y[1] - epsilon
+highpoint = y[1] + epsilon
+trans_x, trans_y = x[0], y[0]
+k = 1
+j = 0
+for i in range(2, n):
+    j += 1
+    # Plot point and [y-epsilon, y+epsilon] interval
+    plt.plot(x[i], y[i], 'o', color='blue')
+    plt.annotate("$(u^{}_{}, y^{}_{})$".format(k, j, k, j), xy=(x[i]+xshift, y[i]+yshift), fontsize=size)
+    plt.plot(x[i], y[i]+epsilon, 'o', color='blue')
+    plt.plot(x[i], y[i]-epsilon, 'o', color='blue')
+    plt.plot([x[i], x[i]], [y[i]-epsilon, y[i]+epsilon], '-', color='blue')
+    # plt.annotate("$(u^{}_{}, y^{}_{}+\epsilon)$".format(k, j, k, j), xy=(x[i]+xshift, y[i]+epsilon+yshift), fontsize=size)
[…]

### 2018-10-09 paper.tex
Finished section II, advanced in section III

@@
 \usepackage{algorithm}
-\usepackage{algorithmic}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
+%\usepackage{algorithmic}
+\usepackage{algorithmicx} % Doc is at http://tug.ctan.org/macros/latex/contrib/algorithmicx/algorithmicx.pdf
+\usepackage{algpseudocode}
+%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+%\renewcommand{\algorithmicensure}{\textbf{Output:}}
 %\usepackage{algpseudocode}
@@
 
-\title{A multi-dimensional extension of the Lightweight Temporary Compression method}
+\title{A multi-dimensional extension of the Lightweight Temporal Compression method}
 
@@
 
-We use the following notations and assumptions to describe the LTC algorithm.
 The algorithm \emph{receives} a stream of \emph{data points} $x_i$
@@
 \begin{equation*}
-\forall k \in \mathbb{N}, \  \exists ! j \in \mathbb{N} \  \xi_k = t_j
+\forall k \in \mathbb{N}, \  \exists ! i \in \mathbb{N} \  \tau_k = t_i
 \end{equation*}
@@
 \begin{equation*}
-\forall k \in \mathbb{N}\ , \forall i \in \mathbb{N},\ (u^k_i, y^k_i) = (t_{j+i} - t_j, x_{j+i}), \quad \mathrm{where}\ t_j = \xi_k.
+\forall k \in \mathbb{N}\ , \forall j \in \mathbb{N^*},\ (u^k_j, y^k_j) = (t_{i+j}, x_{i+j}), \quad \mathrm{where\ }i\mathrm{\ is\ s.t.}\ t_i = \tau_k.
 \end{equation*}
-This definition is such that $u^k_0=0$, and $y^k_i$ is the $i^{th}$ point received
+and:
+\begin{equation*}
+\forall k \in \mathbb{N},\  (u^k_0, y^k_0) = (\tau_k, \xi_k).
+\end{equation*}
+This definition is such that $u^k_0=0$, and $y^k_j$ is the $j^{th}$ data point received
 after the $k^{th}$ transmission.
 
+Figure~\ref{fig:ltc} illustrates the notations and algorithm.  
+\begin{figure}
+\includegraphics[width=\columnwidth]{ltc.pdf}
+\caption{Illustration of the LTC algorithm and notations used. Red dots indicate transmitted points. Dashed lines
+represent the high line and the low line before a point is transmitted.}
+\label{fig:ltc}
+\end{figure}
 \subsection{LTC algorithm}
 
-Using the notations defined previously, the original LTC algorithm is written as 
-follows:
-% define x_i (1D), (t, x_i)
-\begin{enumerate}
-\item Initialization, after $k^{th}$ transmission:
-    \begin{itemize}
-        \item Wait until first point $(u^k_1, y^k_1)$ is received.
-        \item UL $\leftarrow$ $(u^k_1, y^k_1+\epsilon)$
-        \item LL $\leftarrow$ $(u^k_1, y^k_1-\epsilon)$
-    \end{itemize}
-\item Calculate \emph{highLine} as the line connecting $(u^k_0, y^k_0)$ and UL.
-\item Calculate \emph{lowLine} as the line connecting $(u^k_0, y^k_0)$ and LL.
-\end{enumerate}
+The LTC algorithm maintains two lines, the \emph{high line}, and the 
+\emph{low line} defined by (1) the latest transmitted point and (2) the 
+\emph{high point} (high line) and the \emph{low point} (low line). When 
+a point ($t_i$, $x_i$) is received, the high line is updated as 
+follows: if $x_i+\epsilon$ is below the high line, the high line is 
+updated to the line defined by the last transmitted point and ($t_i$, 
+$x_i$); otherwise, the high line is not updated. Likewise, the low line 
+is updated from $x_i-\epsilon$. Threfore, any line located between the 
+high line and the low line approximates the data points received since 
+the last transmitted point with an error bounded by $\epsilon$.
+
+Using the notations defined previously, the original LTC algorithm can 
+be written as in Algorithm~\ref{algo:ltc}. For readability, we assume 
+that access to data points is blocking, i.e., the program will wait 
+until the points are available. We also assume that the content of 
+variable \texttt{tr} is transmitted after each assignment of this 
+variable. Function \texttt{line}, omitted for brevity, returns the 
+ordinate at abscissa $x$ (1st argument) of the line defined by the points
+in its 2nd and 3rd arguments.
+
+\begin{algorithm}
+\begin{algorithmic}[1]
+\State tr = $(u^0_0, y^0_0)$ \Comment{last transmitted point}
+\State k = 1 ; j = 1
+\State lp = $y^1_1 - \epsilon$ \Comment{low point}
+\State hp = $y^1_1 + \epsilon$ \Comment{high point}
+%\Function{line}{$x$, ($x_0$, $y_0$), ($x_1$, $y_1$)} 
+% \Comment{Return the ordinate of the line defined by $(x_0, y_0)$, $(x_1, y_1)$ at abscissa $x$.}
+%\Return $y_0 + \frac{y_1-y_0}{x_1-x_0}(x-x_0)$
+%\EndFunction
+\While{True} \Comment{Process received points as they come}
+    \State j += 1
+    \State new\_lp = max($y^k_j-\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, lp)))
+    \State new\_hp = max($y^k_j+\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, hp)))
+    \If{new\_lp $<$ new\_hp} \Comment{Keep compressing}
+        \State lp = new\_lp
+        \State hp = new\_hp
+        \State \textbf{continue}
+    \EndIf
+    \State tr = $(u^k_j, (lp+hp)/2)$
+    \Comment{Transmit point}
+    \State lp = $y^k_j-\epsilon$
+    \State hp = $y^k_j+\epsilon$
+    \State k += 1
+    \State j = 0
+\EndWhile
+\end{algorithmic}
+\caption{Original LTC algorithm, adapted from~\cite{schoellhammer2004lightweight}.}
+\label{algo:ltc}
+\end{algorithm}
 
@@
 
-\subsection{General formulation}
+In this section we provide a distance-independent formulation of LTC in 
+dimension $n$. By $n$, we refer to the dimension of the data points 
+($x_i$). To handle time, LTC actually operates in dimension 
+$n+1$.
 
-In this section we provide a distance-independent formulation of LTC in 
-dimension $n$. The formulation of LTC in~\cite{ltc} relies on the intersection
-of \emph{convex cones} in dimension $n+1$.
+\subsection{Preliminary comments}
 
-When $n$ is higher than 1, the intersection of convex cones unwieldy to 
-formalize. Instead, we formulate LTC as an intersection test 
-between $m$ \emph{balls} of dimension 
-$n$. We formulate LTC recursively, as follows.
+The formulation of LTC in~\cite{schoellhammer2004lightweight} relies on 
+the intersection of \emph{convex cones} in dimension $n+1$. For $n=1$, it 
+corresponds to the intersection of triangles, which can efficiently be 
+computed by maintaining boundary lines, as detailed in the previous 
+section. In higher dimension, however, cone intersections are not so 
+straighforward, due to the fact that the intersection between 2 cones 
+may not be a cone.
 
-Let $x_0 \in \mathbb{R}^n$ be the last data point transmitted by the 
-algorithm. For convenience, all the subsequent data points will be 
-expressed in the orthogonal space with origin $x_0$. Without loss of 
+To address this issue, we formulate LTC as an intersection test between 
+\emph{balls} of dimension $n$, that is, segments for $n=1$, disks for 
+$n=2$, etc. Balls are defined with respect to the \emph{norm} used in 
+the vector space of data points. For $n=1$, the choice of the norm does 
+not really matter, as all p-norms and the infinity norm are identical. 
+In dimension $n$, however, norm selection will be critical.
+
+\subsection{Algebraic formulation of LTC}
+
+Let $(u_0^k, y_0^k) \in \mathbb{R}^{n+1}$ be the latest transmitted point. For convenience, all the subsequent points will be 
+expressed in the orthogonal space with origin $(u_0^k, y_0^k)$. We denote by $(v_j, z_j)_{j \in \llbracket 0, m \rrbracket}$ such points:
+\begin{equation*}
+\forall j \leq m,\  (v_j, z_j) = (u_j^k - u_0^k, y_j^k - y_0^k)
+\end{equation*}
+Without loss of 
 generality, we assume that the data points are sampled uniformly with a 
-sampling period of 1 time unit. Let k be the number of data points 
-following $x_0$ that have been compressed.
+sampling period of 1 time unit.
 
-The intersection of convex cones in dimension $n+1$ can be written as follows:
-\ldots
+We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $z_j$ and of radius 
+$\epsilon$:
+\begin{equation*}
+\mathcal{B}_j = \left\{ z \in \mathbb{R}^n,\  \norm{z-z_j} \leq \epsilon \right\} \ (j \leq m)
+\end{equation*}
+We define $\mathcal{B}'_j$ by plunging $\mathcal{B}_j$ in $\mathbb{R}^{n+1}$:
+\begin{equation*}
+\mathcal{B'}_j = \left\{ (a_0, \ldots, a_{n}) \in \mathbb{R}^{n+1},\  a_0 = v_j^k \mathrm{\ and\ } (a_1, \ldots, a_{n}) \in \mathcal{B}_j \right\}
+\end{equation*}
+$\mathcal{B'}_j$ defines a convex cone $\mathcal{C}_j$ in $\mathbb{R}^{n+1}$:
+\begin{equation*}
+\mathcal{C}_j = \left\{ \alpha x  \in \mathbb{R}^{n+1},\ x \in \mathcal{B'}_j,\ \alpha \in \mathbb{R}^+ \right\}
+\end{equation*}
 
-Which is equivalent to the following formulation in $\mathbb{R}^n$:
-\begin{eqnarray*}
-&& \exists \textbf{u} \in \mathbb{R}^{n} \  s.t. \  \forall i \in \llbracket 1, k \rrbracket, \quad
-\norm{i\textbf{u} - \textbf{x}_i} \leq \epsilon\\
-\Leftrightarrow && \exists \textbf{u} \in \mathbb{R}^{n} \  s.t. \  \forall i \in \llbracket 1, k \rrbracket, \quad
-\norm{\textbf{u} - \frac{1}{i}\textbf{x}_i} \leq \frac{\epsilon}{i} \\
-\Leftrightarrow && \bigcap_{i=1}^{k} {\mathcal{B}}_i \neq \O,
-\end{eqnarray*}
-where $\mathcal{B}_i 
-\subset \mathbb{R}^n$ is the ball of center $\frac{1}{i}\textbf{x}_i$ 
-and radius $\frac{\epsilon}{i}$.
+No data point will be transmitted as long as:
+\begin{equation*}
+\bigcap_{j=0}^m{\mathcal{C}_j} \neq \O
+\end{equation*}
+Which, due to the definition of convex cones, implies that:
+\begin{equation*}
+\exists x=(a_0, \ldots a_n) \in \mathbb{R}^{n+1},\ \forall j \in \llbracket 0, m \rrbracket,\ \forall \alpha \in \mathbb{R^+}, \alpha x \in \mathcal{C}_j
+\end{equation*}
+Without loss of generality, we can assume that $a_0=v^k_1$ since any multiple
+of $x$ is also in $\mathcal{C}_j$. 
+This implies that $x \in \mathcal{B}'_1$.
 
@@
 %~ \end{eqnarray*}
+
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,biblio.bib}
+\end{document}
 
@@
 
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,biblio.bib}
-
 \end{document}

### 2018-10-09 ltc-plot.py

@@ -3,65 +3,104 @@
 from matplotlib import pyplot as plt
 from numpy import array
 
-# shifts used in point labels
-xshift = -0.05
-yshift = 0.02
 
+def plot_point(x, y, epsilon, j, k, transmitted):
+    xshift = 0.05
+    yshift = 0
+    size = 'x-small'
+    label = "$(u^{}_{}, y^{}_{})$".format(k, j, k, j)
+    if transmitted:
+        color = 'red'
+    else:
+        color = 'blue'
+    plt.plot(x, y, '.', color=color)
+    plt.annotate(label,
+                 xy=(x+xshift, y+yshift),
+                 fontsize=size)
+    if not transmitted:
+        plt.plot(x, y+epsilon, '.', color=color)
+        plt.plot(x, y-epsilon, '.', color=color)
+        plt.plot([x, x], [y-epsilon, y+epsilon], '-', color='blue')
+
+def y_line(x, point_x, point_y, trans_x, trans_y):
+    '''
+    Return the value of y such that (x,y) is on the line
+    defined by (trans_x, trans_y), (point_x, point_y)
+    point may be the high or the low point
+    '''
+    return trans_y + (point_y-trans_y)/(point_x-trans_x)*(x-trans_x)
+
+# Constants
 epsilon = 0.5
-size = 'x-large'
-
 x = [0, 1, 2, 3, 4, 5, 6]
-y = [0, 1, 3.2, 4, 4, 4.8, 7]
+y = [0, 1, 2.1, 4, 4.15, 5.6, 7.3]
 assert(len(x) == len(y))
-
-plt.plot(x[0], y[0], 'o', color='red')
-plt.annotate("$(u^0_0, y^0_0)$", xy=(x[0]+xshift, y[0]+yshift), fontsize=size)
-plt.plot(x[1], y[1], 'o', color='blue')
-plt.annotate("$(u^0_1, y^0_1)$", xy=(x[1]+xshift, y[1]+yshift), fontsize=size)
-plt.plot(x[1], y[1]+epsilon, 'o', color='blue')
-plt.plot(x[1], y[1]-epsilon, 'o', color='blue')
-plt.plot([x[1], x[1]], [y[1]-epsilon, y[1]+epsilon], '-', color='blue')
-
 n = len(x)
+
+# Initialization
 lowpoint = y[1] - epsilon
 highpoint = y[1] + epsilon
 trans_x, trans_y = x[0], y[0]
-k = 1
[…]

### 2018-10-09 paper.tex
update

--- 2018-10-05 paper.tex
@@
 
+In practice, It's needed to transmit raw data which has multi-parameters to clients e.g.
+Accelerometer, Euler Angle and Magnetometer etc.
+Most of 以前的 paper just force on single dimension sensor data Compression.
+**** .
+So we purpose a method to compress multi-dimensional sensor data named LTC-D.
+It is used as linear estimation method.
+Same as usual estimation compression method,  distance(different) with compressed data from LTC-D and original data would not exceed the predefined error range.
+We need to find line to represent original data, it means the lines
+pass through datas' error range.
+But in stream data, time seires data, it is difficult, because all data do not show in same time plane.
+So this method will mapping all data into one time plane.
+Then for each mapped error range of data, check if there is intersection among them.
+If so means there is a line could represent original data, and vice versa.
+
+The method as below: assume the stream $i_{th}$ data $D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$ in our Method.
+通常设置 base point之后的一个时间节点作为mapping节点.
+We also need to record the intersect S for find result lines.
+我们确定以 base point 之后的第一个时间节点， 作为mapping的目标节点，再在 The first data D_1 would change into tolerance range R_1.
+我们 set S = R_1.
+For each follow data D_i i>1, mapping D_1 into hat(D_1) = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$, and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$.
+the tolerance range after R_i, intersect with S, if there is overlap, update S = S 交 R_i. If not, the base point would be transmited and select a point in S as base point with timestamp t_{i-1}.
+
+\todo{refector}
+At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
+\begin{enumerate}
+  \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
+Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
+  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
+  \item Goto 2.
+  \item output \textit{z} data point.
+  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
+  \item Goto 2.
+  \item After all, output \textit{z} data point and center of bounding box respectively.
+\end{enumerate}
+
+对于 误差范围，会根据EPSILON 改变，也会根据我们设定的 data 与 EPSILON 的 不同类型的距离有关系。
+
+如果使用 Manhattan的话 误差范围 会变成 RequirePackagectangle or cube for 2d and 3d respectively. 就是 EPSILON*sqrt(d)  图
+如果使用 Euclidean的话 误差范围 会变成 disk or ball 分别是 2d, 3d， 保持 EPSILON.图
+
+我们用2d Manhattan 来做例子。 画图
+
 \section{Extension to dimension $n$}
@@
 cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance.
-checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
+After that updating tolerance range by adding designed error margin which after mapping
+$\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance. checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
 
@@
 so 我们可以确认 确认交集的存在，并且 把点(mid_x, mid_y, mid_z) 保存下来，以便将来更新base point.
+在这个算法中 第一次遍历circle 得到maxX maxY 需要 O(n) 然后 二分法O(lgn) 进入循环, 之后 O(n) 遍历，在二分法 mid_y, 进入循环之后需要O(n) 遍历circle 得到 max_z and min_z 所以 复杂度是 O(n) + O(lgn)*(O(n) + O(lgn)*O(n)) = O(lgn lgn n)
 

### 2018-10-10 paper.tex
Finished section III

--- 2018-10-09 paper.tex
@@
 \usepackage{algpseudocode}
+%\newtheorem*{theorem}{Lemma}
+
 %\renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
 
+\newtheorem*{theorem}{Theorem}
+
 \begin{document}
@@
 \begin{abstract}
-\end{abstract}
-
-\section{Introduction}
-
-LTC is among the stream compression method that provides the highest 
-compression rate for the lowest resource (CPU, RAM) consumption. As 
-such, it makes it a very good candidate for the compression of data 
-streams acquired in embedded, low-power systems such as connected 
+Lightweight Temporal Compression 
+(LTC~\cite{schoellhammer2004lightweight}) is among the stream 
+compression method that provides the highest compression rate for the 
+lowest resource (CPU, RAM) consumption. As such, it makes it a very 
+good candidate for the compression of data streams acquired in 
+embedded, low-power systems such as connected 
 objects, systems on module (SoMs), etc The type of data acquired on 
@@
 actual movement of the sensor. In this paper, we investigate the 
-extension of LTC to higher dimensions. First, we express the algorithm 
-in an arbitrary vectorial space of dimension $n$. Second, we 
-instantiate it for the Euclidean and xxx distances, in spaces of 
+extension of LTC to higher dimensions. First, we provide a formulation of the algorithm 
+in an arbitrary vectorial space of dimension $n$. Furthermore, we 
+implement the algorithm for the infinity and Euclidean norms, in spaces of 
 dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC 
@@
 device.
+\end{abstract}
 
-In practice, It's needed to transmit raw data which has 
-multi-parameters to clients e.g. Accelerometer, Euler Angle and 
-Magnetometer etc. LTC not work well when we transmit multi-parameters 
-data, cause if we just implement LTC for each parameter, the difference 
-between estimation and origin could exceed error margin which was set 
-in advance. For instance, there is a data $(x, y)$ with two parameters, 
-and using LTC for both parameter respectively. According to LTC method 
-$\mid{\hat{x}-x}\mid\leqslant \epsilon$~\cite{jalaleddine1990ecg}, the 
-estimation may be $(\hat{x}=x+\epsilon, \hat{y}=y+\epsilon)$, then the 
-difference between estimation and original data $(x,y)$ is which is 
-bigger than error margin predefined. In this case, we design a new 
-algorithm, which is multi-parameter version of LTC, and it also work 
-with any type of distance. In standard LTC method, it checks if there 
-is overlapping part between new sector area and recorded range. 
-However, in our multidimensional method, we will map every data point 
-into same time-stamp e.g. $t_0$. It is convenient for us to calculate 
-distance between them and check if overlapping range exists. we provide 
-Multidimensional-LTC with Euclidean and Manhattan distance in below.
+\section{Introduction}
+
+Section~\ref{sec:ltc} provides some background on the LTC algorithm. 
+Section~\ref{sec:extension} presents our formulation in dimension $n$.
 
@@
 \section{Lightweight Temporal Compression}
+\label{sec:ltc}
 
-Lightweight Temporal Compression 
-(LTC~\cite{schoellhammer2004lightweight}) approximates the data stream 
+LTC approximates the data stream 
 by a piece-wise linear function of time, ensuring that the error at 
@@
 \end{equation*}
-This definition is such that $u^k_0=0$, and $y^k_j$ is the $j^{th}$ data point received
+This definition is such that $y^k_j$ is the $j^{th}$ data point received
 after the $k^{th}$ transmission.
-
 Figure~\ref{fig:ltc} illustrates the notations and algorithm.  
@@
 \caption{Illustration of the LTC algorithm and notations used. Red dots indicate transmitted points. Dashed lines
-represent the high line and the low line before a point is transmitted.}
+represent the high line and the low line at times when a point is transmitted.}
 \label{fig:ltc}
@@
 a point ($t_i$, $x_i$) is received, the high line is updated as 
-follows: if $x_i+\epsilon$ is below the high line, the high line is 
+follows: if $x_i+\epsilon$ is below the high line then the high line is 
 updated to the line defined by the last transmitted point and ($t_i$, 
-$x_i$); otherwise, the high line is not updated. Likewise, the low line 
-is updated from $x_i-\epsilon$. Threfore, any line located between the 
+$x_i+\epsilon$); otherwise, the high line is not updated. Likewise, the low line 
+is updated from $x_i-\epsilon$. Therefore, any line located between the 
 high line and the low line approximates the data points received since 
@@
 
-Using the notations defined previously, the original LTC algorithm can 
+Using these notations, the original LTC algorithm can 
 be written as in Algorithm~\ref{algo:ltc}. For readability, we assume 
@@
 \State tr = $(u^0_0, y^0_0)$ \Comment{last transmitted point}
-\State k = 1 ; j = 1
-\State lp = $y^1_1 - \epsilon$ \Comment{low point}
-\State hp = $y^1_1 + \epsilon$ \Comment{high point}
-%\Function{line}{$x$, ($x_0$, $y_0$), ($x_1$, $y_1$)} 
-% \Comment{Return the ordinate of the line defined by $(x_0, y_0)$, $(x_1, y_1)$ at abscissa $x$.}
-%\Return $y_0 + \frac{y_1-y_0}{x_1-x_0}(x-x_0)$
-%\EndFunction
+\State k = 0 ; j = 1
+\State (lp, hp) = ($y^1_1 - \epsilon$, $y^1_1 + \epsilon$) \Comment{low and high points}
+
 \While{True} \Comment{Process received points as they come}
@@
     \If{new\_lp $<$ new\_hp} \Comment{Keep compressing}
-        \State lp = new\_lp
-        \State hp = new\_hp
+        \State (lp = new\_lp, new\_hp)
         \State \textbf{continue}
@@
     \Comment{Transmit point}
-    \State lp = $y^k_j-\epsilon$
-    \State hp = $y^k_j+\epsilon$
+    \State (lp, hp) = ($y^k_j-\epsilon$, $y^k_j+\epsilon$)
     \State k += 1
@@
 \section{Extension to dimension $n$}
-
-In this section we provide a distance-independent formulation of LTC in 
-dimension $n$. By $n$, we refer to the dimension of the data points 
-($x_i$). To handle time, LTC actually operates in dimension 
+\label{sec:extension}
+In this section we provide a norm-independent formulation of LTC in 
+dimension $n$. By $n$ we refer to the dimension of the data points 
+$x_i$. To handle time, LTC actually operates in dimension 
 $n+1$.
@@
 
-The formulation of LTC in~\cite{schoellhammer2004lightweight} relies on 
+We note that the formulation of LTC in~\cite{schoellhammer2004lightweight} relies on 
 the intersection of \emph{convex cones} in dimension $n+1$. For $n=1$, it 
 corresponds to the intersection of triangles, which can efficiently be 
-computed by maintaining boundary lines, as detailed in the previous 
-section. In higher dimension, however, cone intersections are not so 
-straighforward, due to the fact that the intersection between 2 cones 
+computed by maintaining boundary lines, as detailed previously. In higher dimension, however, cone intersections are not so 
+straighforward, due to the fact that the intersection between cones 
 may not be a cone.
@@
 \emph{balls} of dimension $n$, that is, segments for $n=1$, disks for 
-$n=2$, etc. Balls are defined with respect to the \emph{norm} used in 
+$n=2$, etc. Balls are defined from the \emph{norm} used in 
 the vector space of data points. For $n=1$, the choice of the norm does 
@@
 
+\subsubsection{Definitions}
+
 Let $(u_0^k, y_0^k) \in \mathbb{R}^{n+1}$ be the latest transmitted point. For convenience, all the subsequent points will be 
-expressed in the orthogonal space with origin $(u_0^k, y_0^k)$. We denote by $(v_j, z_j)_{j \in \llbracket 0, m \rrbracket}$ such points:
+expressed in the orthogonal space with origin $(\tau^k, \xi^k)$. We denote by $(v_j, z_j)_{j \in \llbracket 0, m \rrbracket}$ such points:
 \begin{equation*}
-\forall j \leq m,\  (v_j, z_j) = (u_j^k - u_0^k, y_j^k - y_0^k)
+\forall j \leq m,\  (v_j, z_j) = (u_j^k - \tau^k, y_j^k - \xi^k)
 \end{equation*}
-Without loss of 
-generality, we assume that the data points are sampled uniformly with a 
-sampling period of 1 time unit.
-
-We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $z_j$ and of radius 
-$\epsilon$:
+We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $\frac{1}{j}z_j$ and of radius 
+$\frac{\epsilon}{j}$:
 \begin{equation*}
-\mathcal{B}_j = \left\{ z \in \mathbb{R}^n,\  \norm{z-z_j} \leq \epsilon \right\} \ (j \leq m)
-\end{equation*}
-We define $\mathcal{B}'_j$ by plunging $\mathcal{B}_j$ in $\mathbb{R}^{n+1}$:
-\begin{equation*}
-\mathcal{B'}_j = \left\{ (a_0, \ldots, a_{n}) \in \mathbb{R}^{n+1},\  a_0 = v_j^k \mathrm{\ and\ } (a_1, \ldots, a_{n}) \in \mathcal{B}_j \right\}
-\end{equation*}
-$\mathcal{B'}_j$ defines a convex cone $\mathcal{C}_j$ in $\mathbb{R}^{n+1}$:
-\begin{equation*}
-\mathcal{C}_j = \left\{ \alpha x  \in \mathbb{R}^{n+1},\ x \in \mathcal{B'}_j,\ \alpha \in \mathbb{R}^+ \right\}
+\mathcal{B}_j = \left\{ z \in \mathbb{R}^n,\  \norm{z-\frac{v_1}{v_j}z_j} \leq \frac{v_1}{v_j}\epsilon \right\}
 \end{equation*}
 
-No data point will be transmitted as long as:
+\subsection{LTC property}
+
+We formulate the \emph{LTC property} as follows:
 \begin{equation*}
-\bigcap_{j=0}^m{\mathcal{C}_j} \neq \O
+\exists z \in \mathbb{R}^n, \ \forall j \in \llbracket 1, m \rrbracket, \norm{\frac{v_j}{v_1}z-z_j} \leq \epsilon.
 \end{equation*}
-Which, due to the definition of convex cones, implies that:
+The LTC algorithm ensures that the LTC property is 
+verified between each transmission. Indeed, all the data points 
+$z$ such that $(v_1, z)$ is between the high line and the low line 
+verify the property. Line 9 in Algorithm~\ref{algo:ltc} guarantees that
+such a point exists.
+The LTC property can be written as follows:
 \begin{equation*}
-\exists x=(a_0, \ldots a_n) \in \mathbb{R}^{n+1},\ \forall j \in \llbracket 0, m \rrbracket,\ \forall \alpha \in \mathbb{R^+}, \alpha x \in \mathcal{C}_j
+\exists z \in \mathbb{R}^n, \ \forall j \in \llbracket 1, m \rrbracket, \norm{z-\frac{v_1}{v_j}z_j} \leq \frac{v_1}{v_j}\epsilon
 \end{equation*}
-Without loss of generality, we can assume that $a_0=v^k_1$ since any multiple
-of $x$ is also in $\mathcal{C}_j$. 
-This implies that $x \in \mathcal{B}'_1$.
+that is:
+\begin{equation}
+\bigcap_{j=1}^m \mathcal{B}_j \neq \O
+\label{eq:ltc-property}
+\end{equation}
+Note that $(\mathcal{B}_j)_{j \in \llbracket 1, m \rrbracket}$ is a sequence
+of balls of strictly decreasing radius, since $v_j > v_1$.
+\todo{Add a figure to illustrate this}
+
+\subsection{Algorithm}
+
+The LTC algorithm generalized to dimension $n$ test, for each data point,
+that the LTC property in Equation~\ref{eq:ltc-property} is verified. It is written in
+Algorithm~\ref{algo:general-ltc}.
+\begin{algorithm}
+\begin{algorithmic}[1]
+\State tr = ($\tau, \xi$) = ($u^0_0, y^0_0$)
+\State k = 0 ; j = 0
+\While{True}
+    \State j += 1
+    \State ($v_j, z_j$) = ($u_j^k - \tau, y_j^k - \xi$)
+    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} \neq \O$}
+        \State \textbf{continue}
+    \EndIf
+    \State Pick $z$ in $\bigcap_{l=1}^{j-1}{\mathcal{B}_j}$
+    \State tr = ($\tau$, $\xi$) = ($u^k_{j-1}, z$)
+    \State k += 1
+    \State j = 0
+\EndWhile
+\end{algorithmic}
+\caption{Generalized LTC}
+\label{algo:general-ltc}
+\end{algorithm}
+
+\todo{Check algorithms (reimplement)}
+
+\subsection{Ball intersections}
+
+Although Algorithm~\ref{algo:general-ltc} looks simple, one should not 
+overlook the fact that there is no good general algorithm to test 
+whether a set of balls intersect. The best general algorithm we could find 
+so far relies on Helly's theorem which is formulated as follows~\cite{helly1923mengen}:
+\begin{theorem}
+Let $\left\{ X_i \right\}_{i \in \llbracket 1, m \rrbracket}$ be a collection of convex subsets of $\mathbb{R}^n$. If the intersection of every $n+1$ 
+subsets is non-empty, then the whole collection has an non-empty intersection.
+\end{theorem}
+This theorem leads to an algorithm of complexity ${m \choose n+1}$ which is 
+not usable in resource-constrained environment.
+
+The only feasible algorithm that we found is norm-specific. It 
+maintains a representation of the intersection 
+$\bigcap_{j=1}^{m}{\mathcal{B}_m}$ which is updated at every iteration.
+The intersection tests can then be done in constant time, however, 
+updating the representation of the intersection may be more costly 
+depending on the norm used. For the infinity norm, the representation 
+is a rectangular cuboid which is straightforward to update by 
+intersection with an n-ball, since the n-ball is a rectangular cuboid too.
+For the Euclidean norm, the representation is a volume with no specific property,
+which is more costly to maintain.
 
@@
 
-It should be noted that the norm has a critical impact on the 
-compression error and ratio. For instance, using the infinity instead 
-of the Euclidean norm increases the compression error by a factor of 
-$\sqrt{n}$ in dimension $n$, and increases the compression ratio by xxx.
+As mentioned before, norm selection in $\mathbb{R}^n$ has a critical 
+impact on the compression error and ratio. To appreciate this effect, 
+let us consider the comparison between the infinity norm and the 
+Euclidean norm in dimension 2. By comparing the unit disk to the unit 
+square, we obtain that the compression ratio of a random stream would 
+be $\frac{4}{\pi}$ times larger with the infinity norm than with the 
+Euclidean norm. Conversely, a compression error bounded by $\epsilon$ 
+with the infinity norm corresponds to a compression error of 
+$\frac{\epsilon}{\sqrt{2}}$ with the Euclidean norm. Unsurprisingly, the
+infinity norm is more 'tolerant' than the Euclidean norm.
 
-%~ Point $k+1$ will be compressed if and only if:
-%~ \begin{eqnarray*}
-%~ && \bigcap_{i=1}^{k+1} {\mathcal{B}}_i \neq \O \\
-%~ \Leftrightarrow && {\mathcal{B}}_{k+1} \cap \bigcap_{i=1}^{k} {\mathcal{B}}_i \neq \O
-%~ \end{eqnarray*}
+\todo{Perhaps add a figure}
 
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,biblio.bib}
-\end{document}
+It should also be noted that using the infinity norm boils down to the 
+use of the 1D LTC algorithm independently in each dimension: a data 
+point is transmitted as soon as the linear approximation doesn't hold 
+in any of the coordinates. \todo{This is unclear}
 
@@
 \subsection{Multidimensional LTC with Manhattan distance}
-In practice, Multidimensional LTC is same as implementing LTC in each parameter respectively.
-But we did some changes in our method.
-Assume $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., z_{n},t_z)$~\cite{schoellhammer2004lightweight}.
-We map each coming data to $t_1$ time-stamp and create a bounding box for recording overlapping range which includes upper and lower bound for each dimension base on $t_1$.
-cause the time different between two adjacent data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-After that updating tolerance range by adding designed error margin which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$ with Manhattan distance.
-checking if there is overlap between tolerance and bounding box.The algorithm is as follows.
+In practice, Multidimensional LTC is same as implementing LTC in each 
+parameter respectively. But we did some changes in our method. Assume 
+$(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with 
+n-dimension, and a base data point Z  $(z_{1}, z_{2}, ..., 
+z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming 
+data to $t_1$ time-stamp and create a bounding box for recording 
+overlapping range which includes upper and lower bound for each 
+dimension base on $t_1$. cause the time different between two adjacent 
+data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j + 
+\frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$. 
+After that updating tolerance range by adding designed error margin 
+which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, 
+j={1...n}$ with Manhattan distance. checking if there is overlap 
+between tolerance and bounding box.The algorithm is as follows.
 
@@
 
-At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
+At beginning of the algorithm, we need a base point (which we will call 
+\textit{z}) and bounding box which has upper and lower bound for each 
+parameter respectively.Then start the algorithm.
 \begin{enumerate}
@@
     \begin{algorithmic}[1]
-        \STATE $tmp_list \gets null$
-        \STATE $max\_x\gets d.x+d.r$
-        \STATE $min\_x\gets d.x-d.r$
+        \State $tmp_list \gets null$
+        \State $max\_x\gets d.x+d.r$
+        \State $min\_x\gets d.x-d.r$
 
-        \FORALL{$old\_disk$ \textbf{in} $l$}
-            \IF{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
-                \STATE \textbf{return} false
-            \ELSIF{$d \cap old\_disk \neq d$}
-                \STATE {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
+        \ForAll{$old\_disk$ \textbf{in} $l$}
+            \If{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
+                \State \textbf{return} false
+            \ElsIf{$d \cap old\_disk \neq d$}
+                \State {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
                         $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
                         $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
-            \ENDIF
-        \ENDFOR
-        \STATE $\textbf{add } d \textbf{ into } tmp\_list$
-        \IF{$max\_x < min\_x$}
-            \STATE \textbf{return} false
-        \ENDIF
-        \WHILE{$min\_x \leqslant max\_x$}
-            \STATE $mid \gets (min\_x + max\_x)/2$
-            \STATE $max\_y \gets +\infty$
-            \STATE $min\_y \gets -\infty$
-            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
-                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
-                \IF{$P_1.y < max\_y$}
-                    \STATE $max\_y \gets p_1.y$
-                    \STATE $max\_index \gets i$
-                \ENDIF
-                \IF{$P_2.y > min\_y$}
-                    \STATE $min\_y \gets p_2.y$
-                    \STATE $min\_index \gets i$
-                \ENDIF
-            \ENDFOR
-            \IF{$max\_y >= min\_y$}
-                \STATE $p.x \gets mid$
-                \STATE $p.y \gets (max\_y+min\_y)/2$
-                \STATE $l \gets tmp\_list$
-                \STATE \textbf{return} true
-            \ENDIF
-            \STATE {Assume $P_d$ is the intersection between line of 
+            \EndIf
+        \EndFor
+        \State $\textbf{add } d \textbf{ into } tmp\_list$
+        \If{$max\_x < min\_x$}
+            \State \textbf{return} false
+        \EndIf
+        \While{$min\_x \leqslant max\_x$}
+            \State $mid \gets (min\_x + max\_x)/2$
+            \State $max\_y \gets +\infty$
+            \State $min\_y \gets -\infty$
+            \For{$i=1$ \textbf{to} $tmp\_list.length$}
+                \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
+                \If{$P_1.y < max\_y$}
+                    \State $max\_y \gets p_1.y$
+                    \State $max\_index \gets i$
+                \EndIf
+                \If{$P_2.y > min\_y$}
+                    \State $min\_y \gets p_2.y$
+                    \State $min\_index \gets i$
+                \EndIf
+            \EndFor
+            \If{$max\_y >= min\_y$}
+                \State $p.x \gets mid$
+                \State $p.y \gets (max\_y+min\_y)/2$
+                \State $l \gets tmp\_list$
+                \State \textbf{return} true
+            \EndIf
+            \State {Assume $P_d$ is the intersection between line of 
             centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
             , and their common chord}
-            \IF{$P_d.x < mid$}
-                \STATE $max\_y \gets mid-1$
-            \ELSIF{$P_d.x > mid$}
-                \STATE $min\_y \gets mid+1$
-            \ENDIF
-        \ENDWHILE
-        \RETURN false
+            \If{$P_d.x < mid$}
+                \State $max\_y \gets mid-1$
+            \ElsIf{$P_d.x > mid$}
+                \State $min\_y \gets mid+1$
+            \EndIf
+        \EndWhile
+        \Return false
     \end{algorithmic}
@@
     \begin{algorithmic}[1]
-        \STATE $tmp_list \gets null$
-        \STATE $max \gets o.d\_n+o.r$
-        \STATE $min \gets o.d\_n-o.r$
+        \State $tmp_list \gets null$
+        \State $max \gets o.d\_n+o.r$
+        \State $min \gets o.d\_n-o.r$
 
-        \FORALL{$old\_obj$ \textbf{in} $l$}
-            \IF{$o \cap old\_obj = \emptyset$} 
-                \STATE \textbf{return} false
-            \ELSIF{$o \cap old\_obj \neq o$}
-                \STATE {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
+        \ForAll{$old\_obj$ \textbf{in} $l$}
+            \If{$o \cap old\_obj = \emptyset$} 
+                \State \textbf{return} false
+            \ElsIf{$o \cap old\_obj \neq o$}
+                \State {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
                         $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
                         $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
-            \ENDIF
-        \ENDFOR
-        \STATE $\textbf{add } o \textbf{ into } tmp\_list$
-        \IF{$max < min$}
-            \STATE \textbf{return} false
-        \ENDIF
+            \EndIf
+        \EndFor
+        \State $\textbf{add } o \textbf{ into } tmp\_list$
+        \If{$max < min$}
+            \State \textbf{return} false
+        \EndIf
         $p\_cp \gets p$
-        \IF{Recursive$(min, max, n, p\_cp)$}
-            \STATE $p \gets p\_cp$
-            \STATE \textbf{return} true
-        \ELSE
-            \STATE \textbf{return} false
-        \ENDIF
+        \If{Recursive$(min, max, n, p\_cp)$}
+            \State $p \gets p\_cp$
+            \State \textbf{return} true
+        \Else
+            \State \textbf{return} false
+        \EndIf
     \end{algorithmic}
@@
     \begin{algorithmic}[1]
-        \WHILE{$left \leqslant right$}
-            \STATE $mid \gets (left + right)/2$
-            \STATE $max \gets +\infty$
-            \STATE $min \gets -\infty$
-            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
-                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
-                \IF{$P_1.d_{j-1} < max$}
-                    \STATE $max \gets p_1.d_{j-1}$
-                    \STATE $max\_index \gets i$
-                \ENDIF
-                \IF{$P_2.d_{j-1} > min$}
-                    \STATE $min \gets p_2.d_{j-1}$
-                    \STATE $min\_index \gets i$
-                \ENDIF
-            \ENDFOR
-            \IF{$max >= min$}
-                \STATE $p.d_j \gets mid$
-                \IF{Recursive$(min, max, j-1, p)$}
-                    \STATE \textbf{return} true
-                \ENDIF
-            \ENDIF
-            \STATE Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
-            \IF{$P_d.d_j < mid$}
-                \STATE $right \gets mid-1$
-            \ELSIF{$P_d.d_j > mid$}
-                \STATE $left \gets mid+1$
-            \ENDIF
+        \While{$left \leqslant right$}
+            \State $mid \gets (left + right)/2$
+            \State $max \gets +\infty$
+            \State $min \gets -\infty$
+            \For{$i=1$ \textbf{to} $tmp\_list.length$}
+                \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
+                \If{$P_1.d_{j-1} < max$}
+                    \State $max \gets p_1.d_{j-1}$
+                    \State $max\_index \gets i$
+                \EndIf
+                \If{$P_2.d_{j-1} > min$}
+                    \State $min \gets p_2.d_{j-1}$
+                    \State $min\_index \gets i$
+                \EndIf
+            \EndFor
+            \If{$max >= min$}
+                \State $p.d_j \gets mid$
+                \If{Recursive$(min, max, j-1, p)$}
+                    \State \textbf{return} true
+                \EndIf
+            \EndIf
+            \State Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
+            \If{$P_d.d_j < mid$}
+                \State $right \gets mid-1$
+            \ElsIf{$P_d.d_j > mid$}
+                \State $left \gets mid+1$
+            \EndIf
 
-        \ENDWHILE
-        \RETURN false
+        \EndWhile
+        \Return false
     \end{algorithmic}
@@
 \section*{Acknowledgement}
-\begin{table}[]
+\begin{table*}[]
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
     \end{tabular}
-\end{table}
+\end{table*}
 
-\begin{table}[]
+\begin{table*}[]
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
     \end{tabular}
-\end{table}
+\end{table*}
+
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,biblio.bib}
+\end{document}
 

### 2018-10-11 paper.tex
write in method

--- 2018-10-09 paper.tex
@@
 
-Lightweight temporal compression (LTC) is one of the linear estimation method to compress data.
-It is The first-order interpolator with two degrees of freedom(FOI-2DF) which is mentioned in ~\cite{jalaleddine1990ecg}.
-Most of linear estimation method need a predefined parameter which is the error margin (let's call $\epsilon$) in order to guarantee the difference between estimation and original data within a scope.
-
-LTC会记录一个范围，from which 可以找到一条直线，代替original data，并且保证 保证度，或者 distort。 当一个新data来的时候，base data会与 data+/-EPSILON 创建一个 临时的范围， 如果这个范围与 已经记录的范围 存在 交集，那么更新已记录的范围， 如果交集为空，则transmit base data，并将，已经记录的范围的median，and current timesamp - 1 作为 base point的值和timestamp.
-以此循环。
-画个图。
-只需要 constant Memory。
+Lightweight temporal compression (LTC) is one of the linear estimation
+ method to compress data. It is The first-order interpolator with two
+degrees of freedom(FOI-2DF) which is mentioned in ~\cite{jalaleddine1990ecg}.
+Most of linear estimation method need a predefined parameter which is
+the error margin (let's call $\epsilon$) in order to guarantee the
+difference between estimation and original data within a scope.
 
@@
 
-In practice, It's needed to transmit raw data which has multi-parameters to clients e.g.
-Accelerometer, Euler Angle and Magnetometer etc.
-Most of 以前的 paper just force on single dimension sensor data Compression.
-**** .
-So we purpose a method to compress multi-dimensional sensor data named LTC-D.
-It is used as linear estimation method.
-Same as usual estimation compression method,  distance(different) with compressed data from LTC-D and original data would not exceed the predefined error range.
-We need to find line to represent original data, it means the lines
-pass through datas' error range.
-But in stream data, time seires data, it is difficult, because all data do not show in same time plane.
-So this method will mapping all data into one time plane.
-Then for each mapped error range of data, check if there is intersection among them.
-If so means there is a line could represent original data, and vice versa.
+\section{Extension to dimension $n$}
 
-The method as below: assume the stream $i_{th}$ data $D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$ in our Method.
-通常设置 base point之后的一个时间节点作为mapping节点.
-We also need to record the intersect S for find result lines.
-我们确定以 base point 之后的第一个时间节点， 作为mapping的目标节点，再在 The first data D_1 would change into tolerance range R_1.
-我们 set S = R_1.
-For each follow data D_i i>1, mapping D_1 into hat(D_1) = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$, and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}}, j={1...n}$.
-the tolerance range after R_i, intersect with S, if there is overlap, update S = S 交 R_i. If not, the base point would be transmited and select a point in S as base point with timestamp t_{i-1}.
+In practice, It's needed to transmit raw data which has multi-parameters
+to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
+Most of previous paper just force on single dimension sensor
+data Compression. So we purpose a method to compress multi-dimensional
+sensor data named LTC-D. It is used as linear estimation method.
+Same as usual estimation compression method,  distance(different)
+with compressed data from LTC-D and original data would not exceed
+the predefined error range. We need to find line to represent
+original data, it means the lines pass through datas' error range.
+But in stream data, time seires data, it is difficult, because
+all data do not show in same time plane. So this method will
+mapping all data into one time plane. Then for each mapped error
+range of data, check if there is intersection among them. If so means
+there is a line could represent original data, and vice versa.
+
+The method as below: assume the stream $i_{th}$ data
+$D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
+be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
+As usual, the timestamp after basepoint would be set as mapping plane.
+We also need to record the intersect $S$ for find result lines.
+The first data $D_1$ would change into tolerance range $R_1$.
+initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
+into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
+and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
+on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
+with S, if there is overlap, update S = S intersect R_i. If not, the base point
+would be transmited and select a point in S as base point with timestamp $t_{i-1}$.
 
@@
 
-对于 误差范围，会根据EPSILON 改变，也会根据我们设定的 data 与 EPSILON 的 不同类型的距离有关系。
-
-如果使用 Manhattan的话 误差范围 会变成 RequirePackagectangle or cube for 2d and 3d respectively. 就是 EPSILON*sqrt(d)  图
-如果使用 Euclidean的话 误差范围 会变成 disk or ball 分别是 2d, 3d， 保持 EPSILON.图
-
-我们用2d Manhattan 来做例子。 画图
-
-\section{Extension to dimension $n$}
+for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
+If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
+But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
+\todo{maybe need a graphic}
 
@@
 Our code is available at ... (make a clean release!)
-
+/todo{below content is useful? }
 \subsection{Multidimensional LTC with Manhattan distance}
@@
 \subsection{Multidimensional LTC with Euclidean distance}
-In Euclidean distance version, we also map the coming data into same time-stamp.
+In Euclidean distance version, we also map the coming data into same time-stamp $t_1$ the timestamp after base point.
 The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
 In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
-画图；
-写一个3-D的例子，并解释一下 算法
-assume 有一个 3D 的数据 (x,y,z, t_n)， 会被mapping到 (....) with error sphere EPSILON/(t_n - t_1).and check if there is public intersection with list of circle which recorded.
-首先确定x的范围，C_maxX = Min=1.n(c_i.x + E/i), C_minX = Max=1.n(c_i.x - E/i), if C_maxX < C_minX, means there is no public intersection amount those circles.
-after that 使用二分法 mid_x=(C_maxX + C_minX)/2, with x=mid_x computer bounding range of y-axis, 并对y轴继续使用 二分法，在z-axis 上计算 C_minZ and C_maxZ, 如果 C_maxZ > C_minZ 说明 在x=mid_x, y=mid_y 这条线上 存在一个或多个点 在intersection amount those circles.
-so 我们可以确认 确认交集的存在，并且 把点(mid_x, mid_y, mid_z) 保存下来，以便将来更新base point.
-在这个算法中 第一次遍历circle 得到maxX maxY 需要 O(n) 然后 二分法O(lgn) 进入循环, 之后 O(n) 遍历，在二分法 mid_y, 进入循环之后需要O(n) 遍历circle 得到 max_z and min_z 所以 复杂度是 O(n) + O(lgn)*(O(n) + O(lgn)*O(n)) = O(lgn lgn n)
+For instance, in 3D-t, assume we have a the base point $Z = D_0$ and the tolerance range $R_1$ which is a ball as the intersection S.
+we need a list L to record mapped balls from $D_1$ to coming data.
+For each comming data $D_i, i>1$ mapping this data into $t_1$, and add it into list.
+Then the work is check out if all balls intersect, and form a public intersection.
+The method is based on plane sweep and binary search.
+At first, select one parameter, such as x-axis, finding a bounding range of all balls $B_i$ in x-axis.
+suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and $Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$.
+If there is overlap among balls, then the axis of the points inside intersection must located between Min_bound_x and Max_bound_x.
+Using binary search to select mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding with the plane x = mid_x.
+If the get bounding range in y-axis where $Max_bound_y > Min_bound_y$ and using binary search again to find mid_y, It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y, parallels z-axis, could pass through all balls.
+Finally, in z-axis, compute bounding range, and If $Max_bound_z > Min_bound_z$, there must be one or more points inside all balls.
+The problem be solved.
+If the loop of binary search in x-axis overs, then there is no public intersection among balls, and need to transmit and update base point.
+In this method we need O(n*logn*logn) time complexity for binary search in x-axis and y-axis and traversal all balls in z-axis, also O(n) space complexity is needed for maintaining list.
+According this method, it could be extended into N-dimensional data.
+The main idea is to search, dimension by dimension, from a room or plane or line and get intersection point finally.
 
-通过这个 例子 我们可以把 3-D 延伸到 n-D。
-
+/todo{below content is useful? }
 In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
@@
 The pseudo-code in Algorithm 1.
-\begin{algorithm}
-    \caption{whether disks intersect}
-    \begin{flushleft}
-        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
-        \textbf{Output:} $true|false$  is there a intersection\\
-        \textbf{function} isIntersect$(l, d, p)$
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \STATE $tmp_list \gets null$
-        \STATE $max\_x\gets d.x+d.r$
-        \STATE $min\_x\gets d.x-d.r$
-
-        \FORALL{$old\_disk$ \textbf{in} $l$}
-            \IF{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
-                \STATE \textbf{return} false
-            \ELSIF{$d \cap old\_disk \neq d$}
-                \STATE {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
-                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
-                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
-            \ENDIF
-        \ENDFOR
-        \STATE $\textbf{add } d \textbf{ into } tmp\_list$
-        \IF{$max\_x < min\_x$}
-            \STATE \textbf{return} false
-        \ENDIF
-        \WHILE{$min\_x \leqslant max\_x$}
-            \STATE $mid \gets (min\_x + max\_x)/2$
-            \STATE $max\_y \gets +\infty$
-            \STATE $min\_y \gets -\infty$
-            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
-                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
-                \IF{$P_1.y < max\_y$}
-                    \STATE $max\_y \gets p_1.y$
-                    \STATE $max\_index \gets i$
-                \ENDIF
-                \IF{$P_2.y > min\_y$}
-                    \STATE $min\_y \gets p_2.y$
-                    \STATE $min\_index \gets i$
-                \ENDIF
-            \ENDFOR
-            \IF{$max\_y >= min\_y$}
-                \STATE $p.x \gets mid$
-                \STATE $p.y \gets (max\_y+min\_y)/2$
-                \STATE $l \gets tmp\_list$
-                \STATE \textbf{return} true
-            \ENDIF
-            \STATE {Assume $P_d$ is the intersection between line of
-            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
-            , and their common chord}
-            \IF{$P_d.x < mid$}
-                \STATE $max\_y \gets mid-1$
-            \ELSIF{$P_d.x > mid$}
-                \STATE $min\_y \gets mid+1$
-            \ENDIF
-        \ENDWHILE
-        \RETURN false
-    \end{algorithmic}
-\end{algorithm}
 
@@
 The pseudo-code would show like Algorithm 2.
-
-\begin{algorithm}
-    \caption{whether intersect  for n dimension}
-    \begin{flushleft}
-        \textbf{Input:} $l$ - list object, $o$ - object of mapped coming data, $p$ - point will be base point\\
-        \textbf{Output:} $true|false$  is there a intersection\\
-        \textbf{function} isIntersect$(l, o, p)$
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \STATE $tmp_list \gets null$
-        \STATE $max \gets o.d\_n+o.r$
-        \STATE $min \gets o.d\_n-o.r$
-
-        \FORALL{$old\_obj$ \textbf{in} $l$}
-            \IF{$o \cap old\_obj = \emptyset$}
-                \STATE \textbf{return} false
-            \ELSIF{$o \cap old\_obj \neq o$}
-                \STATE {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
-                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
-                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
-            \ENDIF
-        \ENDFOR
-        \STATE $\textbf{add } o \textbf{ into } tmp\_list$
-        \IF{$max < min$}
-            \STATE \textbf{return} false
-        \ENDIF
-        $p\_cp \gets p$
-        \IF{Recursive$(min, max, n, p\_cp)$}
-            \STATE $p \gets p\_cp$
-            \STATE \textbf{return} true
-        \ELSE
-            \STATE \textbf{return} false
-        \ENDIF
-    \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-    \begin{flushleft}
-        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \WHILE{$left \leqslant right$}
-            \STATE $mid \gets (left + right)/2$
-            \STATE $max \gets +\infty$
-            \STATE $min \gets -\infty$
-            \FOR{$i=1$ \textbf{to} $tmp\_list.length$}
-                \STATE $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
-                \IF{$P_1.d_{j-1} < max$}
-                    \STATE $max \gets p_1.d_{j-1}$
-                    \STATE $max\_index \gets i$
-                \ENDIF
-                \IF{$P_2.d_{j-1} > min$}
-                    \STATE $min \gets p_2.d_{j-1}$
-                    \STATE $min\_index \gets i$
-                \ENDIF
-            \ENDFOR
-            \IF{$max >= min$}
-                \STATE $p.d_j \gets mid$
-                \IF{Recursive$(min, max, j-1, p)$}
-                    \STATE \textbf{return} true
-                \ENDIF
-            \ENDIF
-            \STATE Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
-            \IF{$P_d.d_j < mid$}
-                \STATE $right \gets mid-1$
-            \ELSIF{$P_d.d_j > mid$}
-                \STATE $left \gets mid+1$
-            \ENDIF
-
-        \ENDWHILE
-        \RETURN false
-    \end{algorithmic}
-\end{algorithm}
 

### 2018-10-11 paper.tex
write in method

--- 2018-10-10 paper.tex
@@
 Our code is available at ... (make a clean release!)
+In practice, It's needed to transmit raw data which has multi-parameters
+to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
+Most of previous paper just force on single dimension sensor
+data Compression. So we purpose a method to compress multi-dimensional
+sensor data named LTC-D. It is used as linear estimation method.
+Same as usual estimation compression method,  distance(different)
+with compressed data from LTC-D and original data would not exceed
+the predefined error range. We need to find line to represent
+original data, it means the lines pass through datas' error range.
+But in stream data, time seires data, it is difficult, because
+all data do not show in same time plane. So this method will
+mapping all data into one time plane. Then for each mapped error
+range of data, check if there is intersection among them. If so means
+there is a line could represent original data, and vice versa.
 
+The method as below: assume the stream $i_{th}$ data
+$D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
+be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
+As usual, the timestamp after basepoint would be set as mapping plane.
+We also need to record the intersect $S$ for find result lines.
+The first data $D_1$ would change into tolerance range $R_1$.
+initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
+into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
+and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
+on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
+with S, if there is overlap, update S = S intersect R_i. If not, the base point
+would be transmited and select a point in S as base point with timestamp $t_{i-1}$.
+
+\todo{refector}
+At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
+\begin{enumerate}
+  \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
+Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
+  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
+  \item Goto 2.
+  \item output \textit{z} data point.
+  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
+  \item Goto 2.
+  \item After all, output \textit{z} data point and center of bounding box respectively.
+\end{enumerate}
+
+for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
+If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
+But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
+\todo{maybe need a graphic}
+\todo{below content is useful? }
 \subsection{Multidimensional LTC with Manhattan distance}
+
 In practice, Multidimensional LTC is same as implementing LTC in each 
@@
 between tolerance and bounding box.The algorithm is as follows.
-
-\note{not clear about Manhattan distance, in my opinion for each axis the distance less than $EPSILEN/t_i-t_0$ + bounding box length}
 
@@
 \subsection{Multidimensional LTC with Euclidean distance}
-In Euclidean distance version, we also map the coming data into same time-stamp.
-The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
-In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
-In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version.
-After that, we extend the method for n-dimension.
+In Euclidean distance version, we also map the coming data into same 
+time-stamp $t_1$ the timestamp after base point. The difference with 
+Manhattan distance version is that recording overlapping part with
+a post-designed model is difficult, which need retain several arcs in 
+2-dimension, or convex surfaces in 3-dimension. In our method, we will 
+record all tolerance range for every mapped data which come from base 
+data point until coming data point, in order to checking if there is 
+intersection among them. For instance, in 3D-t, assume we have a the 
+base point $Z = D_0$ and the tolerance range $R_1$ which is a ball 
+as the intersection S. we need a list L to record mapped balls 
+from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping 
+this data into $t_1$, and add it into list. Then the work is check out 
+if all balls intersect, and form a public intersection. The method is 
+based on plane sweep and binary search. At first, select one parameter, 
+such as x-axis, finding a bounding range of all balls $B_i$ in x-axis. 
+suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and 
+$Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap 
+among balls, then the axis of the points inside intersection must located 
+between Min_bound_x and Max_bound_x. Using binary search to select 
+mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding 
+with the plane x = mid_x. If the get bounding range in y-axis where 
+$Max_bound_y > Min_bound_y$ and using binary search again to find mid_y, 
+It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y, 
+parallels z-axis, could pass through all balls. Finally, in z-axis, 
+computing bounding range, and If $Max_bound_z > Min_bound_z$, there 
+must be one or more points inside all balls. The problem be solved. 
+If the loop of binary search in x-axis overs, then there is no public 
+intersection among balls, and need to transmit and update base point. 
+In this method we need O(n*logn*logn) time complexity for binary search 
+in x-axis and y-axis and traversal all balls in z-axis, also O(n) space 
+complexity is needed for maintaining list. According this method, 
+it could be extended into N-dimensional data. The main idea is to search, 
+dimension by dimension, from a room or plane or line and get intersection 
+point finally.
+
+\todo{below content is useful? }
+In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
 \begin{itemize}
@@
 The pseudo-code in Algorithm 1.
+
 \begin{algorithm}

### 2018-10-11 paper.tex
result

@@
 
+\todo{ update }
+try using difference data set to measure compression radio, Error 
+and energy usage. The numerical value presented below, is the 
+average value in 5 seconds. The current electric current for Neblina 
+without transmit is ***. we received 4000 data for human running and 
+walking in 200Hz. Because of the limite RAM, for energy test, we only
+could save 400 static data into Neblina. We make 400 data run as a circle.
+For walking, one time swing arm need 1.2 second. Every 400 data must have 1 arm swing.
+change epsilon in order to decrease compression radio, measuring energy consumption.
+
+\todo {running}
+If it's possible to save more static data?
+
 \begin{itemize}

### 2018-10-12 paper.tex
write result first version

--- 2018-10-11 paper.tex
@@
 Our code is available at ... (make a clean release!)
-/todo{below content is useful? }
+\todo{below content is useful? }
 \subsection{Multidimensional LTC with Manhattan distance}
@@
 \subsection{Multidimensional LTC with Euclidean distance}
-In Euclidean distance version, we also map the coming data into same time-stamp $t_1$ the timestamp after base point.
+In Euclidean distance version, we also map the coming data into same time-stamp $t_{1}$ the timestamp after base point.
 The difference with Manhattan distance version is that recording overlapping part with a post-designed model is difficult, which need retain several arcs in 2-dimension, or convex surfaces in 3-dimension.
 In our method, we will record all tolerance range for every mapped data which come from base data point until coming data point, in order to checking if there is intersection among them.
-For instance, in 3D-t, assume we have a the base point $Z = D_0$ and the tolerance range $R_1$ which is a ball as the intersection S.
-we need a list L to record mapped balls from $D_1$ to coming data.
-For each comming data $D_i, i>1$ mapping this data into $t_1$, and add it into list.
+For instance, in 3D-t, assume we have a the base point $Z = D_{0}$ and the tolerance range $R_{1}$ which is a ball as the intersection S.
+we need a list L to record mapped balls from $D_{1}$ to coming data.
+For each comming data $D_i, i>{1}$ mapping this data into $t_{1}$, and add it into list.
 Then the work is check out if all balls intersect, and form a public intersection.
@@
 
-/todo{below content is useful? }
+\todo{below content is useful? }
 In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
@@
 
-\subsection{Experiment 1: energy reduction on the Neblina}
+\subsection{Experiment 2: energy reduction on the Neblina}
 
@@
 But in 200Hz sampling rate. The electric before and after compression are 3.5 and 2.9 respectively. The running time of Neblina would be extended about 5.9 hours/
+
+The experiment in Neblina, we weared Neblina on right wrist and
+collected walking data and running data. 4000 data set was collected
+from Neblina in 200Hz sampling rate. Since arm swing appearance
+repeated, we just take 1000 data from it, and make data as cycle of
+these 1000 data. Because 1000 data is produced in 5 seconds with 200Hz
+sampling rate, we measured average energy usage in 5 seconds.
+
+At first, we measured base energy usage in Neblina. The energy usage
+without transmision is 2.515 mAh. It is 3.472mAh with transmision but
+no compression method. From table 3 and table 4, The MaxError don't exceed EPSILON
+and EPSILON*sqrt(Dimension) with LTC-Euclidean and LTC-Manhatan respectively.
+And the average electric current increase with compression radio decreasing.
+Energy usage by using both compression method are smaller than transmit
+without compression. From the result, the activities which has low frequency
+would gain larger compression radio.
+
+The purpose of the compression method is compressing the number of
+data needed to transmited, in order to extend Neblna's life cycle
+by decreasing energy consumption. From table 3, for not vigorous exercise
+such walking, with EPSILON equals 100, the life cycle could be extend
+3(10\%)and 9(31\%) hours with LTC-Euclidean and LTC-Manhattan respectively.
+And vigorous exercise, with same condition, it extends 5.7(19.7\%)
+and 4.8(16.7\%) hours. So LTC-Euclidean and LTC-Manhattan are useful
+to save devices Energy. At same time, The fidelity is guaranteed.
 
@@
 
+\begin{table}[]
+\begin{tabular}{lllllll}
+DataSet           & \multicolumn{6}{l}{walking}                                   \\
+Distance          & \multicolumn{3}{l}{Manhattan} & \multicolumn{3}{l}{Euclidean} \\
+Epsilon           & 100       & 20      & 10      & 100       & 20      & 10      \\
+Max Error         & 158.793   & 31.828  & 16.763  & 153.141   & 31.763  & 15.898  \\
+Compression Radio & 88.9\%    & 66.4\%  & 45.5\%  & 68.6\%    & 25.5\%  & 9.5\%   \\
+Energy Usage      & 2.642     & 2.787   & 3.020   & 2.879     & 3.221   & 3.383
+\end{tabular}
+\end{table}
+
+\begin{table}[]
+\begin{tabular}{lllllll}
+DataSet           & \multicolumn{6}{l}{running}                                   \\
+Distance          & \multicolumn{3}{l}{Manhattan} & \multicolumn{3}{l}{Euclidean} \\
+Epsilon           & 100      & 20       & 10      & 100      & 20       & 10      \\
+Max Error         & 99.995   & 19.984   & 9.979   & 99.995   & 19.989   & 9.959   \\
+Compression Radio & 87.6\%   & 63.3\%   & 37.2\%  & 64.4\%   & 19.8\%   & 5.7\%   \\
+Energy Usage      & 3.098    & 3.020    & 3.134   & 2.952    & 3.320    & 3.393
+\end{tabular}
+\end{table}
+
 \bibliographystyle{IEEEtran}

### 2018-10-15 paper.tex
rewrite section 4

@@
 Our code is available at ... (make a clean release!)
-In practice, It's needed to transmit raw data which has multi-parameters
-to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
-Most of previous paper just force on single dimension sensor
-data Compression. So we purpose a method to compress multi-dimensional
-sensor data named LTC-D. It is used as linear estimation method.
-Same as usual estimation compression method,  distance(different)
-with compressed data from LTC-D and original data would not exceed
-the predefined error range. We need to find line to represent
-original data, it means the lines pass through datas' error range.
-But in stream data, time seires data, it is difficult, because
-all data do not show in same time plane. So this method will
-mapping all data into one time plane. Then for each mapped error
-range of data, check if there is intersection among them. If so means
-there is a line could represent original data, and vice versa.
 
-The method as below: assume the stream $i_{th}$ data
-$D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
-be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
-As usual, the timestamp after basepoint would be set as mapping plane.
-We also need to record the intersect $S$ for find result lines.
-The first data $D_1$ would change into tolerance range $R_1$.
-initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
-into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
-and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
-on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
-with S, if there is overlap, update S = S intersect R_i. If not, the base point
-would be transmited and select a point in S as base point with timestamp $t_{i-1}$.
+As reference above, the norm selection is importance. In this section,
+we show the implementation of infinity norm and Euclidean norm.
 
-\todo{refector}
-At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
+%~ In practice, It's needed to transmit raw data which has multi-parameters
+%~ to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
+%~ Most of previous paper just force on single dimension sensor
+%~ data Compression. So we purpose a method to compress multi-dimensional
+%~ sensor data named LTC-D. It is used as linear estimation method.
+%~ Same as usual estimation compression method,  distance(different)
+%~ with compressed data from LTC-D and original data would not exceed
+%~ the predefined error range. We need to find line to represent
+%~ original data, it means the lines pass through datas' error range.
+%~ But in stream data, time seires data, it is difficult, because
+%~ all data do not show in same time plane. So this method will
+%~ mapping all data into one time plane. Then for each mapped error
+%~ range of data, check if there is intersection among them. If so means
+%~ there is a line could represent original data, and vice versa.
+\subsection{Multidimensional LTC with Manhattan distance}
+In section 2, we can know that the repersentation of intersection
+is a rectangular cuboid. So only one bounding box with n-dimansional
+is needed to represent the intersection. Assume a bounding box
+$\mathcal{BOX}_{m-1} = \bigcap_{j=1}^{m-1}{\mathcal{B}_{m-1}}$ which
+has Upper bound $U_i$ and lower Bound $L_i$ for each dimension
+$i$. So the fomular (1) in $6_{th}$ line of Algorithm 2 would
+be changed to $\mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m} \neq \O $. The Bounding box
+would be updated when this formular return true.
+Otherwise return false.
 \begin{enumerate}
-  \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
-Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
-  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
-  \item Goto 2.
-  \item output \textit{z} data point.
-  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
-  \item Goto 2.
-  \item After all, output \textit{z} data point and center of bounding box respectively.
+    \item Initialization: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
+    \item For the each $m_{th}$ data $(u_m^k, y_m^k)$ with diminsion $n$,
+            defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
+            \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
+    \item The $\mathcal{B}_{m}$ should be a ractangular cube with center
+            $\frac{v_1}{v_j}z_m$ and weight $\frac{v_1}{v_j}\epsilon$.
+    \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_j}x_{mi}+
+            \frac{v_1}{v_j}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_j}x_{mi}-\frac{v_1}{v_j}\epsilon$, return False.
+    \item Otherwise, the intersection do not be empty. Updating
+            the Bounding box $\mathcal{BOX}_m = \mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m}$. For
+            each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_j}x_{mi}+
+            \frac{v_1}{v_j}\epsilon})$, and $L_i = max(L_i , \frac{v_1}{v_j}x_{mi}-\frac{v_1}{v_j}\epsilon})$. Return True.
 \end{enumerate}
 
-for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
-If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
-But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
+% The method as below: assume the stream $i_{th}$ data
+% $D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
+% be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
+% As usual, the timestamp after basepoint would be set as mapping plane.
+% We also need to record the intersect $S$ for find result lines.
+% The first data $D_1$ would change into tolerance range $R_1$.
+% initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
+% into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
+% and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
+% on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
+% with S, if there is overlap, update S = S intersect R_i. If not, the base point
+% would be transmited and select a point in S as base point with timestamp $t_{i-1}$.
+
+% \todo{refector}
+% At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
+% \begin{enumerate}
+%   \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
+Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
+%   \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+%   \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
+%   \item Goto 2.
+%   \item output \textit{z} data point.
+%   \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
+%   \item Goto 2.
+%   \item After all, output \textit{z} data point and center of bounding box respectively.
+% \end{enumerate}
+
+According the Implement, the infinity norm boils down to apply 1D LTC algorithm in each dimension respectively.
+Since, the intersection would be rectangle in 2D and cube in 3D, the corresponding max errors are $\frac{\epsilon}{\sqrt{2}}$ and $\frac{\epsilon}{\sqrt{3}}$.
+As we mentioned in Section 2, the infinity norm is more 'tolerant' than Euclidean norm.
+The max error between original data and reconstructed data certainly not greater than $\frac{\epsilon}{\sqrt{n}}$ where $n$ is dimension of data.
+% for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
+% If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
+% But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
 \todo{maybe need a graphic}
-\todo{below content is useful? }
-\subsection{Multidimensional LTC with Manhattan distance}
 
-In practice, Multidimensional LTC is same as implementing LTC in each
-parameter respectively. But we did some changes in our method. Assume
-$(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with
-n-dimension, and a base data point Z  $(z_{1}, z_{2}, ...,
-z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming
-data to $t_1$ time-stamp and create a bounding box for recording
-overlapping range which includes upper and lower bound for each
-dimension base on $t_1$. cause the time different between two adjacent
-data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j +
-\frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-After that updating tolerance range by adding designed error margin
-which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}},
-j={1...n}$ with Manhattan distance. checking if there is overlap
-between tolerance and bounding box.The algorithm is as follows.
+% In practice, Multidimensional LTC is same as implementing LTC in each
+% parameter respectively. But we did some changes in our method. Assume
+% $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with
+% n-dimension, and a base data point Z  $(z_{1}, z_{2}, ...,
+% z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming
+% data to $t_1$ time-stamp and create a bounding box for recording
+% overlapping range which includes upper and lower bound for each
+% dimension base on $t_1$. cause the time different between two adjacent
+% data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j +
+% \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+% After that updating tolerance range by adding designed error margin
+% which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}},
+% j={1...n}$ with Manhattan distance. checking if there is overlap
+% between tolerance and bounding box.The algorithm is as follows.
 
-At beginning of the algorithm, we need a base point (which we will call
-\textit{z}) and bounding box which has upper and lower bound for each
-parameter respectively.Then start the algorithm.
-\begin{enumerate}
-  \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
+% At beginning of the algorithm, we need a base point (which we will call
+% \textit{z}) and bounding box which has upper and lower bound for each
+% parameter respectively.Then start the algorithm.
+% \begin{enumerate}
+%   \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
 Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
-  \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-  \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
-  \item Goto 2.
-  \item output \textit{z} data point.
-  \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
-  \item Goto 2.
-  \item After all, output \textit{z} data point and center of bounding box respectively.
-\end{enumerate}
+%   \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
+%   \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
+%   \item Goto 2.
+%   \item output \textit{z} data point.
+%   \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
+%   \item Goto 2.
+%   \item After all, output \textit{z} data point and center of bounding box respectively.
+% \end{enumerate}
 

### 2018-10-16 paper.tex
rewrite infinity norm and euclidean norm without recursive pseudocode

@@
 In section 2, we can know that the repersentation of intersection
-is a rectangular cuboid. So only one bounding box with n-dimansional
+is a rectangular cuboid. So only one bounding box with n-dimensional
 is needed to represent the intersection. Assume a bounding box
@@
     \item Initialization: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
-    \item For the each $m_{th}$ data $(u_m^k, y_m^k)$ with diminsion $n$,
+    \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
             defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
@@
     \item The $\mathcal{B}_{m}$ should be a ractangular cube with center
-            $\frac{v_1}{v_j}z_m$ and weight $\frac{v_1}{v_j}\epsilon$.
-    \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_j}x_{mi}+
-            \frac{v_1}{v_j}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_j}x_{mi}-\frac{v_1}{v_j}\epsilon$, return False.
+            $\frac{v_1}{v_m}z_m$ and weight $\frac{v_1}{v_m}\epsilon$.
+    \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_m}x_{mi}+
+            \frac{v_1}{v_m}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon$, return False.
     \item Otherwise, the intersection do not be empty. Updating
             the Bounding box $\mathcal{BOX}_m = \mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m}$. For
-            each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_j}x_{mi}+
-            \frac{v_1}{v_j}\epsilon})$, and $L_i = max(L_i , \frac{v_1}{v_j}x_{mi}-\frac{v_1}{v_j}\epsilon})$. Return True.
+            each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_m}x_{mi}+
+            \frac{v_1}{v_m}\epsilon)$, and $L_i = max(L_i , \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon)$. Return True.
 \end{enumerate}
@@
 \subsection{Multidimensional LTC with Euclidean distance}
-In Euclidean distance version, we also map the coming data into same
-time-stamp $t_1$ the timestamp after base point. The difference with
-Manhattan distance version is that recording overlapping part with
-a post-designed model is difficult, which need retain several arcs in
-2-dimension, or convex surfaces in 3-dimension. In our method, we will
-record all tolerance range for every mapped data which come from base
-data point until coming data point, in order to checking if there is
-intersection among them. For instance, in 3D-t, assume we have a the
-base point $Z = D_0$ and the tolerance range $R_1$ which is a ball
-as the intersection S. we need a list L to record mapped balls
-from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping
-this data into $t_1$, and add it into list. Then the work is check out
-if all balls intersect, and form a public intersection. The method is
-based on plane sweep and binary search. At first, select one parameter,
-such as x-axis, finding a bounding range of all balls $B_i$ in x-axis.
-suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and
-$Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap
-among balls, then the axis of the points inside intersection must located
-between Min_bound_x and Max_bound_x. Using binary search to select
-mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding
-with the plane x = mid_x. If the get bounding range in y-axis where
-$Max_bound_y > Min_bound_y$ and using binary search again to find mid_y,
-It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y,
-parallels z-axis, could pass through all balls. Finally, in z-axis,
-computing bounding range, and If $Max_bound_z > Min_bound_z$, there
-must be one or more points inside all balls. The problem be solved.
-If the loop of binary search in x-axis overs, then there is no public
-intersection among balls, and need to transmit and update base point.
-In this method we need O(n*logn*logn) time complexity for binary search
-in x-axis and y-axis and traversal all balls in z-axis, also O(n) space
-complexity is needed for maintaining list. According this method,
-it could be extended into N-dimensional data. The main idea is to search,
-dimension by dimension, from a room or plane or line and get intersection
-point finally.
-
-\todo{below content is useful? }
-In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
-\begin{itemize}
-\item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk.
-After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data.
-Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
-\item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis.
-So In 3-dimension whether \textit{n} balls intersect need to be check.
-\end{itemize}
-
-At first, let us solve the \textit{n} disks intersect.
-We use a algorithm which is based on plane sweep and dichotomy.
-Assume a disk include center$(x,y)$ and radius $r$.
-The pseudo-code in Algorithm 1.
+In Euclidea norm, the representation of intersection is
+volume. There is no specific model to record repersentation
+with updating, so a list to save all balls $\mathcal{B}_j, 1\leqslant{j}\leqslant{m}$
+is needed. In order to test weather a set of balls intersect,
+the Helly's theorem could work, but the complexity of
+this method is too high to work with embeded, low-power
+systems which has limited CPU and RAM resource. So we
+implement Euclidean norm by using a method which based
+on plane sweep and binary search.
+Assume the list of balls $S_{m-1}$ contains balls from $\mathcal{B}_1$ to $\mathcal{B}_{m-1}$, and an temporary data point $output$ used for updated origin $(\tau^k, \xi^k)$.
+From the formula (1) in Section 3, the $(\mathcal{B}_j)_{j \in \llbracket 1, {m-1} \rrbracket}$ is a sequence of decreasing radius, so the larger balls that includes new coming ball $\mathcal{B}_{m-1}$ could be reomved from list $S_{m-1}$ so that reducing processing complexity of method.
+Therefore the list $S_{m-1}$ may not includes $m-1$ balls.
+Assume each $\Hat{\mathcal{B}} \in S$ which has corresponding center $\Hat{z}$ and radius $\Hat{\epsilon}$.
+Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$, and for each data $(u_m^k, y_m^k)$ with diminsion $n$, defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m = \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
+The $\mathcal{B}_{m}$ should be one n-ball with center $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$.
+The method is written in Algorithm~\ref{algo:isThereIntersection}.
 
 \begin{algorithm}
-    \caption{whether disks intersect}
     \begin{flushleft}
-        \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
-        \textbf{Output:} $true|false$  is there a intersection\\
-        \textbf{function} isIntersect$(l, d, p)$
+        \textbf{Input:} $S$, $\mathcal{B}_m$, $output$ \\
+        \textbf{Output:} $true|false$\\
     \end{flushleft}
     \begin{algorithmic}[1]
-        \State $tmp_list \gets null$
-        \State $max\_x\gets d.x+d.r$
-        \State $min\_x\gets d.x-d.r$
-
-        \ForAll{$old\_disk$ \textbf{in} $l$}
-            \If{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
+        \State d = n \Comment{dimension index}
+        \State $max_d = \frac{v_1}{v_m}(x_d + \epsilon)$
+        \State $min_d = \frac{v_1}{v_m}(x_d - \epsilon)$
+        \ForAll{$\Hat{\mathcal{B}}$ \textbf{in} $S$}
+            \If{$\Hat{\mathcal{B}} \bigcap \mathcal{B}_m = $ \O }
                 \State \textbf{return} false
-            \ElsIf{$d \cap old\_disk \neq d$}
-                \State {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
-                        $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
-                        $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
+            \ElsIf{$\mathcal{B}_m \bigcap \Hat{\mathcal{B}}  = \mathcal{B}_m $}
+                \State remove $\Hat{\mathcal{B}}$ from $S$
+                \State \textbf{continue}\\
+            $max_d = \min(max_d, \Hat{x_d} + \Hat{\epsilon}$)\\
+            $min_d = \max(min_d, \Hat{x_d} - \Hat{\epsilon}$)
             \EndIf
         \EndFor
-        \State $\textbf{add } d \textbf{ into } tmp\_list$
-        \If{$max\_x < min\_x$}
+        \State $\textbf{add } \mathcal{B}_m \textbf{ into } S$
+        \If{$max_d < min_d$}
             \State \textbf{return} false
         \EndIf
-        \While{$min\_x \leqslant max\_x$}
-            \State $mid \gets (min\_x + max\_x)/2$
-            \State $max\_y \gets +\infty$
-            \State $min\_y \gets -\infty$
-            \For{$i=1$ \textbf{to} $tmp\_list.length$}
-                \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
-                \If{$P_1.y < max\_y$}
-                    \State $max\_y \gets p_1.y$
-                    \State $max\_index \gets i$
-                \EndIf
-                \If{$P_2.y > min\_y$}
-                    \State $min\_y \gets p_2.y$
-                    \State $min\_index \gets i$
-                \EndIf
-            \EndFor
-            \If{$max\_y >= min\_y$}
-                \State $p.x \gets mid$
-                \State $p.y \gets (max\_y+min\_y)/2$
-                \State $l \gets tmp\_list$
-                \State \textbf{return} true
-            \EndIf
-            \State {Assume $P_d$ is the intersection between line of
-            centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
-            , and their common chord}
-            \If{$P_d.x < mid$}
-                \State $max\_y \gets mid-1$
-            \ElsIf{$P_d.x > mid$}
-                \State $min\_y \gets mid+1$
-            \EndIf
-        \EndWhile
-        \Return false
-    \end{algorithmic}
-\end{algorithm}
-
-The main idea of the algorithm is, remove the bigger disk who contains mapped coming disk.
-It maybe increase Computational efficiency in the rest of algorithm, cause mapped coming disk is the smallest one than all in list of disks.
-Then we make a bounding range for x-axis and select a x-value $mid$ by using dichotomy method in order to calculate if a point $(y, mid)$ is included all disks.
-The complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
-
-For 3-dimension, assume data point like $(x, y, z)$ also need time-stamp t, we can also use above method by selecting $x$ and $y$ with dichotomy method and then check if there are points $(mid\_x, mid\_y, z)$ included by all balls.
-It needs $O(\log^2\epsilon)$ to determine $mid\_x, mid\_y$, and $O(n)$ to traverse all balls in list and calculate $z$.
-So 3-dimensional method need $O(n \log^2\epsilon)$ totally.
-If we extend this idea for n-dimension, suppose that the coming data is $(x_1,x_2,...,x_n)$ and the mapped data is a object with center $(d_1,d_2,...d_n)$ and radius $r$.
-The pseudo-code would show like Algorithm 2.
-
-\begin{algorithm}
-    \caption{whether intersect  for n dimension}
-    \begin{flushleft}
-        \textbf{Input:} $l$ - list object, $o$ - object of mapped coming data, $p$ - point will be base point\\
-        \textbf{Output:} $true|false$  is there a intersection\\
-        \textbf{function} isIntersect$(l, o, p)$
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \State $tmp_list \gets null$
-        \State $max \gets o.d\_n+o.r$
-        \State $min \gets o.d\_n-o.r$
-
-        \ForAll{$old\_obj$ \textbf{in} $l$}
-            \If{$o \cap old\_obj = \emptyset$}
-                \State \textbf{return} false
-            \ElsIf{$o \cap old\_obj \neq o$}
-                \State {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
-                        $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
-                        $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
-            \EndIf
-        \EndFor
-        \State $\textbf{add } o \textbf{ into } tmp\_list$
-        \If{$max < min$}
-            \State \textbf{return} false
-        \EndIf
-        $p\_cp \gets p$
-        \If{Recursive$(min, max, n, p\_cp)$}
-            \State $p \gets p\_cp$
+        \State temp\_output = output \Comment{used for next operation}
+        \If{Recursive$(min_d, max_d, n, p\_cp)$}
+            \State $output = temp\_output$
             \State \textbf{return} true
@@
     \end{algorithmic}
+    \caption{isThereIntersection}
+    \label{algo:isThereIntersection}
 \end{algorithm}
+
+% \begin{enumerate}
+%     \item Initialzation: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
+%     \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
+%             defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
+%             \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
+%     \item The $\mathcal{B}_{m}$ should be one n-ball with center
+%             $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$.
+%     \item For each ball $\hat{\mathcal{B}}$ in list $S$, if $\hat{\mathcal{B}} \bigcap \mathcal{B}_m = \O$, return False. Else if
+%     $\mathcal{B}_m\subset\hat{\mathcal{B}}$, remove $\hat{\mathcal{B}}$ from list $S$.
+%     \item Select parameter p = n (which is ball's dimension), define $Max_{(p=n)} = \min_{j=1}^{S.length}{(\frac{v_1}{v_j}z_{(p=n)} + \frac{v_1}{v_j}\epsilon)}$, and $Min_{(p=n)} = \max_{j=1}^{S.length}{(\frac{v_1}{v_j}z_{(p=n)} - \frac{v_1}{v_j}\epsilon)}$.
+If $Max_{(p=n)} < Min_{(p=n)}$, return False.
+%     \item Use binary search to select $mid_{(p=n)} = (Min_{(p=n)} + Max_{(p=n)})/2$
+% \end{enumerate}
+
+% In Euclidean distance version, we also map the coming data into same
+% time-stamp $t_1$ the timestamp after base point. The difference with
+% Manhattan distance version is that recording overlapping part with
+% a post-designed model is difficult, which need retain several arcs in
+% 2-dimension, or convex surfaces in 3-dimension. In our method, we will
+% record all tolerance range for every mapped data which come from base
+% data point until coming data point, in order to checking if there is
+% intersection among them. For instance, in 3D-t, assume we have a the
+% base point $Z = D_0$ and the tolerance range $R_1$ which is a ball
+% as the intersection S. we need a list L to record mapped balls
+% from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping
+% this data into $t_1$, and add it into list. Then the work is check out
+% if all balls intersect, and form a public intersection.
+% The method is based on plane sweep and binary search. At first, select one parameter,
+% such as x-axis, finding a bounding range of all balls $B_i$ in x-axis.
+% suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and
+% $Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap
+% among balls, then the axis of the points inside intersection must located
+% between Min_bound_x and Max_bound_x.
+In the method, selecting dimension(n as default in our method) to calculate max point value and min point value of all n-balls in this dimension.
+If the max value bigger than min value, then there is no intersection.
+After that.
+In Recursive function Algorithm~\ref{algo:recursive}, using binary search select
+median $mid_d$ of $max_d$ and $min_d$ in order to find bound range of dimension d-1 ($max_{d-1}$, $min_{d-1}$) over the plane $x_d = max_d$.
+If bound range of dimension $d-1$ is not empty, continue calling function \textbf{Recursive}($min_{d-1}$, $min_{d-1}$, $d-1$, $temp\_output$).
+Recursively calling this function, until getting result.
+\todo{add recursive pseudo-code}
+% Using binary search to select
+% mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding
+% with the plane x = mid_x. If the get bounding range in y-axis where
+% $Max_bound_y > Min_bound_y$ and using binary search again to find mid_y,
+% It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y,
+% parallels z-axis, could pass through all balls. Finally, in z-axis,
+% computing bounding range, and If $Max_bound_z > Min_bound_z$, there
+% must be one or more points inside all balls. The problem be solved.
+% If the loop of binary search in x-axis overs, then there is no public
+% intersection among balls, and need to transmit and update base point.
+% In this method we need O(n*logn*logn) time complexity for binary search
+% in x-axis and y-axis and traversal all balls in z-axis, also O(n) space
+% complexity is needed for maintaining list. According this method,
+% it could be extended into N-dimensional data. The main idea is to search,
+% dimension by dimension, from a room or plane or line and get intersection
+% point finally.
+
+% \todo{below content is useful? }
+% In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
+% \begin{itemize}
+% \item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk.
+After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data.
+Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
+% \item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis.
+So In 3-dimension whether \textit{n} balls intersect need to be check.
+% \end{itemize}
+
+% At first, let us solve the \textit{n} disks intersect.
+We use a algorithm which is based on plane sweep and dichotomy.
+Assume a disk include center$(x,y)$ and radius $r$.
+The pseudo-code in Algorithm 1.
+
+% \begin{algorithm}
+%     \caption{whether disks intersect}
+%     \begin{flushleft}
+%         \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
+%         \textbf{Output:} $true|false$  is there a intersection\\
+%         \textbf{function} isIntersect$(l, d, p)$
+%     \end{flushleft}
+%     \begin{algorithmic}[1]
+%         \State $tmp_list \gets null$
+%         \State $max\_x\gets d.x+d.r$
+%         \State $min\_x\gets d.x-d.r$
+
+%         \ForAll{$old\_disk$ \textbf{in} $l$}
+%             \If{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
+%                 \State \textbf{return} false
+%             \ElsIf{$d \cap old\_disk \neq d$}
+%                 \State {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
+%                         $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
+%                         $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
+%             \EndIf
+%         \EndFor
+%         \State $\textbf{add } d \textbf{ into } tmp\_list$
+%         \If{$max\_x < min\_x$}
+%             \State \textbf{return} false
+%         \EndIf
+%         \While{$min\_x \leqslant max\_x$}
+%             \State $mid \gets (min\_x + max\_x)/2$
+%             \State $max\_y \gets +\infty$
+%             \State $min\_y \gets -\infty$
+%             \For{$i=1$ \textbf{to} $tmp\_list.length$}
+%                 \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
+%                 \If{$P_1.y < max\_y$}
+%                     \State $max\_y \gets p_1.y$
+%                     \State $max\_index \gets i$
+%                 \EndIf
+%                 \If{$P_2.y > min\_y$}
+%                     \State $min\_y \gets p_2.y$
+%                     \State $min\_index \gets i$
+%                 \EndIf
+%             \EndFor
+%             \If{$max\_y >= min\_y$}
+%                 \State $p.x \gets mid$
+%                 \State $p.y \gets (max\_y+min\_y)/2$
+%                 \State $l \gets tmp\_list$
+%                 \State \textbf{return} true
+%             \EndIf
+%             \State {Assume $P_d$ is the intersection between line of
+%             centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
+%             , and their common chord}
+%             \If{$P_d.x < mid$}
+%                 \State $max\_y \gets mid-1$
+%             \ElsIf{$P_d.x > mid$}
+%                 \State $min\_y \gets mid+1$
+%             \EndIf
+%         \EndWhile
+%         \Return false
+%     \end{algorithmic}
+% \end{algorithm}
+
+% The main idea of the algorithm is, remove the bigger disk who contains mapped coming disk.
+It maybe increase Computational efficiency in the rest of algorithm, cause mapped coming disk is the smallest one than all in list of disks.
+Then we make a bounding range for x-axis and select a x-value $mid$ by using dichotomy method in order to calculate if a point $(y, mid)$ is included all disks.
+In 2-dimension Euclidean norm, the complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
+In 3-dimension, It needs $O(\log^2\epsilon)$ to determine $mid\_3, mid\_2$, and $O(n)$ to traverse all balls in list and calculate bounding range of dimension d=1.
+So 3-dimensional method need $O(n \log^2\epsilon)$ totally.
+If we extend this idea for n-dimension, the complexiy of this method is $O(n \log^{n}\epsilon)$ where n is the number of dimension.
+
+% \begin{algorithm}
+%     \begin{flushleft}
+%         \textbf{Input:} $S$, $\mathcal{B}_m$, $output$
+%         \textbf{Output:} $true|false$  is there a intersection\\
+%         \textbf{function} isIntersect$(l, o, p)$
+%     \end{flushleft}
+%     \begin{algorithmic}[1]
+%         \State $tmp_list \gets null$
+%         \State $max \gets o.d\_n+o.r$
+%         \State $min \gets o.d\_n-o.r$
+
+%         \ForAll{$old\_obj$ \textbf{in} $l$}
+%             \If{$o \cap old\_obj = \emptyset$}
+%                 \State \textbf{return} false
+%             \ElsIf{$o \cap old\_obj \neq o$}
+%                 \State {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
+%                         $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
+%                         $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
+%             \EndIf
+%         \EndFor
+%         \State $\textbf{add } o \textbf{ into } tmp\_list$
+%         \If{$max < min$}
+%             \State \textbf{return} false
+%         \EndIf
+%         $p\_cp \gets p$
+%         \If{Recursive$(min, max, n, p\_cp)$}
+%             \State $p \gets p\_cp$
+%             \State \textbf{return} true
+%         \Else
+%             \State \textbf{return} false
+%         \EndIf
+%     \end{algorithmic}
+%     \caption{isThereIntersection}
+%     \label{algo:isThereIntersection}
+% \end{algorithm}
 
@@
 \begin{table*}[]
+    \caption{}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
 \begin{table*}[]
+    \caption{Table}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
 \begin{table}[]
-\begin{tabular}{lllllll}
-DataSet           & \multicolumn{6}{l}{walking}                                   \\
-Distance          & \multicolumn{3}{l}{Manhattan} & \multicolumn{3}{l}{Euclidean} \\
-Epsilon           & 100       & 20      & 10      & 100       & 20      & 10      \\
-Max Error         & 158.793   & 31.828  & 16.763  & 153.141   & 31.763  & 15.898  \\
-Compression Radio & 88.9\%    & 66.4\%  & 45.5\%  & 68.6\%    & 25.5\%  & 9.5\%   \\
-Energy Usage      & 2.642     & 2.787   & 3.020   & 2.879     & 3.221   & 3.383
+    \caption{}
+    \begin{tabular}{|l|l|l|l|l|l|l|}
+    \hline
+    DataSet           & \multicolumn{6}{l|}{walking}                                   \\\hline
+    Distance          & \multicolumn{3}{l|}{Manhattan} & \multicolumn{3}{l|}{Euclidean} \\\hline
+    Epsilon           & 100       & 20      & 10      & 100       & 20      & 10      \\\hline
+    Max Error         & 158.793   & 31.828  & 16.763  & 153.141   & 31.763  & 15.898  \\\hline
+    Compression Radio & 88.9\%    & 66.4\%  & 45.5\%  & 68.6\%    & 25.5\%  & 9.5\%   \\\hline
+    Energy Usage      & 2.642     & 2.787   & 3.020   & 2.879     & 3.221   & 3.383   \\\hline
     \end{tabular}
@@
 \begin{table}[]
-\begin{tabular}{lllllll}
-DataSet           & \multicolumn{6}{l}{running}                                   \\
-Distance          & \multicolumn{3}{l}{Manhattan} & \multicolumn{3}{l}{Euclidean} \\
-Epsilon           & 100      & 20       & 10      & 100      & 20       & 10      \\
-Max Error         & 99.995   & 19.984   & 9.979   & 99.995   & 19.989   & 9.959   \\
-Compression Radio & 87.6\%   & 63.3\%   & 37.2\%  & 64.4\%   & 19.8\%   & 5.7\%   \\
-Energy Usage      & 3.098    & 3.020    & 3.134   & 2.952    & 3.320    & 3.393
+    \caption{}
+    \begin{tabular}{|l|l|l|l|l|l|l|}
+    \hline
+    DataSet           & \multicolumn{6}{l|}{running}                                   \\\hline
+    Distance          & \multicolumn{3}{l|}{Manhattan} & \multicolumn{3}{l|}{Euclidean} \\\hline
+    Epsilon           & 100      & 20       & 10      & 100      & 20       & 10      \\\hline
+    Max Error         & 99.995   & 19.984   & 9.979   & 99.995   & 19.989   & 9.959   \\\hline
+    Compression Radio & 87.6\%   & 63.3\%   & 37.2\%  & 64.4\%   & 19.8\%   & 5.7\%   \\\hline
+    Energy Usage      & 3.098    & 3.020    & 3.134   & 2.952    & 3.320    & 3.393   \\\hline
     \end{tabular}

### 2018-10-16 paper.tex
update result

@@
 \subsection{Experiment 1: Pilot tests on Computer}
+In this experiment, in order to compare the performance in different norm, different EPSILON and different dataset.
+We collected 2 data set from Neblina, 5-times bicep curl data and Mohammad Lateral bicep curl.
 \begin{itemize}
@@
     \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
-    \item Result: Result shows in table.
-    \item Conclusion: From the table, The LTC-Manhattan has higher compression radio.
-But LTC-Euclidean make sure the Max Error between reconstructed data and original data under EPSILON.Compression ratios would decrease with changing EPSILON smaller.
+    \item Result: From the table 1 and table 2, The Max Error, Compression Radio and Time usage in both norm decrease when EPSILON become smaller.
+Comparing with different norm and same EPSILON, the infinity no, and few ndeed has more 'tolerance'.
+But when comparing using Infinity with $\epsilon=100/\sqrt{n}$, where n is number of dimension, to make sure the max error would not greater than 100, and Euclidean with $\epsilon$=100, the Euclidean norm has better compression radio.
+Although Infinity norm makes Max error larger, but it has less running time, and few fixed Memory usage according number of dimension.
+The Memory Usage of Euclidea is not fixed, because it need save $\mathcal{B}_i, i\subset\llbracket 1, m \rrbracket$ after origin $(u_0^k, y_0^k)$, costing lots of Memory.
+From the table 1 and 2, the Compression Radio in second data set is pretty better than first data set, because Mohammad Lateral bicep has more data than first dataset about 67.5 times.
+It is pointless to consider the different compression radio in this situation.
+
+    \item Conclusion: The infinity norm has higher compression radio than Euclidean norm with same $\epsilon$, and uses less running time and little memory.
+But Euclidean makes sure the Max Error between reconstructed data and original data under EPSILON.
+Both of norm would has lower Compression ratios when $\epsilon$ becomes smaller.
 \end{itemize}
@@
 \subsection{Experiment 2: energy reduction on the Neblina}
+The experiment in Neblina V2 module~\cite{Neblina}, which is a module integrating multiple sensors. Its current System-on-Chip (SoC) radio is the Nordic Semiconductor nRF52832, and it has 64KB RAM.
 
-The capacity of battery in Neblina is 100mAh, and the battery usage would not change too much, because it contans others fusion method which will running when turning on the Neblina.
-In 50Hz sensor sampling rate, the average usage electric current for transmit accelerometers data is 2.0mA. It means Neblina could tranmit accelerometers data constantly in 100/2.0=50 hours.
-After compressed by LTC-Manhattan method, the average usage electric current is 1.95mA. It just extend Neblina lift abou 1.28 hours.
-But in 200Hz sampling rate. The electric before and after compression are 3.5 and 2.9 respectively. The running time of Neblina would be extended about 5.9 hours/
+The capacity of battery in Neblina is 100mAh, and the battery usage would not change too much, because it contains others fusion method which will running when turning on the Neblina.
+In 50Hz sensor sampling rate, the average usage electric current for transmit accelerometer data is 2.0mA. It means Neblina could transmit accelerometer data constantly in 100/2.0=50 hours.
+when Neblina does not move, the average usage electric current using Infinity norm compression is 1.95mA. It just extend Neblina work life about 1.28 hours.
+But in 200Hz sampling rate. The electric before and after compression are 3.5 and 2.9 respectively. The running time of Neblina would be extended about 5.9 hours.
 
-The experiment in Neblina, we weared Neblina on right wrist and
+we wore Neblina on right wrist and
 collected walking data and running data. 4000 data set was collected
@@
 
-\todo{ update }
-try using difference data set to measure compression radio, Error
-and energy usage. The numerical value presented below, is the
-average value in 5 seconds. The current electric current for Neblina
-without transmit is ***. we received 4000 data for human running and
-walking in 200Hz. Because of the limite RAM, for energy test, we only
-could save 400 static data into Neblina. We make 400 data run as a circle.
-For walking, one time swing arm need 1.2 second. Every 400 data must have 1 arm swing.
-change epsilon in order to decrease compression radio, measuring energy consumption.
+% \todo{ update }
+% try using difference data set to measure compression radio, Error
+% and energy usage. The numerical value presented below, is the
+% average value in 5 seconds. The current electric current for Neblina
+% without transmit is ***. we received 4000 data for human running and
+% walking in 200Hz. Because of the limite RAM, for energy test, we only
+% could save 400 static data into Neblina. We make 400 data run as a circle.
+% % For walking, one time swing arm need 1.2 second. Every 400 data must have 1 arm swing.
+% change epsilon in order to decrease compression radio, measuring energy consumption.
 
-\todo {running}
-If it's possible to save more static data?
+% \todo {running}
+% If it's possible to save more static data?
 
-\begin{itemize}
-    \item Data set: human activities, running, walking, jogging and work behind desk.
-    \item Experiment Condition: work with neblina.
-    \item Result:
-    \item Conclusion:
-\end{itemize}
+% \begin{itemize}
+%     \item Data set: human activities, running, walking, jogging and work behind desk.
+%     \item Experiment Condition: work with neblina.
+%     \item Result:
+%     \item Conclusion:
+% \end{itemize}
 
-The transform rate of Neblina is 50Hz.
-\\
-5-times bicep curl from Neblina. It includes 613 data which produced in 12.28 seconds.
-\\
-Mohammad Lateral bicep data which include 41428, produced in proximate 14 minutes.
+% The transform rate of Neblina is 50Hz.
+% \\
+% 5-times bicep curl from Neblina. It includes 613 data which produced in 12.28 seconds.
+% \\
+% Mohammad Lateral bicep data which include 41428, produced in proximate 14 minutes.
 
-\subsection{Compression ratios}
+% \subsection{Compression ratios}
 
-\subsection{Errors}
+% \subsection{Errors}
 
-\subsection{Memory consumption}
+% \subsection{Memory consumption}
 
@@
 \begin{table*}[]
-    \caption{}
+    \begin{center}
+    \caption{Result of Experiment 1 in Dimension 2}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
     Data set               & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
-    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Eclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
+    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
     Epsilon                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$  & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ \hline
@@
     \end{tabular}
+    \end{center}
 \end{table*}
@@
 \begin{table*}[]
-    \caption{Table}
+    \begin{center}
+    \caption{Result of Experiment 1 in Dimension 3}
     \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
@@
 \begin{table}[]
-    \caption{}
+    \begin{center}
+    \caption{result of Experiment 2 with walking Data Set}
     \begin{tabular}{|l|l|l|l|l|l|l|}
@@
     \end{tabular}
+    \end{center}
 \end{table}
@@
 \begin{table}[]
-    \caption{}
+    \begin{center}
+    \caption{result of Experiment 2 with running Data Set}
     \begin{tabular}{|l|l|l|l|l|l|l|}

### 2018-10-16 paper.tex
Started working on experiment 1

@@
 \usepackage{algorithm}
-%\usepackage{algorithmic}
 \usepackage{algorithmicx} % Doc is at http://tug.ctan.org/macros/latex/contrib/algorithmicx/algorithmicx.pdf
 \usepackage{algpseudocode}
-%\newtheorem*{theorem}{Lemma}
-
-%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-%\renewcommand{\algorithmicensure}{\textbf{Output:}}
-%\usepackage{algpseudocode}
 \usepackage{amsfonts} % for R symbol (the set of real numbers)
 \usepackage{color}
+\usepackage{colortbl} % for \rowcolor
 \usepackage[pdftex]{graphicx}
@@
 \newcommand{\norm}[1]{\left\lVert#1\right\rVert}
-
 \newtheorem*{theorem}{Theorem}
+\definecolor{headcolor}{gray}{0.9}
 
@@
 with the infinity norm corresponds to a compression error of
-$\frac{\epsilon}{\sqrt{2}}$ with the Euclidean norm. Unsurprisingly, the
+$\frac{\epsilon}{\sqrt{n}}$ with the Euclidean norm. Unsurprisingly, the
 infinity norm is more 'tolerant' than the Euclidean norm.
@@
 \section{Results}
-\todo{ result table ?}
-\subsection{Experiment 1: Pilot tests on Computer}
-In this experiment, in order to compare the performance in different norm, different EPSILON and different dataset.
-We collected 2 data set from Neblina, 5-times bicep curl data and Mohammad Lateral bicep curl.
-\begin{itemize}
-    \item Data set: 5-times bicep curl which includes 613 data;
-                    Mohammad Lateral bicep curl which include 41428 data;
-                    All data is collected from Neblina, with 50Hz sampling of Sensors.
-                    Using Valgrind massif measure memory usage. And using 'gettimeofday()' function in 'sys/time.h' for measure processing time usage.
-    \item Experiment Condition: Fedora 64-bit system with 16G memory, i5-3210M CPU @ 2.50GHz × 4. For each data set, we change number of Dimension and EPSILON.
-    \item Result: From the table 1 and table 2, The Max Error, Compression Radio and Time usage in both norm decrease when EPSILON become smaller.
-Comparing with different norm and same EPSILON, the infinity no, and few ndeed has more 'tolerance'.
-But when comparing using Infinity with $\epsilon=100/\sqrt{n}$, where n is number of dimension, to make sure the max error would not greater than 100, and Euclidean with $\epsilon$=100, the Euclidean norm has better compression radio.
-Although Infinity norm makes Max error larger, but it has less running time, and few fixed Memory usage according number of dimension.
-The Memory Usage of Euclidea is not fixed, because it need save $\mathcal{B}_i, i\subset\llbracket 1, m \rrbracket$ after origin $(u_0^k, y_0^k)$, costing lots of Memory.
-From the table 1 and 2, the Compression Radio in second data set is pretty better than first data set, because Mohammad Lateral bicep has more data than first dataset about 67.5 times.
-It is pointless to consider the different compression radio in this situation.
 
-    \item Conclusion: The infinity norm has higher compression radio than Euclidean norm with same $\epsilon$, and uses less running time and little memory.
-But Euclidean makes sure the Max Error between reconstructed data and original data under EPSILON.
-Both of norm would has lower Compression ratios when $\epsilon$ becomes smaller.
-\end{itemize}
+We conducted two experiments using Motsai's Neblina 
+module\footnote{\url{ https://motsai.com/products/neblina}}, a system 
+with a Nordic Semiconductor nRF52832 micro-controller, 64~KB of RAM, 
+and Bluetooth Low Energy connectivity. The Neblina has a 3D 
+accelerometer, 3D gyroscope, 3D magnetometer, and environmental sensors 
+for humidity, temperature and pressure. It can function as an Inertial
+Motion Unit, a Vertical Reference Unit, or an Attitude and Heading Reference
+System.
+
+\subsection{Experiment 1: validation tests}
+
+In this experiment we validated the behavior of our LTC extensions on a 
+PC processing data acquired with the Neblina. We collected 2 data sets, 
+``5-times biceps curl" and ``Mohammad lateral biceps curl". from the 
+accelerometer with a 50Hz sampling rate (see 
+Figure~\ref{fig:datasets}).
+
+We compressed the datasets with various values of $\epsilon$, using our 
+2D (x and y) and 3D (x, y and z) implementations of LTC. On the Neblina,
+the resolution of the accelerometer is about 20~mg (196~mm/$s^2$).
+ We used a 
+laptop computer with 16~GB of memory, and Intel i5-3210M CPU @ 2.50GHz 
+× 4, and Linux Fedora 27. We measured memory consumption using 
+Valgrind's massif 
+tool~\cite{nethercote2006building}\footnote{\url{http://valgrind.org}}, 
+and processing time using \texttt{gettimeofday()} from the GNU C 
+Library.
+
+Results are reported in Table~\ref{table:results-validation}. 
+As expected, the maximum measured error remains lower than $\epsilon$ in 
+all cases, and the compression ratio increases with $\epsilon$. 
+%Compared to the infinity norm, The Euclidean norm reduces the 
+%compression ratio by a factor of \pm, which was also expected.
+
+    %~ \item Result: From the table 1 and table 2, The Max Error, 
+    %~ Compression Radio and Time usage in both norm decrease when EPSILON 
+    %~ become smaller. Comparing with different norm and same EPSILON, the 
+    %~ infinity no, and few ndeed has more 'tolerance'. But when comparing 
+    %~ using Infinity with $\epsilon=100/\sqrt{n}$, where n is number of 
+    %~ dimension, to make sure the max error would not greater than 100, 
+    %~ and Euclidean with $\epsilon$=100, the Euclidean norm has better 
+    %~ compression radio. Although Infinity norm makes Max error larger, 
+    %~ but it has less running time, and few fixed Memory usage according 
+    %~ number of dimension. The Memory Usage of Euclidea is not fixed, 
+    %~ because it need save $\mathcal{B}_i, i\subset\llbracket 1, m 
+    %~ \rrbracket$ after origin $(u_0^k, y_0^k)$, costing lots of Memory. 
+    %~ From the table 1 and 2, the Compression Radio in second data set is 
+    %~ pretty better than first data set, because Mohammad Lateral bicep 
+    %~ has more data than first dataset about 67.5 times. It is pointless 
+    %~ to consider the different compression radio in this situation.
+
+    %~ \item Conclusion: The infinity norm has higher compression radio 
+    %~ than Euclidean norm with same $\epsilon$, and uses less running 
+    %~ time and little memory. But Euclidean makes sure the Max Error 
+    %~ between reconstructed data and original data under EPSILON. Both of 
+    %~ norm would has lower Compression ratios when $\epsilon$ becomes 
+    %~ smaller.
+
+\begin{table}
+
+    \begin{subfigure}{\columnwidth}
+    \centering
+    \begin{tabular}{l|l|l|l|l}
+    \hline
+    \rowcolor{headcolor}
+    Norm                       & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
+    $\epsilon$                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$ \\
+    Max error              & 90.24       & 66.79           & 99.63       & 70.47          \\ 
+    Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\ 
+    Peak memory usage      & 80B          & 80B             & 432B        & 240B           \\ 
+    Processing time        & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms        \\ \hline
+    \end{tabular}
+    \caption{5-times bicep curl (2D)}
+    \end{subfigure}\\
+    \begin{subfigure}{\columnwidth}
+    \centering
+    \begin{tabular}{l|l|l|l|l}
+    \hline
+    \rowcolor{headcolor}
+    Norm               & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
+    $\epsilon$             & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ 
+    Max error              & 99.49     & 70.52             & 99.99      & 70.71             \\ 
+    Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ 
+    Peak memory       & 80B        & 80B               & 2.1KB      & 1.3KB             \\ 
+    Processing time      & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
+    \end{tabular}
+    \caption{Mohammad lateral biceps curl (2D)}
+    \end{subfigure}\\    
+    \begin{subfigure}{\columnwidth}
+    \centering
+    \begin{tabular}{l|l|l|l|l}
+    \hline
+    \rowcolor{headcolor}
+                            & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
+    $\epsilon$             & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$   \\ 
+    Max error              & 100.17       & 60.38           & 99.94       & 56.89            \\ 
+    Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\ 
+    Peak memory            & 112B         & 112B            & 384B        & 256B             \\ 
+    Processing time        & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms          \\ \hline
+    \end{tabular}
+    \caption{5-times biceps curl (3D)}
+    \end{subfigure}\\
+    \begin{subfigure}{\columnwidth}
+    \centering
+    \begin{tabular}{l|l|l|l|l}
+    \hline
+    \rowcolor{headcolor}
+                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
+    $\epsilon$                & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\
+    Max error                 & 97.54     & 56.00             & 99.99      & 57.73             \\
+    Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\
+    Peak memory & 112B        & 112B              & 4.9KB      & 3.0KB             \\
+    Processing time           & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
+    \end{tabular}
+    \caption{Mohammad lateral biceps curl (3D)}
+    \end{subfigure}
+    \caption{Validation experiment}
+    \label{table:results-validation}
+\end{table}
 
 \subsection{Experiment 2: energy reduction on the Neblina}
-The experiment in Neblina V2 module~\cite{Neblina}, which is a module integrating multiple sensors. Its current System-on-Chip (SoC) radio is the Nordic Semiconductor nRF52832, and it has 64KB RAM.
 
-The capacity of battery in Neblina is 100mAh, and the battery usage would not change too much, because it contains others fusion method which will running when turning on the Neblina.
-In 50Hz sensor sampling rate, the average usage electric current for transmit accelerometer data is 2.0mA. It means Neblina could transmit accelerometer data constantly in 100/2.0=50 hours.
-when Neblina does not move, the average usage electric current using Infinity norm compression is 1.95mA. It just extend Neblina work life about 1.28 hours.
-But in 200Hz sampling rate. The electric before and after compression are 3.5 and 2.9 respectively. The running time of Neblina would be extended about 5.9 hours.
+The capacity of battery in Neblina is 100mAh, and the battery usage 
+would not change too much, because it contains others fusion method 
+which will running when turning on the Neblina. In 50Hz sensor sampling 
+rate, the average usage electric current for transmit accelerometer 
+data is 2.0mA. It means Neblina could transmit accelerometer data 
+constantly in 100/2.0=50 hours. when Neblina does not move, the average 
+usage electric current using Infinity norm compression is 1.95mA. It 
+just extend Neblina work life about 1.28 hours. But in 200Hz sampling 
+rate. The electric before and after compression are 3.5 and 2.9 
+respectively. The running time of Neblina would be extended about 5.9 
+hours.
 
@@
 \section*{Acknowledgement}
-\begin{table*}[]
-    \begin{center}
-    \caption{Result of Experiment 1 in Dimension 2}
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-    \hline
-    \multicolumn{9}{|l|}{Dimension 2}                                                                                                                         \\ \hline
-    Data set               & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
-    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
-    Epsilon                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$  & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ \hline
-    Max Error              & 127.63       & 94.46           & 99.63       & 70.47           & 140.70     & 99.73             & 99.99      & 70.71             \\ \hline
-    Compression Radio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%         & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ \hline
-    Max memory Usage(peak) & 80B          & 80B             & 432B        & 240B            & 80B        & 80B               & 2.1KB      & 1.3KB             \\ \hline
-    Time Usage(Total)      & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms         & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
-    \end{tabular}
-    \end{center}
-\end{table*}
-
-\begin{table*}[]
-    \begin{center}
-    \caption{Result of Experiment 1 in Dimension 3}
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-    \hline
-    \multicolumn{9}{|l|}{Dimension 3}                                                                                                                         \\ \hline
-    Data set               & \multicolumn{4}{l|}{5-times bicep curl}                        & \multicolumn{4}{l|}{Mohammad Lateral bicep}                     \\ \hline
-    Distance               & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} & \multicolumn{2}{l|}{Manhattan} & \multicolumn{2}{l|}{Euclidean} \\ \hline
-    Epsilon                & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$  & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\ \hline
-    Max Error              & 141.66       & 85.40           & 99.94       & 56.89           & 168.95     & 97.01             & 99.99      & 57.73             \\ \hline
-    Compression Radio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%          & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\ \hline
-    Max memory Usage(peak) & 112B         & 112B            & 384B        & 256B            & 112B       & 112B              & 4.9KB      & 3.0KB             \\ \hline
-    Time Usage(Total)      & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms         & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
-    \end{tabular}
-    \end{center}
-\end{table*}
 

### 2018-10-17 paper.tex
Fixed Table I

@@
     \rowcolor{headcolor}
-    Norm                       & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
+                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
     $\epsilon$                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$ \\
-    Max error              & 90.24       & 66.79           & 99.63       & 70.47          \\ 
+    Max error              & 99.88       & 70.68           & 99.63       & 70.47          \\ 
     Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\ 
@@
     \rowcolor{headcolor}
-    Norm               & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
+                   & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
     $\epsilon$             & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ 
-    Max error              & 99.49     & 70.52             & 99.99      & 70.71             \\ 
+    Max error              & 99.99     & 70.71             & 99.99      & 70.71             \\ 
     Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ 
@@
     $\epsilon$             & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$   \\ 
-    Max error              & 100.17       & 60.38           & 99.94       & 56.89            \\ 
+    Max error              & 99.88       & 57.41           & 99.94       & 56.89            \\ 
     Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\ 
@@
     $\epsilon$                & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\
-    Max error                 & 97.54     & 56.00             & 99.99      & 57.73             \\
+    Max error                 & 99.96     & 57.73             & 99.99      & 57.73             \\
     Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\

### 2018-10-17 paper.tex
Restructured figure scripts, put all figures on same range, first complete draft of section V

@@
 dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC
-to the 1-dimensional version, on gyroscopic data acquired on a SoM
+to the 1-dimensional version, on acceleration data acquired on a SoM
 device.
@@
 % Some related works from Bo's report
+
+Compression reduces radio usage but increases resource usage.
 
@@
 be $\frac{4}{\pi}$ times larger with the infinity norm than with the 
-Euclidean norm. Conversely, a compression error bounded by $\epsilon$
-with the infinity norm corresponds to a compression error of
-$\frac{\epsilon}{\sqrt{n}}$ with the Euclidean norm. Unsurprisingly, the
+Euclidean norm. In 3D, this ratio would be $\frac{6}{\pi}$. Conversely, 
+a compression error bounded by $\epsilon$ with the infinity norm 
+corresponds to a compression error of $\frac{\epsilon}{\sqrt{n}}$ with 
+the Euclidean norm. Unsurprisingly, the
 infinity norm is more 'tolerant' than the Euclidean norm.
@@
 
-As reference above, the norm selection is importance. In this section,
-we show the implementation of infinity norm and Euclidean norm.
+%~ As reference above, the norm selection is importance. In this section,
+%~ we show the implementation of infinity norm and Euclidean norm.
 
-%~ In practice, It's needed to transmit raw data which has multi-parameters
-%~ to clients e.g. Accelerometer, Euler Angle and Magnetometer etc.
-%~ Most of previous paper just force on single dimension sensor
-%~ data Compression. So we purpose a method to compress multi-dimensional
-%~ sensor data named LTC-D. It is used as linear estimation method.
-%~ Same as usual estimation compression method,  distance(different)
-%~ with compressed data from LTC-D and original data would not exceed
-%~ the predefined error range. We need to find line to represent
-%~ original data, it means the lines pass through datas' error range.
-%~ But in stream data, time seires data, it is difficult, because
-%~ all data do not show in same time plane. So this method will
-%~ mapping all data into one time plane. Then for each mapped error
-%~ range of data, check if there is intersection among them. If so means
-%~ there is a line could represent original data, and vice versa.
-\subsection{Multidimensional LTC with Manhattan distance}
-In section 2, we can know that the repersentation of intersection
-is a rectangular cuboid. So only one bounding box with n-dimensional
-is needed to represent the intersection. Assume a bounding box
-$\mathcal{BOX}_{m-1} = \bigcap_{j=1}^{m-1}{\mathcal{B}_{m-1}}$ which
-has Upper bound $U_i$ and lower Bound $L_i$ for each dimension
-$i$. So the fomular (1) in $6_{th}$ line of Algorithm 2 would
-be changed to $\mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m} \neq \O $. The Bounding box
-would be updated when this formular return true.
-Otherwise return false.
-\begin{enumerate}
-    \item Initialization: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
-    \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
-            defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
-            \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
-    \item The $\mathcal{B}_{m}$ should be a ractangular cube with center
-            $\frac{v_1}{v_m}z_m$ and weight $\frac{v_1}{v_m}\epsilon$.
-    \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_m}x_{mi}+
-            \frac{v_1}{v_m}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon$, return False.
-    \item Otherwise, the intersection do not be empty. Updating
-            the Bounding box $\mathcal{BOX}_m = \mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m}$. For
-            each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_m}x_{mi}+
-            \frac{v_1}{v_m}\epsilon)$, and $L_i = max(L_i , \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon)$. Return True.
-\end{enumerate}
+%~ \subsection{Multidimensional LTC with Manhattan distance}
+%~ In section 2, we can know that the repersentation of intersection
+%~ is a rectangular cuboid. So only one bounding box with n-dimensional
+%~ is needed to represent the intersection. Assume a bounding box
+%~ $\mathcal{BOX}_{m-1} = \bigcap_{j=1}^{m-1}{\mathcal{B}_{m-1}}$ which
+%~ has Upper bound $U_i$ and lower Bound $L_i$ for each dimension
+%~ $i$. So the fomular (1) in $6_{th}$ line of Algorithm 2 would
+%~ be changed to $\mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m} \neq \O $. The Bounding box
+%~ would be updated when this formular return true.
+%~ Otherwise return false.
+%~ \begin{enumerate}
+    %~ \item Initialization: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
+    %~ \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
+            %~ defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
+            %~ \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
+    %~ \item The $\mathcal{B}_{m}$ should be a ractangular cube with center
+            %~ $\frac{v_1}{v_m}z_m$ and weight $\frac{v_1}{v_m}\epsilon$.
+    %~ \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_m}x_{mi}+
+            %~ \frac{v_1}{v_m}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon$, return False.
+    %~ \item Otherwise, the intersection do not be empty. Updating
+            %~ the Bounding box $\mathcal{BOX}_m = \mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m}$. For
+            %~ each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_m}x_{mi}+
+            %~ \frac{v_1}{v_m}\epsilon)$, and $L_i = max(L_i , \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon)$. Return True.
+%~ \end{enumerate}
 
-% The method as below: assume the stream $i_{th}$ data
-% $D_i = (x_{i1}, x_{i2}, ..., x_{in},t_i)$, the first data $D_0$ would
-% be save as base point $Z=(z_{1}, z_{2}, ..., z_{n},t_z)$in the Method.
-% As usual, the timestamp after basepoint would be set as mapping plane.
-% We also need to record the intersect $S$ for find result lines.
-% The first data $D_1$ would change into tolerance range $R_1$.
-% initializing $S = R_1$. For each follow data$ D_i, i>1$, mapping $D_1$
-% into $\hat{D_1}$ = $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$,
-% and error margin after mapping should be $\frac{\epsilon}{t_i-t_z}$
-% on $\hat{x_{ij}}, j={1...n}$. The tolerance range after R_i, intersect
-% with S, if there is overlap, update S = S intersect R_i. If not, the base point
-% would be transmited and select a point in S as base point with timestamp $t_{i-1}$.
-
-% \todo{refector}
-% At beginning of the algorithm, we need a base point (which we will call \textit{z}) and bounding box which has upper and lower bound for each parameter respectively.Then start the algorithm.
-% \begin{enumerate}
-%   \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
-Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
-%   \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-%   \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
-%   \item Goto 2.
-%   \item output \textit{z} data point.
-%   \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
-%   \item Goto 2.
-%   \item After all, output \textit{z} data point and center of bounding box respectively.
-% \end{enumerate}
-
-According the Implement, the infinity norm boils down to apply 1D LTC algorithm in each dimension respectively.
+%~ According the Implement, the infinity norm boils down to apply 1D LTC algorithm in each dimension respectively.
 Since, the intersection would be rectangle in 2D and cube in 3D, the corresponding max errors are $\frac{\epsilon}{\sqrt{2}}$ and $\frac{\epsilon}{\sqrt{3}}$.
@@
 The max error between original data and reconstructed data certainly not greater than $\frac{\epsilon}{\sqrt{n}}$ where $n$ is dimension of data.
-% for tolerance range, it depends on EPSILON and different type of distances for EPSILON.
-% If we using Manhattan distance to create tolerance range, it would become rectangle in 2D and cube for 3D.
-% But the tolerance range wold become disk or ball in 2D and 3D respectively, by using Euclidean distance.
-\todo{maybe need a graphic}
 
-% In practice, Multidimensional LTC is same as implementing LTC in each
-% parameter respectively. But we did some changes in our method. Assume
-% $(x_{i1}, x_{i2}, ..., x_{in},t_i)$ is the $i_{th}$ coming data with
-% n-dimension, and a base data point Z  $(z_{1}, z_{2}, ...,
-% z_{n},t_z)$~\cite{schoellhammer2004lightweight}. We map each coming
-% data to $t_1$ time-stamp and create a bounding box for recording
-% overlapping range which includes upper and lower bound for each
-% dimension base on $t_1$. cause the time different between two adjacent
-% data, so the $i_th$ data after mapping is $(\{\hat{x_{ij}}=z_j +
-% \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-% After that updating tolerance range by adding designed error margin
-% which after mapping $\frac{\epsilon}{t_i-t_z}$ on $\hat{x_{ij}},
-% j={1...n}$ with Manhattan distance. checking if there is overlap
-% between tolerance and bounding box.The algorithm is as follows.
+%~ \todo{maybe need a graphic}
 
-% At beginning of the algorithm, we need a base point (which we will call
-% \textit{z}) and bounding box which has upper and lower bound for each
-% parameter respectively.Then start the algorithm.
-% \begin{enumerate}
-%   \item Initialization: Get first data point, and set point \textit{z} equals to first data point.
-Get the second data point $(x_{21},...,x_{2n},t_2)$, and assign each upper bound $U_j = x_{2j}+\frac{\epsilon}{t_2-t_1}$ and lower bound $L_j = x_{2j}-\frac{\epsilon}{t_2-t_1}$ where $j=\{1...n\}$.
-%   \item Get next data point, map the data point $(x_{i1},...,x_{in},t_i)$ into $(\{\hat{x_{ij}}=z_j + \frac{x_{ij}-z_{j}}{t_i-t_z} \mid1\leqslant{j}\leqslant{n}\},t_i)$.
-%   \item For each parameter(dimension) \textit{j}, if upper bound $U_j$ smaller than $x_{ij}-\frac{\epsilon}{t_i-t_1}$ or lower bound $L_j$ bigger than $x_{ij}+\frac{\epsilon}{t_i-t_1}$, then \textbf{goto 5}, else $U_j = min(U_j, x_{ij}+\frac{\epsilon}{t_i-t_1})$, and $L_j = max(L_j, x_{ij}-\frac{\epsilon}{t_i-t_1})$.
-%   \item Goto 2.
-%   \item output \textit{z} data point.
-%   \item Reset: set data point \textit{z} equals to center of the bounding box with time-stamp $t_{i-1}$, and $U_j=x_{ij}+\frac{\epsilon}{t_i-t_{i-1}}$, $L_j =x_{ij}-\frac{\epsilon}{t_i-t_{i-1}}$ with $j=\{1...n\}$.
-%   \item Goto 2.
-%   \item After all, output \textit{z} data point and center of bounding box respectively.
-% \end{enumerate}
-
-\subsection{Multidimensional LTC with Euclidean distance}
-In Euclidea norm, the representation of intersection is
-volume. There is no specific model to record repersentation
-with updating, so a list to save all balls $\mathcal{B}_j, 1\leqslant{j}\leqslant{m}$
-is needed. In order to test weather a set of balls intersect,
-the Helly's theorem could work, but the complexity of
-this method is too high to work with embeded, low-power
-systems which has limited CPU and RAM resource. So we
-implement Euclidean norm by using a method which based
-on plane sweep and binary search.
+%~ \subsection{Multidimensional LTC with Euclidean distance}
+%~ In Euclidea norm, the representation of intersection is
+%~ volume. There is no specific model to record repersentation
+%~ with updating, so a list to save all balls $\mathcal{B}_j, 1\leqslant{j}\leqslant{m}$
+%~ is needed. In order to test weather a set of balls intersect,
+%~ the Helly's theorem could work, but the complexity of
+%~ this method is too high to work with embeded, low-power
+%~ systems which has limited CPU and RAM resource. So we
+%~ implement Euclidean norm by using a method which based
+%~ on plane sweep and binary search.
 Assume the list of balls $S_{m-1}$ contains balls from $\mathcal{B}_1$ to $\mathcal{B}_{m-1}$, and an temporary data point $output$ used for updated origin $(\tau^k, \xi^k)$.
@@
 Assume each $\Hat{\mathcal{B}} \in S$ which has corresponding center $\Hat{z}$ and radius $\Hat{\epsilon}$.
-Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$, and for each data $(u_m^k, y_m^k)$ with diminsion $n$, defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m = \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
+%~ Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$, and for each data $(u_m^k, y_m^k)$ with diminsion $n$, defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m = \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
 The $\mathcal{B}_{m}$ should be one n-ball with center $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$.
@@
 
-\begin{algorithm}
-    \begin{flushleft}
-        \textbf{Input:} $S$, $\mathcal{B}_m$, $output$ \\
-        \textbf{Output:} $true|false$\\
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \State d = n \Comment{dimension index}
-        \State $max_d = \frac{v_1}{v_m}(x_d + \epsilon)$
-        \State $min_d = \frac{v_1}{v_m}(x_d - \epsilon)$
-        \ForAll{$\Hat{\mathcal{B}}$ \textbf{in} $S$}
-            \If{$\Hat{\mathcal{B}} \bigcap \mathcal{B}_m = $ \O }
-                \State \textbf{return} false
-            \ElsIf{$\mathcal{B}_m \bigcap \Hat{\mathcal{B}}  = \mathcal{B}_m $}
-                \State remove $\Hat{\mathcal{B}}$ from $S$
-                \State \textbf{continue}\\
-            $max_d = \min(max_d, \Hat{x_d} + \Hat{\epsilon}$)\\
-            $min_d = \max(min_d, \Hat{x_d} - \Hat{\epsilon}$)
-            \EndIf
-        \EndFor
-        \State $\textbf{add } \mathcal{B}_m \textbf{ into } S$
-        \If{$max_d < min_d$}
-            \State \textbf{return} false
-        \EndIf
-        \State temp\_output = output \Comment{used for next operation}
-        \If{Recursive$(min_d, max_d, n, p\_cp)$}
-            \State $output = temp\_output$
-            \State \textbf{return} true
-        \Else
-            \State \textbf{return} false
-        \EndIf
-    \end{algorithmic}
-    \caption{isThereIntersection}
-    \label{algo:isThereIntersection}
-\end{algorithm}
+%~ \begin{algorithm}
+    %~ \begin{flushleft}
+        %~ \textbf{Input:} $S$, $\mathcal{B}_m$, $output$ \\
+        %~ \textbf{Output:} $true|false$\\
+    %~ \end{flushleft}
+    %~ \begin{algorithmic}[1]
+        %~ \State d = n \Comment{dimension index}
+        %~ \State $max_d = \frac{v_1}{v_m}(x_d + \epsilon)$
+        %~ \State $min_d = \frac{v_1}{v_m}(x_d - \epsilon)$
+        %~ \ForAll{$\Hat{\mathcal{B}}$ \textbf{in} $S$}
+            %~ \If{$\Hat{\mathcal{B}} \bigcap \mathcal{B}_m = $ \O }
+                %~ \State \textbf{return} false
+            %~ \ElsIf{$\mathcal{B}_m \bigcap \Hat{\mathcal{B}}  = \mathcal{B}_m $}
+                %~ \State remove $\Hat{\mathcal{B}}$ from $S$
+                %~ \State \textbf{continue}\\
+            %~ $max_d = \min(max_d, \Hat{x_d} + \Hat{\epsilon}$)\\
+            %~ $min_d = \max(min_d, \Hat{x_d} - \Hat{\epsilon}$)
+            %~ \EndIf
+        %~ \EndFor
+        %~ \State $\textbf{add } \mathcal{B}_m \textbf{ into } S$
+        %~ \If{$max_d < min_d$}
+            %~ \State \textbf{return} false
+        %~ \EndIf
+        %~ \State temp\_output = output \Comment{used for next operation}
+        %~ \If{Recursive$(min_d, max_d, n, p\_cp)$}
+            %~ \State $output = temp\_output$
+            %~ \State \textbf{return} true
+        %~ \Else
+            %~ \State \textbf{return} false
+        %~ \EndIf
+    %~ \end{algorithmic}
+    %~ \caption{isThereIntersection}
+    %~ \label{algo:isThereIntersection}
+%~ \end{algorithm}
 
-% \begin{enumerate}
-%     \item Initialzation: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
-%     \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
-%             defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
-%             \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
-%     \item The $\mathcal{B}_{m}$ should be one n-ball with center
-%             $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$.
-%     \item For each ball $\hat{\mathcal{B}}$ in list $S$, if $\hat{\mathcal{B}} \bigcap \mathcal{B}_m = \O$, return False. Else if
-%     $\mathcal{B}_m\subset\hat{\mathcal{B}}$, remove $\hat{\mathcal{B}}$ from list $S$.
-%     \item Select parameter p = n (which is ball's dimension), define $Max_{(p=n)} = \min_{j=1}^{S.length}{(\frac{v_1}{v_j}z_{(p=n)} + \frac{v_1}{v_j}\epsilon)}$, and $Min_{(p=n)} = \max_{j=1}^{S.length}{(\frac{v_1}{v_j}z_{(p=n)} - \frac{v_1}{v_j}\epsilon)}$.
-If $Max_{(p=n)} < Min_{(p=n)}$, return False.
-%     \item Use binary search to select $mid_{(p=n)} = (Min_{(p=n)} + Max_{(p=n)})/2$
-% \end{enumerate}
-
-% In Euclidean distance version, we also map the coming data into same
-% time-stamp $t_1$ the timestamp after base point. The difference with
-% Manhattan distance version is that recording overlapping part with
-% a post-designed model is difficult, which need retain several arcs in
-% 2-dimension, or convex surfaces in 3-dimension. In our method, we will
-% record all tolerance range for every mapped data which come from base
-% data point until coming data point, in order to checking if there is
-% intersection among them. For instance, in 3D-t, assume we have a the
-% base point $Z = D_0$ and the tolerance range $R_1$ which is a ball
-% as the intersection S. we need a list L to record mapped balls
-% from $D_1$ to coming data. For each comming data $D_i, i>1$ mapping
-% this data into $t_1$, and add it into list. Then the work is check out
-% if all balls intersect, and form a public intersection.
-% The method is based on plane sweep and binary search. At first, select one parameter,
-% such as x-axis, finding a bounding range of all balls $B_i$ in x-axis.
-% suppose $Max_bound_x = Min{1..n}{B_i.center.x + EPSILON/i}$, and
-% $Min_bound_x = Max{1..n}{B_i.center.x - EPSILON/i}$. If there is overlap
-% among balls, then the axis of the points inside intersection must located
-% between Min_bound_x and Max_bound_x.
-In the method, selecting dimension(n as default in our method) to calculate max point value and min point value of all n-balls in this dimension.
+%~ In the method, selecting dimension(n as default in our method) to calculate max point value and min point value of all n-balls in this dimension.
 If the max value bigger than min value, then there is no intersection.
@@
 In Recursive function Algorithm~\ref{algo:recursive}, using binary search select
-median $mid_d$ of $max_d$ and $min_d$ in order to find bound range of dimension d-1 ($max_{d-1}$, $min_{d-1}$) over the plane $x_d = max_d$.
+%~ median $mid_d$ of $max_d$ and $min_d$ in order to find bound range of dimension d-1 ($max_{d-1}$, $min_{d-1}$) over the plane $x_d = max_d$.
 If bound range of dimension $d-1$ is not empty, continue calling function \textbf{Recursive}($min_{d-1}$, $min_{d-1}$, $d-1$, $temp\_output$).
 Recursively calling this function, until getting result.
-\todo{add recursive pseudo-code}
-% Using binary search to select
-% mid_x = (Min_bound_x + Max_bound_x)/2, then calculate a y-axis bounding
-% with the plane x = mid_x. If the get bounding range in y-axis where
-% $Max_bound_y > Min_bound_y$ and using binary search again to find mid_y,
-% It means there is a line x=mid_x, Max_bound_y>= y >= Min_bound_y,
-% parallels z-axis, could pass through all balls. Finally, in z-axis,
-% computing bounding range, and If $Max_bound_z > Min_bound_z$, there
-% must be one or more points inside all balls. The problem be solved.
-% If the loop of binary search in x-axis overs, then there is no public
-% intersection among balls, and need to transmit and update base point.
-% In this method we need O(n*logn*logn) time complexity for binary search
-% in x-axis and y-axis and traversal all balls in z-axis, also O(n) space
-% complexity is needed for maintaining list. According this method,
-% it could be extended into N-dimensional data. The main idea is to search,
-% dimension by dimension, from a room or plane or line and get intersection
-% point finally.
+%~ \todo{add recursive pseudo-code}
 
-% \todo{below content is useful? }
-% In the rest of this section, we describe examples for 2-dimensional and 3-dimensional version. After that, we extend the method for n-dimension.
-% \begin{itemize}
-% \item \textbf{2-dimensional LTC in Euclidean distance:}In this situation, the tolerance range after mapping is a disk.
-After initializing base data point \textit{z}, for each coming data point need to be mapped into a same time-stamp, and heck if there is a intersection amount disks in disks set and new mapped coming data.
-Therefore, a algorithm is need to determine whether \textit{n} disks intersect or not.
-% \item \textbf{3-dimensional LTC in Euclidean distance:}In 3-dimension, cause of the preassigned error margin, the disks become balls with one extra axis.
-So In 3-dimension whether \textit{n} balls intersect need to be check.
-% \end{itemize}
-
-% At first, let us solve the \textit{n} disks intersect.
-We use a algorithm which is based on plane sweep and dichotomy.
-Assume a disk include center$(x,y)$ and radius $r$.
-The pseudo-code in Algorithm 1.
-
-% \begin{algorithm}
-%     \caption{whether disks intersect}
-%     \begin{flushleft}
-%         \textbf{Input:} $l$ - list of disks, $d$ - mapped coming disk, $p$ - point will be base point\\
-%         \textbf{Output:} $true|false$  is there a intersection\\
-%         \textbf{function} isIntersect$(l, d, p)$
-%     \end{flushleft}
-%     \begin{algorithmic}[1]
-%         \State $tmp_list \gets null$
-%         \State $max\_x\gets d.x+d.r$
-%         \State $min\_x\gets d.x-d.r$
-
-%         \ForAll{$old\_disk$ \textbf{in} $l$}
-%             \If{$d \cap old\_disk = \emptyset$} % distance(d.center, old\_disk.center) > d.r + old\_disk.r
-%                 \State \textbf{return} false
-%             \ElsIf{$d \cap old\_disk \neq d$}
-%                 \State {$\textbf{add } old\_disk \textbf{ into } tmp\_list$\\
-%                         $max\_x\gets $ MIN($max\_x, old\_disk.x+old\_disk.r$)\\
-%                         $min\_x\gets $ MAX($min\_x, old\_disk.x-old\_disk.r$)}
-%             \EndIf
-%         \EndFor
-%         \State $\textbf{add } d \textbf{ into } tmp\_list$
-%         \If{$max\_x < min\_x$}
-%             \State \textbf{return} false
-%         \EndIf
-%         \While{$min\_x \leqslant max\_x$}
-%             \State $mid \gets (min\_x + max\_x)/2$
-%             \State $max\_y \gets +\infty$
-%             \State $min\_y \gets -\infty$
-%             \For{$i=1$ \textbf{to} $tmp\_list.length$}
-%                 \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $x=mid$, $(P1.y\geqslant P2.y)$
-%                 \If{$P_1.y < max\_y$}
-%                     \State $max\_y \gets p_1.y$
-%                     \State $max\_index \gets i$
-%                 \EndIf
-%                 \If{$P_2.y > min\_y$}
-%                     \State $min\_y \gets p_2.y$
-%                     \State $min\_index \gets i$
-%                 \EndIf
-%             \EndFor
-%             \If{$max\_y >= min\_y$}
-%                 \State $p.x \gets mid$
-%                 \State $p.y \gets (max\_y+min\_y)/2$
-%                 \State $l \gets tmp\_list$
-%                 \State \textbf{return} true
-%             \EndIf
-%             \State {Assume $P_d$ is the intersection between line of
-%             centers from $tmp\_list[max\_index]$ and $tmp\_list[min\_index]$
-%             , and their common chord}
-%             \If{$P_d.x < mid$}
-%                 \State $max\_y \gets mid-1$
-%             \ElsIf{$P_d.x > mid$}
-%                 \State $min\_y \gets mid+1$
-%             \EndIf
-%         \EndWhile
-%         \Return false
-%     \end{algorithmic}
-% \end{algorithm}
-
-% The main idea of the algorithm is, remove the bigger disk who contains mapped coming disk.
-It maybe increase Computational efficiency in the rest of algorithm, cause mapped coming disk is the smallest one than all in list of disks.
-Then we make a bounding range for x-axis and select a x-value $mid$ by using dichotomy method in order to calculate if a point $(y, mid)$ is included all disks.
-In 2-dimension Euclidean norm, the complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
+%~ In 2-dimension Euclidean norm, the complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
 In 3-dimension, It needs $O(\log^2\epsilon)$ to determine $mid\_3, mid\_2$, and $O(n)$ to traverse all balls in list and calculate bounding range of dimension d=1.
@@
 
-% \begin{algorithm}
-%     \begin{flushleft}
-%         \textbf{Input:} $S$, $\mathcal{B}_m$, $output$
-%         \textbf{Output:} $true|false$  is there a intersection\\
-%         \textbf{function} isIntersect$(l, o, p)$
-%     \end{flushleft}
-%     \begin{algorithmic}[1]
-%         \State $tmp_list \gets null$
-%         \State $max \gets o.d\_n+o.r$
-%         \State $min \gets o.d\_n-o.r$
+%~ \begin{algorithm}
+    %~ \begin{flushleft}
+        %~ \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
+    %~ \end{flushleft}
+    %~ \begin{algorithmic}[1]
+        %~ \While{$left \leqslant right$}
+            %~ \State $mid \gets (left + right)/2$
+            %~ \State $max \gets +\infty$
+            %~ \State $min \gets -\infty$
+            %~ \For{$i=1$ \textbf{to} $tmp\_list.length$}
+                %~ \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
+                %~ \If{$P_1.d_{j-1} < max$}
+                    %~ \State $max \gets p_1.d_{j-1}$
+                    %~ \State $max\_index \gets i$
+                %~ \EndIf
+                %~ \If{$P_2.d_{j-1} > min$}
+                    %~ \State $min \gets p_2.d_{j-1}$
+                    %~ \State $min\_index \gets i$
+                %~ \EndIf
+            %~ \EndFor
+            %~ \If{$max >= min$}
+                %~ \State $p.d_j \gets mid$
+                %~ \If{Recursive$(min, max, j-1, p)$}
+                    %~ \State \textbf{return} true
+                %~ \EndIf
+            %~ \EndIf
+            %~ \State Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
+            %~ \If{$P_d.d_j < mid$}
+                %~ \State $right \gets mid-1$
+            %~ \ElsIf{$P_d.d_j > mid$}
+                %~ \State $left \gets mid+1$
+            %~ \EndIf
 
-%         \ForAll{$old\_obj$ \textbf{in} $l$}
-%             \If{$o \cap old\_obj = \emptyset$}
-%                 \State \textbf{return} false
-%             \ElsIf{$o \cap old\_obj \neq o$}
-%                 \State {$\textbf{add } old\_obj \textbf{ into } tmp\_list$\\
-%                         $max\gets $ MIN($max, old\_obj.d\_n+old\_obj.r$)\\
-%                         $min\gets $ MAX($min, old\_obj.d\_n-old\_obj.r$)}
-%             \EndIf
-%         \EndFor
-%         \State $\textbf{add } o \textbf{ into } tmp\_list$
-%         \If{$max < min$}
-%             \State \textbf{return} false
-%         \EndIf
-%         $p\_cp \gets p$
-%         \If{Recursive$(min, max, n, p\_cp)$}
-%             \State $p \gets p\_cp$
-%             \State \textbf{return} true
-%         \Else
-%             \State \textbf{return} false
-%         \EndIf
-%     \end{algorithmic}
-%     \caption{isThereIntersection}
-%     \label{algo:isThereIntersection}
-% \end{algorithm}
+        %~ \EndWhile
+        %~ \Return false
+    %~ \end{algorithmic}
+%~ \end{algorithm}
 
-\begin{algorithm}
-    \begin{flushleft}
-        \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
-    \end{flushleft}
-    \begin{algorithmic}[1]
-        \While{$left \leqslant right$}
-            \State $mid \gets (left + right)/2$
-            \State $max \gets +\infty$
-            \State $min \gets -\infty$
-            \For{$i=1$ \textbf{to} $tmp\_list.length$}
-                \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
-                \If{$P_1.d_{j-1} < max$}
-                    \State $max \gets p_1.d_{j-1}$
-                    \State $max\_index \gets i$
-                \EndIf
-                \If{$P_2.d_{j-1} > min$}
-                    \State $min \gets p_2.d_{j-1}$
-                    \State $min\_index \gets i$
-                \EndIf
-            \EndFor
-            \If{$max >= min$}
-                \State $p.d_j \gets mid$
-                \If{Recursive$(min, max, j-1, p)$}
-                    \State \textbf{return} true
-                \EndIf
-            \EndIf
-            \State Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
-            \If{$P_d.d_j < mid$}
-                \State $right \gets mid-1$
-            \ElsIf{$P_d.d_j > mid$}
-                \State $left \gets mid+1$
-            \EndIf
-
-        \EndWhile
-        \Return false
-    \end{algorithmic}
-\end{algorithm}
-
-\section{Results}
+\section{Experiments and Results}
 
@@
 and Bluetooth Low Energy connectivity. The Neblina has a 3D 
-accelerometer, 3D gyroscope, 3D magnetometer, and environmental sensors 
+accelerometer, a 3D gyroscope, a 3D magnetometer, and environmental sensors 
 for humidity, temperature and pressure. It can function as an Inertial 
-Motion Unit, a Vertical Reference Unit, or an Attitude and Heading Reference
-System.
+Motion Unit, a Vertical Reference Unit, or an Attitude and Heading 
+Reference System. The Neblina has a battery of 100mAh; its average 
+consumption is 2.52~mA without radio transmission and 3.47~mA with 
+radio transmission, leading to an autonomy of 39.7~h without 
+transmission and 28.8~h with transmission. \todo{Omid, could you review
+this paragraph?}
 
@@
 In this experiment we validated the behavior of our LTC extensions on a 
-PC processing data acquired with the Neblina. We collected 2 data sets, 
-``5-times biceps curl" and ``Mohammad lateral biceps curl". from the 
-accelerometer with a 50Hz sampling rate (see 
-Figure~\ref{fig:datasets}).
+PC processing data acquired with the Neblina. We collected two 3D 
+accelerometer time series, a short one and a longer one, acquired 
+on two different subjects performing biceps curl, with a 50Hz sampling rate (see 
+Figure~\ref{fig:datasets-1}). It should be noted that the longer dataset also has 
+a higher amplitude, most likely due to differences between subjects.
 
-We compressed the datasets with various values of $\epsilon$, using our 
+\begin{figure*}
+\begin{subfigure}{2\columnwidth}
+\includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-x.pdf}
+\includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-y.pdf}
+\includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-z.pdf}
+\caption{Short}
+\end{subfigure}
+\begin{subfigure}{2\columnwidth}
+\includegraphics[width=0.33\columnwidth]{figures/Mohammad-bicep-curl-plot-x.pdf}
+\includegraphics[width=0.33\columnwidth]{figures/Mohammad-bicep-curl-plot-y.pdf}
+\includegraphics[width=0.33\columnwidth]{figures/Mohammad-bicep-curl-plot-z.pdf}
+\caption{Long} 
+\end{subfigure}
+\caption{Time series used in Experiment 1}
+\label{fig:datasets-1}
+\end{figure*}
+
+We compressed the time series with various values of $\epsilon$, using our 
 2D (x and y) and 3D (x, y and z) implementations of LTC. On the Neblina,
@@
 Results are reported in Table~\ref{table:results-validation}. 
-As expected, the maximum measured error remains lower than $\epsilon$ in 
-all cases, and the compression ratio increases with $\epsilon$. 
-%Compared to the infinity norm, The Euclidean norm reduces the 
-%compression ratio by a factor of \pm, which was also expected.
+As expected, the compression ratio increases with $\epsilon$, and the 
+maximum measured error remains lower than $\epsilon$ in all cases. The 
+maximum is reached most of the time on these time series.
 
-    %~ \item Result: From the table 1 and table 2, The Max Error, 
-    %~ Compression Radio and Time usage in both norm decrease when EPSILON 
-    %~ become smaller. Comparing with different norm and same EPSILON, the 
-    %~ infinity no, and few ndeed has more 'tolerance'. But when comparing 
-    %~ using Infinity with $\epsilon=100/\sqrt{n}$, where n is number of 
-    %~ dimension, to make sure the max error would not greater than 100, 
-    %~ and Euclidean with $\epsilon$=100, the Euclidean norm has better 
-    %~ compression radio. Although Infinity norm makes Max error larger, 
-    %~ but it has less running time, and few fixed Memory usage according 
-    %~ number of dimension. The Memory Usage of Euclidea is not fixed, 
-    %~ because it need save $\mathcal{B}_i, i\subset\llbracket 1, m 
-    %~ \rrbracket$ after origin $(u_0^k, y_0^k)$, costing lots of Memory. 
-    %~ From the table 1 and 2, the Compression Radio in second data set is 
-    %~ pretty better than first data set, because Mohammad Lateral bicep 
-    %~ has more data than first dataset about 67.5 times. It is pointless 
-    %~ to consider the different compression radio in this situation.
+\paragraph{Inifinity vs Euclidean norms}
+Compared to the infinity norm, The average ratio between the compression ratios obtained
+with the infinity and Euclidean norm is 1.08 for 2D data, and 1.20 
+for 3D data. These ratios are lower than the theoretical values of 
+$\frac{4}{\pi}$ in 2D and $\frac{6}{\pi}$ in 3D, which are obtained for 
+random-uniform signals. Unsurprisingly, the infinity norm surpasses the 
+Euclidean norm in terms of resource consumption. Memory-wise, the 
+infinity norm requires a constant amount of 80~B, used to store the 
+intersection of n-balls. This amount is realistic on modules such as
+the Neblina. The Euclidean norm, however, uses up to 4.9~KB of memory 
+on the Long time series in 3D with $\epsilon=100$. More importantly, 
+the amount of required memory increases for more complex time series 
+(Long vs Short), and it also increases with larger 
+values of $\epsilon$. Similar observations are made for the processing 
+time, with values ranging from 0.2~ms for the simplest time series and 
+smallest $\epsilon$, to 26.4~ms for the most complex time series and 
+largest $\epsilon$. A better algorithm needs to be found to make the 
+Euclidean norm usable for systems on modules.
 
-    %~ \item Conclusion: The infinity norm has higher compression radio 
-    %~ than Euclidean norm with same $\epsilon$, and uses less running 
-    %~ time and little memory. But Euclidean makes sure the Max Error 
-    %~ between reconstructed data and original data under EPSILON. Both of 
-    %~ norm would has lower Compression ratios when $\epsilon$ becomes 
-    %~ smaller.
+\paragraph{2D vs 3D}
+For a given $\epsilon$ of 100 and a given time series, the compression 
+ratios are always higher in 2D than in 3D. It makes sense since the 
+\todo{x} is higher in 3D than it is in 2D. Resource consumption is 
+higher in 3D than in 2D: for the infinity norm, 3D consumes 1.4 times 
+more memory than 2D (1.6 times on average for Euclidean norm), and 
+processing time is 1.3 longer on average (1.18 on average for Euclidean 
+norm).
 
 \begin{table}
-
     \begin{subfigure}{\columnwidth}
@@
     Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\ 
-    Peak memory usage      & 80B          & 80B             & 432B        & 240B           \\ 
-    Processing time        & 0.103ms      & 0.082ms         & 0.220ms     & 0.200ms        \\ \hline
+    Peak memory            & 80~B          & 80~B             & 432~B        & 240~B           \\ 
+    Processing time        & 0.103~ms      & 0.082~ms         & 0.220~ms     & 0.200~ms        \\ \hline
     \end{tabular}
-    \caption{5-times bicep curl (2D)}
+    \caption{Short (2D)}
     \end{subfigure}\\
@@
     Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ 
-    Peak memory       & 80B        & 80B               & 2.1KB      & 1.3KB             \\ 
-    Processing time      & 5.70ms     & 4.85ms            & 20.04ms    & 19.28ms           \\ \hline
+    Peak memory       & 80~B        & 80~B               & 2.1~KB      & 1.3~KB             \\ 
+    Processing time      & 5.70~ms     & 4.85~ms            & 20.04~ms    & 19.28~ms           \\ \hline
     \end{tabular}
-    \caption{Mohammad lateral biceps curl (2D)}
+    \caption{Long (2D)}
     \end{subfigure}\\    
@@
     Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\ 
-    Peak memory            & 112B         & 112B            & 384B        & 256B             \\ 
-    Processing time        & 0.119ms      & 0.094ms         & 0.230ms     & 0.200ms          \\ \hline
+    Peak memory            & 112~B         & 112~B            & 384~B        & 256~B             \\ 
+    Processing time        & 0.119~ms      & 0.094~ms         & 0.230~ms     & 0.200~ms          \\ \hline
     \end{tabular}
-    \caption{5-times biceps curl (3D)}
+    \caption{Short (3D)}
     \end{subfigure}\\
@@
     Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\
-    Peak memory & 112B        & 112B              & 4.9KB      & 3.0KB             \\
-    Processing time           & 8.50ms     & 7.07ms            & 26.41ms    & 21.26ms           \\ \hline
+    Peak memory & 112~B        & 112~B              & 4.9~KB      & 3.0~KB             \\
+    Processing time           & 8.50~ms     & 7.07~ms            & 26.41~ms    & 21.26~ms           \\ \hline
     \end{tabular}
-    \caption{Mohammad lateral biceps curl (3D)}
+    \caption{Long (3D)}
     \end{subfigure}
-    \caption{Validation experiment}
+    \caption{Results from Experiment 1}
     \label{table:results-validation}
@@
 
-\subsection{Experiment 2: energy reduction on the Neblina}
+\subsection{Experiment 2: impact on energy consumption}
 
-The capacity of battery in Neblina is 100mAh, and the battery usage 
-would not change too much, because it contains others fusion method 
-which will running when turning on the Neblina. In 50Hz sensor sampling 
-rate, the average usage electric current for transmit accelerometer 
-data is 2.0mA. It means Neblina could transmit accelerometer data 
-constantly in 100/2.0=50 hours. when Neblina does not move, the average 
-usage electric current using Infinity norm compression is 1.95mA. It 
-just extend Neblina work life about 1.28 hours. But in 200Hz sampling 
-rate. The electric before and after compression are 3.5 and 2.9 
-respectively. The running time of Neblina would be extended about 5.9 
-hours.
+We measured the energy consumption of the Neblina module 
+for different values of $\epsilon$ and norms, to quantify the 
+added-value of LTC for this system.
 
-we wore Neblina on right wrist and
-collected walking data and running data. 4000 data set was collected
-from Neblina in 200Hz sampling rate. Since arm swing appearance
-repeated, we just take 1000 data from it, and make data as cycle of
-these 1000 data. Because 1000 data is produced in 5 seconds with 200Hz
-sampling rate, we measured average energy usage in 5 seconds.
+We acquired two 3D accelerometer time series at 200Hz corresponding to 
+common human activities: walking and running (see Figure~\ref{fig:datasets-2}). In both cases, the 
+subject was wearing the Neblina module on their right wrist.
+We collected 1,000 data points for each activity, corresponding to 
+5 seconds of activity.
+\begin{figure*}
+\begin{subfigure}{2\columnwidth}
+\includegraphics[width=0.33\columnwidth]{./figures/walking-1000-x.pdf}
+\includegraphics[width=0.33\columnwidth]{./figures/walking-1000-y.pdf}
+\includegraphics[width=0.33\columnwidth]{./figures/walking-1000-z.pdf}
+\caption{Walking}
+\end{subfigure}
+\begin{subfigure}{2\columnwidth}
+\includegraphics[width=0.33\columnwidth]{./figures/running-1000-x.pdf}
+\includegraphics[width=0.33\columnwidth]{./figures/running-1000-y.pdf}
+\includegraphics[width=0.33\columnwidth]{./figures/running-1000-z.pdf}
+\caption{Running}
+\end{subfigure}
+\caption{Time series used in Experiment 2}
+\label{fig:datasets-2}
+\end{figure*}
 
-At first, we measured base energy usage in Neblina. The energy usage
-without transmision is 2.515 mAh. It is 3.472mAh with transmision but
-no compression method. From table 3 and table 4, The MaxError don't exceed EPSILON
-and EPSILON*sqrt(Dimension) with LTC-Euclidean and LTC-Manhatan respectively.
-And the average electric current increase with compression radio decreasing.
-Energy usage by using both compression method are smaller than transmit
-without compression. From the result, the activities which has low frequency
-would gain larger compression radio.
+We measured energy consumption associated with the transmission of 
+these time series, for different norms and $\epsilon$ values. To do so, 
+we 'replayed' the time series by loading them as a byte array in the 
+Neblina, and we measured current intensity every 500~ms.
 
-The purpose of the compression method is compressing the number of
-data needed to transmited, in order to extend Neblna's life cycle
-by decreasing energy consumption. From table 3, for not vigorous exercise
-such walking, with EPSILON equals 100, the life cycle could be extend
-3(10\%)and 9(31\%) hours with LTC-Euclidean and LTC-Manhattan respectively.
-And vigorous exercise, with same condition, it extends 5.7(19.7\%)
-and 4.8(16.7\%) hours. So LTC-Euclidean and LTC-Manhattan are useful
-to save devices Energy. At same time, The fidelity is guaranteed.
+Results are reported in Table~\ref{table:results-energy}\todo{errors don't make sense}.
+For a given $\epsilon$ and norm, the compression ratio was larger for 
+walking than for running, since the running signal had a higher 
+entropy. The ratio of saved energy is relative to the reference current of 
+3.47~mA measured when the Neblina transmits data without compression.
+In all cases, activating compression saved energy. The reduction in energy
+consumption behaved as the compression ratio: it increased with $\epsilon$,
+was higher for the infinity norm than for the Euclidean, and it was 
+higher for the walking activity than for running. For a realistic error 
+of $\epsilon=20$\todo{unit}, the ratio of saved energy with the infinity norm was
+close to 20\%, which is very substantial.
 
-% \todo{ update }
-% try using difference data set to measure compression radio, Error
-% and energy usage. The numerical value presented below, is the
-% average value in 5 seconds. The current electric current for Neblina
-% without transmit is ***. we received 4000 data for human running and
-% walking in 200Hz. Because of the limite RAM, for energy test, we only
-% could save 400 static data into Neblina. We make 400 data run as a circle.
-% % For walking, one time swing arm need 1.2 second. Every 400 data must have 1 arm swing.
-% change epsilon in order to decrease compression radio, measuring energy consumption.
+\begin{table}[]
+    \begin{subfigure}{\columnwidth}
+    \centering
+    \begin{tabular}{l|l|l|l|l|l|l}
+    \hline
+    \rowcolor{headcolor}
+                           & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
+    $\epsilon$              & 100       & 20      & 10      & 100       & 20      & 10   \\
+    Max error              & 158.793   & 31.828  & 16.763  & 153.141   & 31.763  & 15.898  \\
+    Compr.      ratio      & 88.9\%    & 66.4\%  & 45.5\%  & 68.6\%    & 25.5\%  & 9.5\%   \\
+    Average mA    & 2.642     & 2.787   & 3.020   & 2.879     & 3.221   & 3.383   \\
+    Saved energy  & 23.9\%    & 19.7\%  & 13.0\%  & 17.0\%    & 7.18 \% & 2.50\%\\
+    \hline
+    \end{tabular}
+    \caption{Walking}
+    \end{subfigure}
+    \begin{subfigure}{\columnwidth}
+    \centering
+    \begin{tabular}{l|l|l|l|l|l|l}
+    \hline
+    \rowcolor{headcolor}
+                      & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
+    $\epsilon$         & 100      & 20       & 10      & 100      & 20       & 10      \\
+    Max error         & 99.995   & 19.984   & 9.979   & 99.995   & 19.989   & 9.959   \\
+    Compr.      ratio & 87.6\%   & 63.3\%   & 37.2\%  & 64.4\%   & 19.8\%   & 5.7\%   \\
+    Average mA      & 3.098    & 3.020    & 3.134   & 2.952    & 3.320    & 3.393   \\
+    Saved energy   &  10.7\%   & 13.0\%   & 9.68\%  & 14.9\%   & 4.32\%   & 2.22 \%\\
+    \hline
+    \end{tabular}
+    \caption{Running}
+    \end{subfigure}
+    \caption{Results from Experiment 2}
+    \label{table:results-energy}
+\end{table}
 
-% \todo {running}
-% If it's possible to save more static data?
+%~ and the battery usage 
+%~ would not change too much, because it contains others fusion method 
+%~ which will running when turning on the Neblina. In 50Hz sensor sampling 
+%~ rate, the average usage electric current for transmit accelerometer 
+%~ data is 2.0mA. It means Neblina could transmit accelerometer data 
+%~ constantly in 100/2.0=50 hours. when Neblina does not move, the average 
+%~ usage electric current using Infinity norm compression is 1.95mA.
 
-% \begin{itemize}
-%     \item Data set: human activities, running, walking, jogging and work behind desk.
-%     \item Experiment Condition: work with neblina.
-%     \item Result:
-%     \item Conclusion:
-% \end{itemize}
-
-% The transform rate of Neblina is 50Hz.
-% \\
-% 5-times bicep curl from Neblina. It includes 613 data which produced in 12.28 seconds.
-% \\
-% Mohammad Lateral bicep data which include 41428, produced in proximate 14 minutes.
-
-% \subsection{Compression ratios}
-
-% \subsection{Errors}
-
-% \subsection{Memory consumption}
+ %~ It 
+%~ just extend Neblina work life about 1.28 hours. But in 200Hz sampling 
+%~ rate. The electric before and after compression are 3.5 and 2.9 
+%~ respectively. The running time of Neblina would be extended about 5.9 
+%~ hours.
 
@@
 
+Euclidean norm would benefit from a better algorithm but it still
+provides interesting energy savings.
+
 \section*{Acknowledgement}
-
-\begin{table}[]
-    \begin{center}
-    \caption{result of Experiment 2 with walking Data Set}
-    \begin{tabular}{|l|l|l|l|l|l|l|}
-    \hline
-    DataSet           & \multicolumn{6}{l|}{walking}                                   \\\hline
-    Distance          & \multicolumn{3}{l|}{Manhattan} & \multicolumn{3}{l|}{Euclidean} \\\hline
-    Epsilon           & 100       & 20      & 10      & 100       & 20      & 10      \\\hline
-    Max Error         & 158.793   & 31.828  & 16.763  & 153.141   & 31.763  & 15.898  \\\hline
-    Compression Radio & 88.9\%    & 66.4\%  & 45.5\%  & 68.6\%    & 25.5\%  & 9.5\%   \\\hline
-    Energy Usage      & 2.642     & 2.787   & 3.020   & 2.879     & 3.221   & 3.383   \\\hline
-    \end{tabular}
-    \end{center}
-\end{table}
-
-\begin{table}[]
-    \begin{center}
-    \caption{result of Experiment 2 with running Data Set}
-    \begin{tabular}{|l|l|l|l|l|l|l|}
-    \hline
-    DataSet           & \multicolumn{6}{l|}{running}                                   \\\hline
-    Distance          & \multicolumn{3}{l|}{Manhattan} & \multicolumn{3}{l|}{Euclidean} \\\hline
-    Epsilon           & 100      & 20       & 10      & 100      & 20       & 10      \\\hline
-    Max Error         & 99.995   & 19.984   & 9.979   & 99.995   & 19.989   & 9.959   \\\hline
-    Compression Radio & 87.6\%   & 63.3\%   & 37.2\%  & 64.4\%   & 19.8\%   & 5.7\%   \\\hline
-    Energy Usage      & 3.098    & 3.020    & 3.134   & 2.952    & 3.320    & 3.393   \\\hline
-    \end{tabular}
-    \end{center}
-\end{table}
+This work was funded by the Canadian
 

### 2018-10-17 paper.tex
Added intro

@@
 
-\author{Bo Li, Tristan Glatard\\
-  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
-  {first.last}@concordia.ca \vspace*{-0.5cm}}
-
+\author{Bo Li$^1$, Omid Sarbishei$^2$, Tristan Glatard$^1$\\
+  $^1$ Department of Computer Science and Software Engineering, Concordia University, Montreal, QC, Canada \\
+  $^2$ Motsai, Saint Bruno, QC, Canada.}
 \maketitle
@@
 Lightweight Temporal Compression
-(LTC~\cite{schoellhammer2004lightweight}) is among the stream
-compression method that provides the highest compression rate for the
+(LTC) is among the lossy stream
+compression methods that provide the highest compression rate for the
 lowest resource (CPU, RAM) consumption. As such, it makes it a very
 good candidate for the compression of data streams acquired in
-embedded, low-power systems such as connected
-objects, systems on module (SoMs), etc The type of data acquired on
+energy-constrained systems such as systems on module (SoMs). The type of data acquired on
 such systems, however, is often multi-dimensional. For instance 
@@
 actual movement of the sensor. In this paper, we investigate the 
-extension of LTC to higher dimensions. First, we provide a formulation of the algorithm
-in an arbitrary vectorial space of dimension $n$. Furthermore, we
-implement the algorithm for the infinity and Euclidean norms, in spaces of
-dimension 2D+t and 3D+t. Finally, we compare the multi-dimensional LTC
-to the 1-dimensional version, on acceleration data acquired on a SoM
-device.
+extension of LTC to higher dimensions. First, we provide a formulation 
+of the algorithm in an arbitrary vectorial space of dimension $n$. 
+Then, we implement the algorithm for the infinity and Euclidean norms, 
+in spaces of dimension 2D+t and 3D+t. We evaluate our implementation on 
+3D acceleration streams acquired by a SoM during human activities. 
+Results show that the 3D implementation of LTC can save up to 20\% in 
+energy consumption for low-paced activities such as walking. The 
+implementation with the infinity norm only requires about 100~B of 
+memory.
 \end{abstract}
@@
 
-Section~\ref{sec:ltc} provides some background on the LTC algorithm.
-Section~\ref{sec:extension} presents our formulation in dimension $n$.
+% Compression of stream data
+% need references
+Compressing data streams is required in many contexts, to reduce 
+storage and network requirements of data analytics. In particular, it is 
+highly beneficial to energy-constrained devices such as Systems on 
+Modules (SoM), as they reduce the amount of energy-consuming radio transmissions.
+However, resource-intensive algorithms such as~\cite{x},~\cite{y} 
+or~\cite{z} are not well-suited for energy-constrained systems, due to 
+the limited memory available on these systems (typically a few KB), and 
+the energy consumption associated with CPU usage. On such systems, 
+compression algorithms need to find a trade-off between reducing 
+network communications and increasing memory and CPU usage. As 
+discussed in~\cite{zordan2014performance}, linear compression methods 
+provide a very good compromise between these two factors, leading to 
+substantial energy reduction.
 
-% Some related works from Bo's report
+% lossy vs lossless compression
 
-Compression reduces radio usage but increases resource usage.
+% LTC summary
+% define transmitted, received points, copmression ratio
+The Lightweight Temporal Compression method 
+(LTC~\cite{schoellhammer2004lightweight}) has been designed 
+specifically for energy-constrained systems, initially sensor networks. 
+It approximates data points by a piecewise linear function that 
+guarantees an upper bound on the reconstruction error. LTC is a very 
+lightweight method, with memory requirements in $\mathcal{O}(1)$. 
+However, LTC has only been described for 1D streams, which makes it 
+limited for multi-dimensional streams such as the ones coming from 
+accelerometers, gyroscopes and other movement sensors.
 
-% transmitted, received points
+In this paper, we extend LTC to dimension $n$. To do so, we propose an 
+algebraic formulation of the algorithm that also yields a 
+norm-independent expression of it. We implement our extension on 
+Motsai's Neblina module, and we test it on 3D acceleration streams 
+acquired during human exercises, namely biceps curling, walking and 
+running. Our implementation of LTC is available as free software on GitHub\todo{add link}.
 
-% contributions: formalization of LTC algorithm, extension to n d, extension to any norm, open-source implementation.
+We assume that the stream consists of a sequence of data points 
+received at uneven intervals. The compression algorithm 
+\emph{transmits} fewer points than it receives. The transmitted points 
+might be part of the stream, or computed from stream elements. The 
+\emph{compression ratio} is the ratio between the number of received 
+points and the number of transmitted points. An application would 
+reconstruct the stream from the transmitted points: the 
+\emph{reconstruction error} is the maximum absolute difference between 
+a data point of the reconstructed stream, and the corresponding data 
+point in the original stream.
+
+% Outline
+Section~\ref{sec:ltc} provides some background on the LTC algorithm, 
+and formalizes the description initially proposed 
+in~\cite{schoellhammer2004lightweight}. Section~\ref{sec:extension} 
+presents our norm-independent extension to dimension $n$, and 
+Section~\ref{sec:implementation} describes our implementation. 
+Section~\ref{sec:results} reports on experiments to validate our 
+implementation, and evaluate the impact of n-dimensional LTC on SoM 
+energy consumption.
+\begin{figure}
+\includegraphics[width=\columnwidth]{ltc.pdf}
+\caption{Illustration of the LTC algorithm and notations used. Red dots indicate transmitted points. Dashed lines
+represent the high line and the low line at times when a point is transmitted.}
+\label{fig:ltc}
+\end{figure}
 
@@
 Figure~\ref{fig:ltc} illustrates the notations and algorithm.
-\begin{figure}
-\includegraphics[width=\columnwidth]{ltc.pdf}
-\caption{Illustration of the LTC algorithm and notations used. Red dots indicate transmitted points. Dashed lines
-represent the high line and the low line at times when a point is transmitted.}
-\label{fig:ltc}
-\end{figure}
-\subsection{LTC algorithm}
 
@@
 \section{Implementation}
+\label{sec:implementation}
 Our code is available at ... (make a clean release!)
@@
 \section{Experiments and Results}
+\label{sec:results}
 

### 2018-10-17 paper.tex
Added conclusion

@@
 % need references
-Compressing data streams is required in many contexts, to reduce 
-storage and network requirements of data analytics. In particular, it is 
-highly beneficial to energy-constrained devices such as Systems on 
-Modules (SoM), as they reduce the amount of energy-consuming radio transmissions.
-However, resource-intensive algorithms such as~\cite{x},~\cite{y} 
-or~\cite{z} are not well-suited for energy-constrained systems, due to 
-the limited memory available on these systems (typically a few KB), and 
-the energy consumption associated with CPU usage. On such systems, 
-compression algorithms need to find a trade-off between reducing 
-network communications and increasing memory and CPU usage. As 
+Lossy compression of data streams is required in many contexts, to reduce 
+storage and network requirements of data analytics. In particular, it 
+is highly beneficial to energy-constrained devices such as Systems on 
+Modules (SoM), as they reduce the amount of energy-consuming radio 
+transmissions. However, resource-intensive algorithms such as the ones 
+based on polynomial interpolation or auto-regression 
+methods~\cite{lu2010optimized} are not well-suited for 
+energy-constrained systems, due to the limited memory available on 
+these systems (typically a few KB), and the energy consumption 
+associated with CPU usage. On such systems, compression algorithms need 
+to find a trade-off between reducing network communications and 
+increasing memory and CPU usage. As 
 discussed in~\cite{zordan2014performance}, linear compression methods 
@@
 acquired during human exercises, namely biceps curling, walking and 
-running. Our implementation of LTC is available as free software on GitHub\todo{add link}.
+running. Our implementation of LTC is available as free software.
 
@@
 \emph{transmits} fewer points than it receives. The transmitted points 
-might be part of the stream, or computed from stream elements. The 
+might be included in the stream, or computed from stream points. The 
 \emph{compression ratio} is the ratio between the number of received 
@@
 \emph{reconstruction error} is the maximum absolute difference between 
-a data point of the reconstructed stream, and the corresponding data 
+a point of the reconstructed stream, and the corresponding 
 point in the original stream.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{ltc.pdf}
+\caption{Illustration of the LTC algorithm and notations used. Blue 
+dots are received points, red dots are transmitted points. Dashed lines 
+represent the high line and the low line at times when a point is 
+transmitted.\vspace*{-0.3cm}}
+\label{fig:ltc}
+\end{figure}
 
@@
 energy consumption.
-\begin{figure}
-\includegraphics[width=\columnwidth]{ltc.pdf}
-\caption{Illustration of the LTC algorithm and notations used. Red dots indicate transmitted points. Dashed lines
-represent the high line and the low line at times when a point is transmitted.}
-\label{fig:ltc}
-\end{figure}
 
@@
 
-Euclidean norm would benefit from a better algorithm but it still
-provides interesting energy savings.
+We presented an extension of the Lightweight Temporal Compression 
+method to dimension $n$ that can be instantiated for any distance 
+function. Our extension formulates LTC as an intersection dection 
+problem between n-balls. We implemented our extension on a SoM for the 
+infinity and Euclidean norms, and we measured the energy reduction 
+resulting from compression for acceleration streams acquired during a 
+few human activities.
+
+We conclude from our experiments that the proposed extension to LTC is 
+well suited to reduce energy consumption on SoMs, as it reduce energy 
+consumption by up to 20\%. The implementation behaves better with the 
+infinity norm than with the Euclidean one, due to the lack of efficient 
+algorithms to detect the intersection between n-balls defined for the 
+Euclidean norms.
+
+Our future work focuses on this issue. Our current implementation with 
+the Euclidean norm relies on Helly's theorem, which only provides an 
+algorithm of complexity ${m \choose n+1}$ to compress $m$ points in 
+dimension $n$. We note that Helly's theorem works for arbitrary convex 
+subsets of $\mathbb{R}^n$, while we are considering a \emph{sequence} 
+of \emph{balls} of \emph{decreasing radius}. Based on this 
+observation, a stronger result might exist that would lead to a more 
+efficient implementation of LTC with the Euclidean norm. Our current 
+idea is to look for a point function of the ball centers that would 
+necessarily belong to the ball intersection when it is not empty; such 
+a point, if it exists, necessarily converges to the center of the last 
+ball in the sequence as $n$ increases, as the radius of the last ball
+decreases to zero.
+
+The effect of norm selection should not be underestimated. Some 
+situations might be better described with the Euclidean norm than with the
+infinity norm, such as the ones involving position or movement measures. 
+Using the infinity norm instead of the Euclidean would lead to important 
+error differences, proportional to $\sqrt{n}$ in dimension $n$.
 
 \section*{Acknowledgement}
-This work was funded by the Canadian
+This work was funded by a Strategic Project Grant of the Natural 
+Sciences and Engineering Research Council of Canada. We thank Hosein 
+Nourani for providing the data used in Experiment 1.
 

### 2018-10-17 paper.tex

@@
 
+\algblock{Input}{EndInput}
+\algnotext{EndInput}
+\algblock{Output}{EndOutput}
+\algnotext{EndOutput}
+\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
+
 % new commands
@@
 compression methods that provide the highest compression rate for the 
-lowest resource (CPU, RAM) consumption. As such, it makes it a very
-good candidate for the compression of data streams acquired in
-energy-constrained systems such as systems on module (SoMs). The type of data acquired on
-such systems, however, is often multi-dimensional. For instance 
-accelerometers and gyroscopes usually measure variables along 3 
-directions, these variables being distinct but related through the 
-actual movement of the sensor. In this paper, we investigate the 
-extension of LTC to higher dimensions. First, we provide a formulation 
+lowest CPU and memory consumption. As such, it is very well suited to 
+compress data streams in energy-constrained systems such as connected 
+objects. The current formulation of LTC, however, is one-dimensional 
+while data acquired in connected objects is often multi-dimensional: for instance, 
+accelerometers and gyroscopes usually measure variables along 
+3 directions related by the actual movement of the sensor. In this 
+paper, we investigate the extension of LTC to 
+higher dimensions. First, we provide a formulation 
 of the algorithm in an arbitrary vectorial space of dimension $n$. 
@@
 in spaces of dimension 2D+t and 3D+t. We evaluate our implementation on 
-3D acceleration streams acquired by a SoM during human activities. 
+3D acceleration streams acquired during human activities. 
 Results show that the 3D implementation of LTC can save up to 20\% in 
-energy consumption for low-paced activities such as walking. The 
-implementation with the infinity norm only requires about 100~B of 
-memory.
+energy consumption for low-paced activities, with a memory usage of about 100~B.
 \end{abstract}
@@
 
-% Compression of stream data
-% need references
-Lossy compression of data streams is required in many contexts, to reduce 
-storage and network requirements of data analytics. In particular, it 
-is highly beneficial to energy-constrained devices such as Systems on 
-Modules (SoM), as they reduce the amount of energy-consuming radio 
-transmissions. However, resource-intensive algorithms such as the ones 
-based on polynomial interpolation or auto-regression 
-methods~\cite{lu2010optimized} are not well-suited for 
+With the recent technological advances in Internet of Things (IoT) 
+applications, more than one billion connected objects are expected to 
+be launched worldwide by 2025\footnote{\url{ 
+https://www.statista.com/statistics/471264/iot-number-of-connected-devices-worldwide}} 
+Power consumption is amongst the biggest challenges targeting connected 
+objects, particularly in the industrial domains, where several sensing 
+systems are commonly launched in the field to run for days or even 
+weeks without being recharged. Typically, such devices use sensors to 
+capture properties such as temperature or motion, and stream them to a 
+host system over a radio transmission protocol such as Bluetooth 
+Low-Energy (BLE). System designers aim to reduce the rate of data 
+transmission as much as possible, as radio transmission is a 
+power-hungry operation.
+
+ Compression is a key technique to reduce the rate of radio 
+ transmission.  While in several applications lossless compression 
+ methods are more desirable than lossy compression techniques, in the 
+ context of IoT and sensor data streams, the measured sensor data 
+ intrinsically involves noise and measurement errors, which can 
+ be treated as a configurable 
+tolerance for a lossy compression algorithm.
+
+Resource-intensive lossy compression algorithms such as the ones based on 
+polynomial interpolation, discrete cosine and Fourier transforms, or 
+auto-regression methods~\cite{lu2010optimized} are not well-suited for 
 energy-constrained systems, due to the limited memory available on 
@@
 It approximates data points by a piecewise linear function that 
-guarantees an upper bound on the reconstruction error. LTC is a very 
-lightweight method, with memory requirements in $\mathcal{O}(1)$. 
-However, LTC has only been described for 1D streams, which makes it 
-limited for multi-dimensional streams such as the ones coming from 
-accelerometers, gyroscopes and other movement sensors.
+guarantees an upper bound on the reconstruction error, and a reduced 
+memory footprint in $\mathcal{O}(1)$. However, LTC has only been 
+described for 1D streams, while streams acquired by connected objects, such as 
+acceleration or gyroscopic data, are often multi-dimensional.
 
@@
 \emph{compression ratio} is the ratio between the number of received 
-points and the number of transmitted points. An application would 
-reconstruct the stream from the transmitted points: the 
+points and the number of transmitted points. An application 
+reconstructs the stream from the transmitted points: the 
 \emph{reconstruction error} is the maximum absolute difference between 
@@
 \end{figure}
+\todo{show $\xi$ in the Figure}
 
@@
 Section~\ref{sec:results} reports on experiments to validate our 
-implementation, and evaluate the impact of n-dimensional LTC on SoM 
-energy consumption.
+implementation, and evaluates the impact of n-dimensional LTC on 
+energy consumption of connected objects.
 
@@
 by a piece-wise linear function of time, ensuring that the error at
-every time-point is bounded.
+every time-point is bounded by parameter $\epsilon$.
 
@@
 
-The algorithm \emph{receives} a stream of \emph{data points} $x_i$
-at times $t_i$ ($i \in \mathbb{N}$), and it \emph{transmits} a stream of data points $\xi_i$
+The algorithm receives a stream of data points $x_i$
+at times $t_i$ ($i \in \mathbb{N}$), and it transmits a stream of data points $\xi_i$
 at times $\tau_i$ ($i \in \mathbb{N}$). To simplify the notations, we assume that:
@@
 That is, transmission times coincide with reception times.
-We define the \emph{centered received points} as follows:
+We define the \emph{shifted received points} as follows:
 \begin{equation*}
-\forall k \in \mathbb{N}\ , \forall j \in \mathbb{N^*},\ (u^k_j, y^k_j) = (t_{i+j}, x_{i+j}), \quad \mathrm{where\ }i\mathrm{\ is\ s.t.}\ t_i = \tau_k.
+\forall k \in \mathbb{N}\ , \forall j \in \mathbb{N^*},\ (u^k_j, y^k_j) = (t_{i+j}, x_{i+j}), 
 \end{equation*}
-and:
+where $i$ is such that $t_i = \tau_k$ and:
 \begin{equation*}
@@
 This definition is such that $y^k_j$ is the $j^{th}$ data point received
-after the $k^{th}$ transmission.
+after the $k^{th}$ transmission and $u^k_j$ is the corresponding timestamp.
 Figure~\ref{fig:ltc} illustrates the notations and algorithm.
@@
 \begin{algorithmic}[1]
+\Input
+   \Desc{$(u^k_j, y^k_j)$}{$\quad \quad $Received data stream}
+   \Desc{$\epsilon$}{$\quad \quad$Error bound}
+\EndInput
+\Output
+   \Desc{tr}{Transmitted points}
+\EndOutput
 \State tr = $(u^0_0, y^0_0)$ \Comment{last transmitted point}
@@
     \If{new\_lp $<$ new\_hp} \Comment{Keep compressing}
-        \State (lp = new\_lp, new\_hp)
+        \State (lp, hp) = (new\_lp, new\_hp)
         \State \textbf{continue}
@@
 Let $(u_0^k, y_0^k) \in \mathbb{R}^{n+1}$ be the latest transmitted point. For convenience, all the subsequent points will be
-expressed in the orthogonal space with origin $(\tau^k, \xi^k)$. We denote by $(v_j, z_j)_{j \in \llbracket 0, m \rrbracket}$ such points:
+expressed in the orthogonal space with origin $(\tau_k, \xi_k)$. We denote by $(v_j, z_j)_{j \in \llbracket 0, m \rrbracket}$ such points:
 \begin{equation*}
-\forall j \leq m,\  (v_j, z_j) = (u_j^k - \tau^k, y_j^k - \xi^k)
+\forall j \leq m,\  (v_j, z_j) = (u_j^k - \tau_k, y_j^k - \xi_k)
 \end{equation*}
-We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $\frac{1}{j}z_j$ and of radius
-$\frac{\epsilon}{j}$:
+We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $\frac{v_1}{v_j}z_j$ and of radius
+$\frac{v_1}{v_j}\epsilon$:
 \begin{equation*}
@@
 
-\subsection{LTC property}
+\subsubsection{LTC property}
 
@@
 \end{equation*}
-The LTC algorithm ensures that the LTC property is
+The original LTC algorithm ensures that the LTC property is
 verified between each transmission. Indeed, all the data points
@@
 such a point exists.
-The LTC property can be written as follows:
+
+The LTC property can be re-written as follows:
 \begin{equation*}
@@
 of balls of strictly decreasing radius, since $v_j > v_1$.
-\todo{Add a figure to illustrate this}
 
@@
 
-The LTC algorithm generalized to dimension $n$ test, for each data point,
-that the LTC property in Equation~\ref{eq:ltc-property} is verified. It is written in
-Algorithm~\ref{algo:general-ltc}.
+The LTC algorithm generalized to dimension $n$ tests that the LTC 
+property in Equation~\ref{eq:ltc-property} is verified after each reception of a data 
+point. It is written in Algorithm~\ref{algo:general-ltc}.
 \begin{algorithm}
 \begin{algorithmic}[1]
+\Input
+   \Desc{$(u^k_j, y^k_j)$}{$\quad \quad $Received data stream}
+   \Desc{$\epsilon$}{$\quad \quad$Error bound}
+\EndInput
+\Output
+   \Desc{tr}{Transmitted points}
+\EndOutput
+
 \State tr = ($\tau, \xi$) = ($u^0_0, y^0_0$)
@@
 \end{theorem}
-This theorem leads to an algorithm of complexity ${m \choose n+1}$ which is
+\noindent This theorem leads to an algorithm of complexity ${m \choose n+1}$ which is
 not usable in resource-constrained environment.
@@
 maintains a representation of the intersection
-$\bigcap_{j=1}^{m}{\mathcal{B}_m}$ which is updated at every iteration.
-The intersection tests can then be done in constant time, however,
-updating the representation of the intersection may be more costly
+$\bigcap_{j=1}^{m}{\mathcal{B}_j}$ which is updated at every iteration.
+The intersection tests can then be done in constant time. However,
+updating the representation of the intersection may be costly
 depending on the norm used. For the infinity norm, the representation
@@
 intersection with an n-ball, since the n-ball is a rectangular cuboid too.
-For the Euclidean norm, the representation is a volume with no specific property,
+For the Euclidean norm, the representation is a volume with no particular property,
 which is more costly to maintain.
@@
 let us consider the comparison between the infinity norm and the
-Euclidean norm in dimension 2. By comparing the unit disk to the unit
-square, we obtain that the compression ratio of a random stream would
+Euclidean norm in dimension 2. By comparing the unit disk to a
+square of side 2, we obtain that the compression ratio of a random stream would
 be $\frac{4}{\pi}$ times larger with the infinity norm than with the 
@@
 
-\todo{Perhaps add a figure}
-
-It should also be noted that using the infinity norm boils down to the
-use of the 1D LTC algorithm independently in each dimension: a data
-point is transmitted as soon as the linear approximation doesn't hold
-in any of the coordinates. \todo{This is unclear}
+It should also be noted that using the infinity norm in dimension $n$ 
+boils down to the use of the 1D LTC algorithm independently in each 
+dimension, since a data point will be transmitted as soon as the linear 
+approximation doesn't hold in any of the dimensions.
 
@@
 Our code is available at ... (make a clean release!)
+
+\todo{explain difference between exp 1 and exp 2 for euclidean}
 
@@
 
+\todo{talk about data shift}
+
 We conducted two experiments using Motsai's Neblina 
@@
 with a Nordic Semiconductor nRF52832 micro-controller, 64~KB of RAM, 
-and Bluetooth Low Energy connectivity. The Neblina has a 3D 
-accelerometer, a 3D gyroscope, a 3D magnetometer, and environmental sensors 
-for humidity, temperature and pressure. It can function as an Inertial 
-Motion Unit, a Vertical Reference Unit, or an Attitude and Heading 
-Reference System. The Neblina has a battery of 100mAh; its average 
-consumption is 2.52~mA without radio transmission and 3.47~mA with 
-radio transmission, leading to an autonomy of 39.7~h without 
-transmission and 28.8~h with transmission. \todo{Omid, could you review
-this paragraph?}
+and Bluetooth Low Energy connectivity. Neblina has a 3D 
+accelerometer, a 3D gyroscope, a 3D magnetometer, and environmental 
+sensors for humidity, temperature and pressure. The platform is 
+equipped with sensor fusion algorithms for 3D orientation tracking and 
+a machine learning engine for complex motion analysis and motion 
+pattern recognition~\cite{sarbishei2016accuracy}. Neblina has a 
+battery of 100mAh; its average consumption is 2.52~mA when using 
+accelerometer and gyroscope sensors at 200~Hz but without radio 
+transmission, and 3.47~mA with radio transmission, leading to an 
+autonomy of 39.7~h without transmission and 28.8~h with transmission.
 
-\subsection{Experiment 1: validation tests}
+\subsection{Experiment 1: validation}
 
-In this experiment we validated the behavior of our LTC extensions on a 
-PC processing data acquired with the Neblina. We collected two 3D 
+\todo{In all of our experiments, the board was attached to the lower 
+right arm as shown in Fig. X. (Put a picture of Neblina in a box worn 
+on the wrist)}
+
+In this experiment, we validated the behavior of our LTC extension on a 
+PC using data acquired with Neblina. We collected two 3D 
 accelerometer time series, a short one and a longer one, acquired 
@@
 \includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-z.pdf}
-\caption{Short}
+\caption{Short biceps curl}
 \end{subfigure}
@@
 \includegraphics[width=0.33\columnwidth]{figures/Mohammad-bicep-curl-plot-z.pdf}
-\caption{Long} 
+\caption{Long biceps curl} 
 \end{subfigure}
@@
 
-We compressed the time series with various values of $\epsilon$, using our 
-2D (x and y) and 3D (x, y and z) implementations of LTC. On the Neblina,
-the resolution of the accelerometer is about 20~mg (196~mm/$s^2$).
- We used a 
-laptop computer with 16~GB of memory, and Intel i5-3210M CPU @ 2.50GHz 
+We compressed the time series with various values of $\epsilon$, using 
+our 2D (x and y) and 3D (x, y and z) implementations of LTC. On 
+Neblina, the raw uncalibrated accelerometer data corresponds to errors 
+around 20~mg (196~mm/$s^2$). \todo{Check g units} We used a 
+laptop computer with 16~GB of RAM, an Intel i5-3210M CPU @ 2.50GHz 
 × 4, and Linux Fedora 27. We measured memory consumption using 
@@
 \paragraph{Inifinity vs Euclidean norms}
-Compared to the infinity norm, The average ratio between the compression ratios obtained
+Compared to the infinity norm, the average ratio between the compression ratios obtained
 with the infinity and Euclidean norm is 1.08 for 2D data, and 1.20 
@@
 infinity norm requires a constant amount of 80~B, used to store the 
-intersection of n-balls. This amount is realistic on modules such as
-the Neblina. The Euclidean norm, however, uses up to 4.9~KB of memory 
-on the Long time series in 3D with $\epsilon=100$. More importantly, 
+intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory 
+for the Long time series in 3D with $\epsilon=100$. More importantly, 
 the amount of required memory increases for more complex time series 
@@
 smallest $\epsilon$, to 26.4~ms for the most complex time series and 
-largest $\epsilon$. A better algorithm needs to be found to make the 
-Euclidean norm usable for systems on modules.
+largest $\epsilon$.
 
@@
 ratios are always higher in 2D than in 3D. It makes sense since the 
-\todo{x} is higher in 3D than it is in 2D. Resource consumption is 
-higher in 3D than in 2D: for the infinity norm, 3D consumes 1.4 times 
-more memory than 2D (1.6 times on average for Euclidean norm), and 
-processing time is 1.3 longer on average (1.18 on average for Euclidean 
-norm).
+probability for the signal to deviate from a straight line 
+approximation is higher in 3D than it is in 2D. Besides, resource 
+consumption is higher in 3D than in 2D: for the infinity norm, 3D 
+consumes 1.4 times more memory than 2D (1.6 times on average for 
+Euclidean norm), and processing time is 1.3 longer on average (1.18 on 
+average for Euclidean norm).
 
@@
     \end{tabular}
-    \caption{Short (2D)}
+    \caption{Short biceps curl (2D)}
     \end{subfigure}\\
@@
     Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\ 
-    Peak memory       & 80~B        & 80~B               & 2.1~KB      & 1.3~KB             \\ 
+    Peak memory       & 80~B        & 80~B               & 2.1~KB      & 2.5~KB             \\ 
     Processing time      & 5.70~ms     & 4.85~ms            & 20.04~ms    & 19.28~ms           \\ \hline
     \end{tabular}
-    \caption{Long (2D)}
+    \caption{Long biceps curl (2D)}
     \end{subfigure}\\    
@@
     \end{tabular}
-    \caption{Short (3D)}
+    \caption{Short biceps curl (3D)}
     \end{subfigure}\\
@@
     \end{tabular}
-    \caption{Long (3D)}
+    \caption{Long biceps curl (3D)}
     \end{subfigure}
@@
 
-\subsection{Experiment 2: impact on energy consumption}
-
-We measured the energy consumption of the Neblina module 
-for different values of $\epsilon$ and norms, to quantify the 
-added-value of LTC for this system.
-
-We acquired two 3D accelerometer time series at 200Hz corresponding to 
-common human activities: walking and running (see Figure~\ref{fig:datasets-2}). In both cases, the 
-subject was wearing the Neblina module on their right wrist.
-We collected 1,000 data points for each activity, corresponding to 
-5 seconds of activity.
 \begin{figure*}
@@
 \end{figure*}
+\subsection{Experiment 2: impact on energy consumption}
+
+We measured the energy consumption of Neblina
+for different values of $\epsilon$ and norms, to quantify the 
+added-value of LTC for this system.
+
+We acquired two 3D accelerometer time series at 200Hz corresponding to 
+common human activities: walking and running (see Figure~\ref{fig:datasets-2}). In both cases, the 
+subject was wearing Neblina on their right wrist.
+We collected 1,000 data points for each activity, corresponding to 
+5 seconds of activity.
 
@@
 these time series, for different norms and $\epsilon$ values. To do so, 
-we 'replayed' the time series by loading them as a byte array in the 
-Neblina, and we measured current intensity every 500~ms.
+we `replayed' the time series by loading them as a byte array in 
+Neblina, and we measured the current every 500~ms.
 
-Results are reported in Table~\ref{table:results-energy}\todo{errors don't make sense}.
-For a given $\epsilon$ and norm, the compression ratio was larger for 
-walking than for running, since the running signal had a higher 
-entropy. The ratio of saved energy is relative to the reference current of 
-3.47~mA measured when the Neblina transmits data without compression.
-In all cases, activating compression saved energy. The reduction in energy
-consumption behaved as the compression ratio: it increased with $\epsilon$,
-was higher for the infinity norm than for the Euclidean, and it was 
+ Results are reported in Table~\ref{table:results-energy}. For a given 
+ $\epsilon$ and norm, the compression ratio is larger for walking than 
+ for running. The ratio of saved energy is relative to the reference 
+ current of 3.47~mA measured when Neblina transmits data without 
+ compression. In all cases, activating compression saves energy. The 
+ reduction in energy consumption behaves as the compression ratio: it 
+ increases with $\epsilon$,
+it is higher for the infinity norm than for the Euclidean, and it is
 higher for the walking activity than for running. For a realistic error 
 of $\epsilon=20$\todo{unit}, the ratio of saved energy with the infinity norm was
-close to 20\%, which is very substantial.
+close to 20\%, which is substantial.
 
@@
    $\epsilon$              & 100       & 20      & 10       & 100      & 20       & 10    \\
-    Max error              & 158.793   & 31.828  & 16.763  & 153.141   & 31.763  & 15.898  \\
-    Compr.      ratio      & 88.9\%    & 66.4\%  & 45.5\%  & 68.6\%    & 25.5\%  & 9.5\%   \\
-    Average mA    & 2.642     & 2.787   & 3.020   & 2.879     & 3.221   & 3.383   \\
-    Saved energy  & 23.9\%    & 19.7\%  & 13.0\%  & 17.0\%    & 7.18 \% & 2.50\%\\
+   Max error              & 99.97     & 20.00        & 10.00      & 99.99   & 19.98   & 9.98  \\
+   Compr.      ratio      & 88.9\%    & 66.4\%  & 45.5\%   & 87.6\%   & 63.3\%   & 37.2\% \\
+   Average mA                & 2.64     & 2.79   & 3.02   & 3.10    & 3.02    & 3.13  \\
+   Saved energy              & 23.9\%    & 19.7\%  & 13.0\%  &  10.7\%   & 13.0\%   & 9.68\%\\
    \hline
@@
    \rowcolor{headcolor}
+
                      & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
    $\epsilon$        & 100       & 20      & 10         & 100      & 20       & 10      \\
-    Max error         & 99.995   & 19.984   & 9.979   & 99.995   & 19.989   & 9.959   \\
-    Compr.      ratio & 87.6\%   & 63.3\%   & 37.2\%  & 64.4\%   & 19.8\%   & 5.7\%   \\
-    Average mA      & 3.098    & 3.020    & 3.134   & 2.952    & 3.320    & 3.393   \\
-    Saved energy   &  10.7\%   & 13.0\%   & 9.68\%  & 14.9\%   & 4.32\%   & 2.22 \%\\
+   Max error         & 100.00       & 20.00        & 10.00        & 100.00   & 19.99   & 9.96   \\
+   Compr.      ratio & 68.6\%    & 25.5\%  & 9.5\%     & 64.4\%   & 19.8\%   & 5.7\%   \\
+   Average mA        & 2.88     & 3.22   & 3.38     & 2.95    & 3.32    & 3.39   \\
+   Saved energy      & 17.0\%    & 7.18 \%   & 2.50\%   & 14.9\%   & 4.32\%   & 2.22 \%\\
    \hline
@@
 method to dimension $n$ that can be instantiated for any distance 
-function. Our extension formulates LTC as an intersection dection 
-problem between n-balls. We implemented our extension on a SoM for the 
+function. Our extension formulates LTC as an intersection detection 
+problem between n-balls. We implemented our extension on Neblina for the 
 infinity and Euclidean norms, and we measured the energy reduction 
-resulting from compression for acceleration streams acquired during a 
-few human activities.
+induced by compression for acceleration streams acquired during
+ human activities.
 
 We conclude from our experiments that the proposed extension to LTC is 
-well suited to reduce energy consumption on SoMs, as it reduce energy 
-consumption by up to 20\%. The implementation behaves better with the 
-infinity norm than with the Euclidean one, due to the lack of efficient 
-algorithms to detect the intersection between n-balls defined for the 
-Euclidean norms.
+well suited to reduce energy consumption in connected objects. The implementation 
+behaves better with the infinity norm than with the Euclidean one, due 
+to the time complexity of the current algorithm to detect the intersection 
+between n-balls for the Euclidean norm.
 
-Our future work focuses on this issue. Our current implementation with 
-the Euclidean norm relies on Helly's theorem, which only provides an 
-algorithm of complexity ${m \choose n+1}$ to compress $m$ points in 
-dimension $n$. We note that Helly's theorem works for arbitrary convex 
+Our future work focuses on this latter issue. Our current 
+implementation of LTC with Euclidean norm relies on Helly's theorem, 
+which only provides an algorithm of complexity ${m \choose n+1}$ to 
+compress $m$ points in 
+dimension $n$. We note that Helly's theorem holds for arbitrary convex 
 subsets of $\mathbb{R}^n$, while we are considering a \emph{sequence} 
@@
 efficient implementation of LTC with the Euclidean norm. Our current 
-idea is to look for a point function of the ball centers that would 
+idea is to search for a point expressed as a function of the ball centers that would 
 necessarily belong to the ball intersection when it is not empty; such 
@@
 ball in the sequence as $n$ increases, as the radius of the last ball 
-decreases to zero.
+decreases to zero. The resulting algorithm would then compute this 
+point and check its inclusion in every ball, which is done in 
+$\mathcal{O}(m)$ complexity.
 
-The effect of norm selection should not be underestimated. Some 
-situations might be better described with the Euclidean norm than with the
-infinity norm, such as the ones involving position or movement measures. 
-Using the infinity norm instead of the Euclidean would lead to important 
-error differences, proportional to $\sqrt{n}$ in dimension $n$.
+The choice of an appropriate norm should not be underestimated. This problem 
+is specific to multi-dimensional streams, since all common norms are 
+identical in 1D. Some situations might be better described with the 
+Euclidean norm than with the infinity norm, such as the ones involving 
+position or movement measures. Using the infinity norm instead of the 
+Euclidean would lead to important error differences, proportional to 
+$\sqrt{n}$ in dimension $n$. A better algorithm to detect the 
+intersection of n-balls in our context would improve the efficiency of LTC
+in dimension $n$ for arbitrary norms.
 

### 2018-10-17 paper.tex
conver epsilon to G range

@@
                            & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
-    $\epsilon$                & 100          & 100/$\sqrt{2}$  & 100         & 100/$\sqrt{2}$ \\
-    Max error              & 99.88       & 70.68           & 99.63       & 70.47          \\ 
+    $\epsilon$                & 48.8~mg          & 34.5~mg  & 48.8~mg         & 34.5~mg \\
+    Max error              & 48.8~mg       & 34.5~mg           & 48.6~mg       & 34.4~mg          \\
     Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\
@@
                    & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
-    $\epsilon$             & 100        & 100/$\sqrt{2}$    & 100        & 100/$\sqrt{2}$    \\ 
-    Max error              & 99.99     & 70.71             & 99.99      & 70.71             \\ 
+    $\epsilon$             & 48.8~mg        & 34.5~mg    & 48.8~mg        & 34.5~mg    \\
+    Max error              & 48.8~mg     & 34.5~mg   &48.8~mg       & 34.5~mg             \\
     Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\
@@
                             & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
-    $\epsilon$             & 100          & 100/$\sqrt{3}$  & 100         & 100/$\sqrt{3}$   \\ 
-    Max error              & 99.88       & 57.41           & 99.94       & 56.89            \\ 
+    $\epsilon$             & 48.8~mg          & 28.2~mg  & 48.8~mg         & 28.2~mg   \\
+    Max error              & 48.8~mg       & 28.0~mg           & 48.8~mg       & 27.8~mg            \\
     Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\
@@
                               & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
-    $\epsilon$                & 100        & 100/$\sqrt{3}$    & 100        & 100/$\sqrt{3}$    \\
-    Max error                 & 99.96     & 57.73             & 99.99      & 57.73             \\
+    $\epsilon$                & 48.8~mg        & 28.2~mg    & 48.8~mg        & 28.2~mg    \\
+    Max error                 & 48.8~mg     & 28.2~mg             & 48.8~mg      & 28.2~mg             \\
     Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\
@@
 higher for the walking activity than for running. For a realistic error
-of $\epsilon=20$\todo{unit}, the ratio of saved energy with the infinity norm was
+of $\epsilon=9.8~mg$\todo{unit}, the ratio of saved energy with the infinity norm was
 close to 20\%, which is substantial.
@@
                           & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
-   $\epsilon$              & 100       & 20      & 10       & 100      & 20       & 10    \\
-   Max error              & 99.97     & 20.00        & 10.00      & 99.99   & 19.98   & 9.98  \\
+   $\epsilon$ (mg)             & 48.8       & 9.8      & 4.9       & 48.8      & 9.8       & 4.9    \\
+   Max error (mg)              & 48.8     & 9.8        & 4.9      & 48.8   & 9.8   & 4.9  \\
    Compr.      ratio      & 88.9\%    & 66.4\%  & 45.5\%   & 87.6\%   & 63.3\%   & 37.2\% \\
-   Average mA                & 2.64     & 2.79   & 3.02   & 3.10    & 3.02    & 3.13  \\
+   Average (mA)                & 2.64     & 2.79   & 3.02   & 3.10    & 3.02    & 3.13  \\
    Saved energy              & 23.9\%    & 19.7\%  & 13.0\%  &  10.7\%   & 13.0\%   & 9.68\%\\
@@
                      & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
-   $\epsilon$        & 100       & 20      & 10         & 100      & 20       & 10      \\
-   Max error         & 100.00       & 20.00        & 10.00        & 100.00   & 19.99   & 9.96   \\
+   $\epsilon$ (mg)        & 48.8       & 9.8      & 4.9       & 48.8      & 9.8       & 4.9    \\
+   Max error (mg)         & 48.8       & 9.8        & 4.9        & 48.8   &9.8    & 4.9   \\
    Compr.      ratio & 68.6\%    & 25.5\%  & 9.5\%     & 64.4\%   & 19.8\%   & 5.7\%   \\
-   Average mA        & 2.88     & 3.22   & 3.38     & 2.95    & 3.32    & 3.39   \\
+   Average (mA)        & 2.88     & 3.22   & 3.38     & 2.95    & 3.32    & 3.39   \\
    Saved energy      & 17.0\%    & 7.18 \%   & 2.50\%   & 14.9\%   & 4.32\%   & 2.22 \%\\

### 2018-10-17 paper.tex
Some corrections

--- 2018-10-17 paper.tex
@@
   $^1$ Department of Computer Science and Software Engineering, Concordia University, Montreal, QC, Canada \\
-  $^2$ Motsai, Saint Bruno, QC, Canada.}
+  $^2$  Research and Development Department, Motsai Research, Saint Bruno, QC, Canada}
 \maketitle
@@
 
-\todo{In all of our experiments, the board was attached to the lower 
-right arm as shown in Fig. X. (Put a picture of Neblina in a box worn 
+\todo{(Put a picture of Neblina in a box worn 
 on the wrist)}
@@
 on two different subjects performing biceps curl, with a 50Hz sampling rate (see 
-Figure~\ref{fig:datasets-1}). It should be noted that the longer dataset also has 
+Figure~\ref{fig:datasets-1}). In both cases, the 
+subject was wearing Neblina on their right wrist. It should be noted that the longer dataset also has 
 a higher amplitude, most likely due to differences between subjects.
@@
 \includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-z.pdf}
-\caption{Short biceps curl}
+\caption{Short biceps curl$^a$}
 \end{subfigure}
@@
 \end{subfigure}
-\caption{Time series used in Experiment 1}
+\caption{Time series used in Experiment 1\\
+{\footnotesize $^a$ Average of az data is -7.81g. It was shifted to 0 so that the graphs can all use the same y scale.}}
 \label{fig:datasets-1}
@@
 smallest $\epsilon$, to 26.4~ms for the most complex time series and 
-largest $\epsilon$.
+largest $\epsilon$. Figure~\ref{fig:memory} shows the memory consumption 
+of the 3D Euclidean implementation for $\epsilon=48.8~mg$: peaks appear
+at the end of long compressed ranges where the signal was $\epsilon$-closed
+to the linear approximation.
 
@@
 \end{figure*}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{./figures/memory-mohammad.pdf}
+\caption{Memory usage of 3D Euclidean implementation, long biceps curl time series, $\epsilon$=48.8~mg.}
+\label{fig:memory}
+\end{figure}
+
 \subsection{Experiment 2: impact on energy consumption}
@@
 $\sqrt{n}$ in dimension $n$. A better algorithm to detect the 
-intersection of n-balls in our context would improve the efficiency of LTC
-in dimension $n$ for arbitrary norms.
+intersection of n-balls in our context would improve the efficiency of 
+LTC in dimension $n$ for arbitrary norms. Investigating other norms, in 
+particular the 1-norm, would be relevant too.
 

### 2018-10-17 paper.tex
fix yrange of figures and fix epsilon

--- 2018-10-17 paper.tex
@@
 intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory
-for the Long time series in 3D with $\epsilon=100$. More importantly, 
+for the Long time series in 3D with $\epsilon=48.8~mg$. More importantly,
 the amount of required memory increases for more complex time series
@@
 \paragraph{2D vs 3D}
-For a given $\epsilon$ of 100 and a given time series, the compression 
+For a given $\epsilon$ of 48.8~mg and a given time series, the compression 
 ratios are always higher in 2D than in 3D. It makes sense since the

### 2018-10-17 paper.tex

--- 2018-10-17 paper.tex
@@
 smallest $\epsilon$, to 26.4~ms for the most complex time series and
-largest $\epsilon$. Figure~\ref{fig:memory} shows the memory consumption 
+largest $\epsilon$.Figure~\ref{fig:memory} shows the memory consumption 
 of the 3D Euclidean implementation for $\epsilon=48.8~mg$: peaks appear

### 2018-10-17 paper.tex
Minor fixes

--- 2018-10-17 paper.tex
@@
 
-\todo{talk about data shift}
-
 We conducted two experiments using Motsai's Neblina 
@@
 Neblina, the raw uncalibrated accelerometer data corresponds to errors 
-around 20~mg (196~mm/$s^2$). \todo{Check g units} We used a 
+around 20~mg (1~g is 9.8~m/s$^2$). We used a 
 laptop computer with 16~GB of RAM, an Intel i5-3210M CPU @ 2.50GHz 
@@
 largest $\epsilon$. Figure~\ref{fig:memory} shows the memory consumption 
-of the 3D Euclidean implementation for $\epsilon=48.8~mg$: peaks appear
+of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear
 at the end of long compressed ranges where the signal was $\epsilon$-closed
@@
 higher for the walking activity than for running. For a realistic error
-of $\epsilon=9.8~mg$\todo{unit}, the ratio of saved energy with the infinity norm was
+of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm was
 close to 20\%, which is substantial.

### 2018-10-17 paper.tex

@@
 
-\paragraph{Inifinity vs Euclidean norms}
+\paragraph{Infinity vs Euclidean norms}
 Compared to the infinity norm, the average ratio between the compression ratios obtained
@@
 intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory
-for the Long time series in 3D with $\epsilon=100$. More importantly, 
+for the Long time series in 3D with $\epsilon$=48.8~mg. More importantly,
 the amount of required memory increases for more complex time series
@@
 smallest $\epsilon$, to 26.4~ms for the most complex time series and
-largest $\epsilon$. Figure~\ref{fig:memory} shows the memory consumption 
+largest $\epsilon$.Figure~\ref{fig:memory} shows the memory consumption 
 of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear

### 2018-10-17 paper.tex
Some fixes

@@
                            & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
-    $\epsilon$                & 48.8~mg          & 34.5~mg  & 48.8~mg         & 34.5~mg \\
-    Max error              & 48.8~mg       & 34.5~mg           & 48.6~mg       & 34.4~mg          \\
-    Compression ratio      & 29.03\%      & 20.88\%         & 25.12\%     & 19.57\%        \\
-    Peak memory            & 80~B          & 80~B             & 432~B        & 240~B           \\
-    Processing time        & 0.103~ms      & 0.082~ms         & 0.220~ms     & 0.200~ms        \\ \hline
+    $\epsilon$  (mg)          & 48.8         & 34.5       & 48.8       & 34.5 \\
+    Max error   (mg)          & 48.8         & 34.5       & 48.6       & 34.4 \\
+    Compression ratio (\%)    & 29.03        & 20.88      & 25.12      & 19.57\\
+    Peak memory   (B)         & 80           & 80         & 432        & 240  \\
+    Processing time (ms)      & 0.103        & 0.082      & 0.220s     & 0.200\\ \hline
     \end{tabular}
@@
                    & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
-    $\epsilon$             & 48.8~mg        & 34.5~mg    & 48.8~mg        & 34.5~mg    \\
-    Max error              & 48.8~mg     & 34.5~mg   &48.8~mg       & 34.5~mg             \\
-    Compression ratio      & 60.17\%    & 51.59\%           & 57.75\%    & 48.86\%           \\
-    Peak memory       & 80~B        & 80~B               & 2.1~KB      & 2.5~KB             \\
-    Processing time      & 5.70~ms     & 4.85~ms            & 20.04~ms    & 19.28~ms           \\ \hline
+    $\epsilon$ (mg)            & 48.8        & 34.5       & 48.8        & 34.5    \\
+    Max error  (mg)            & 48.8        & 34.5       & 48.8        & 34.5             \\
+    Compression ratio (\%)     & 60.17       & 51.59      & 57.75       & 48.86           \\
+    Peak memory  (B)           & 80          & 80         & 2100        & 2500             \\
+    Processing time (ms)       & 5.70        & 4.85       & 20.04       & 19.28           \\ \hline
     \end{tabular}
@@
                            & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
-    $\epsilon$             & 48.8~mg          & 28.2~mg  & 48.8~mg         & 28.2~mg   \\
-    Max error              & 48.8~mg       & 28.0~mg           & 48.8~mg       & 27.8~mg            \\
-    Compression ratio      & 23.00\%      & 12.89\%         & 18.43\%     & 9.95\%           \\
-    Peak memory            & 112~B         & 112~B            & 384~B        & 256~B             \\
-    Processing time        & 0.119~ms      & 0.094~ms         & 0.230~ms     & 0.200~ms          \\ \hline
+    $\epsilon$ (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
+    Max error  (mg)        & 48.8          & 28.0          & 48.8   & 27.8   \\
+    Compression ratio (\%) & 23.00         & 12.89         & 18.43  & 9.95   \\
+    Peak memory (B)        & 112           & 112           & 384    & 256    \\
+    Processing time (ms)   & 0.119         & 0.094         & 0.230  & 0.200  \\ \hline
     \end{tabular}
@@
                               & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
-    $\epsilon$                & 48.8~mg        & 28.2~mg    & 48.8~mg        & 28.2~mg    \\
-    Max error                 & 48.8~mg     & 28.2~mg             & 48.8~mg      & 28.2~mg             \\
-    Compression ratio         & 51.13\%    & 37.17\%           & 46.05\%    & 32.63\%           \\
-    Peak memory & 112~B        & 112~B              & 4.9~KB      & 3.0~KB             \\
-    Processing time           & 8.50~ms     & 7.07~ms            & 26.41~ms    & 21.26~ms           \\ \hline
+    $\epsilon$ (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
+    Max error  (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
+    Compression ratio (\%)         & 51.13       & 37.17      & 46.05    & 32.63   \\
+    Peak memory (B)                & 112         & 112        & 4900     & 3000    \\
+    Processing time (ms)           & 8.50        & 7.07       & 26.41    & 21.26   \\ \hline
     \end{tabular}
@@
    Max error (mg)              & 48.8     & 9.8        & 4.9      & 48.8   & 9.8   & 4.9  \\
-   Compr.      ratio      & 88.9\%    & 66.4\%  & 45.5\%   & 87.6\%   & 63.3\%   & 37.2\% \\
+   Compr.      ratio (\%)      & 88.9    & 66.4  & 45.5   & 87.6   & 63.3   & 37.2 \\
    Average (mA)                & 2.64     & 2.79   & 3.02   & 3.10    & 3.02    & 3.13  \\
-   Saved energy              & 23.9\%    & 19.7\%  & 13.0\%  &  10.7\%   & 13.0\%   & 9.68\%\\
+   Saved energy (\%)              & 23.9    & 19.7  & 13.0  &  10.7   & 13.0   & 9.7\\
    \hline
@@
    $\epsilon$ (mg)        & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9    \\
-   Max error (mg)         & 48.8       & 9.8        & 4.9        & 48.8   &9.8    & 4.9   \\
-   Compr.      ratio & 68.6\%    & 25.5\%  & 9.5\%     & 64.4\%   & 19.8\%   & 5.7\%   \\
+   Max error (mg)         & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9   \\
+   Compr.      ratio (\%) & 68.6       & 25.5     & 9.5       & 64.4      & 19.8   & 5.7   \\
    Average (mA)        & 2.88     & 3.22   & 3.38     & 2.95    & 3.32    & 3.39   \\
-   Saved energy      & 17.0\%    & 7.18 \%   & 2.50\%   & 14.9\%   & 4.32\%   & 2.22 \%\\
+   Saved energy (\%)      & 17.0    & 7.2    & 2.5   & 14.9   & 4.3   & 2.2\\
    \hline

### 2018-10-17 paper.tex
Some fixes

@@
 
+\newpage
+
 \section{Lightweight Temporal Compression}
@@
 
-Using these notations, the original LTC algorithm can
-be written as in Algorithm~\ref{algo:ltc}. For readability, we assume
-that access to data points is blocking, i.e., the program will wait
-until the points are available. We also assume that the content of
-variable \texttt{tr} is transmitted after each assignment of this
-variable. Function \texttt{line}, omitted for brevity, returns the
-ordinate at abscissa $x$ (1st argument) of the line defined by the points
-in its 2nd and 3rd arguments.
-
 \begin{algorithm}
@@
 
- %~ is one of the linear estimation
-%~ method to compress data. It is The first-order interpolator with two
-%~ degrees of freedom (FOI-2DF) which is mentioned in
-%~ ~\cite{jalaleddine1990ecg}.  Most of linear estimation method need a
-%~ predefined parameter which is the error margin (let's call $\epsilon$)
-%~ in order to guarantee the difference between estimation and original
-%~ data within a scope.
-
-%~ \todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be written}
+Using these notations, the original LTC algorithm can
+be written as in Algorithm~\ref{algo:ltc}. For readability, we assume
+that access to data points is blocking, i.e., the program will wait
+until the points are available. We also assume that the content of
+variable \texttt{tr} is transmitted after each assignment of this
+variable. Function \texttt{line}, omitted for brevity, returns the
+ordinate at abscissa $x$ (1st argument) of the line defined by the points
+in its 2nd and 3rd arguments.
 
@@
 \label{sec:implementation}
-Our code is available at ... (make a clean release!)
 
-\todo{explain difference between exp 1 and exp 2 for euclidean}
+To implement LTC with the infinity norm, we maintain a cuboid 
+representation of $\cap_{l=1}^j{\mathcal{B}_l}$ throughout the 
+iterations of the \texttt{while} loop in 
+Algorithm~\ref{algo:general-ltc}. The implementation only requires 
+constant memory and reduced CPU time to update the cuboid with the 
+n-ball associated with the new data point at each iteration.
 
-%~ As reference above, the norm selection is importance. In this section,
-%~ we show the implementation of infinity norm and Euclidean norm.
+With the Euclidean norm, the intersection test is more complex, as 
+mentioned previously. We keep in memory a growing set $S$ of balls and 
+the bounding box $B$ of their intersection. Then, when a new point 
+arrives, we consider the associated ball $\mathcal{B}_j$ and our 
+intersection test works as in Algorithm~\ref{algo:euclidean}. 
+\texttt{box} is a function that returns the bounding box of an n-ball. 
+\texttt{find\_bisection(S, B)} searches for a point in all the elements 
+in S, using plane sweep and bisection initialized by the bounds of B.
 
-%~ \subsection{Multidimensional LTC with Manhattan distance}
-%~ In section 2, we can know that the repersentation of intersection
-%~ is a rectangular cuboid. So only one bounding box with n-dimensional
-%~ is needed to represent the intersection. Assume a bounding box
-%~ $\mathcal{BOX}_{m-1} = \bigcap_{j=1}^{m-1}{\mathcal{B}_{m-1}}$ which
-%~ has Upper bound $U_i$ and lower Bound $L_i$ for each dimension
-%~ $i$. So the fomular (1) in $6_{th}$ line of Algorithm 2 would
-%~ be changed to $\mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m} \neq \O $. The Bounding box
-%~ would be updated when this formular return true.
-%~ Otherwise return false.
-%~ \begin{enumerate}
-    %~ \item Initialization: Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$.
-    %~ \item For each data $(u_m^k, y_m^k)$ with diminsion $n$,
-            %~ defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m =
-            %~ \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
-    %~ \item The $\mathcal{B}_{m}$ should be a ractangular cube with center
-            %~ $\frac{v_1}{v_m}z_m$ and weight $\frac{v_1}{v_m}\epsilon$.
-    %~ \item For each dimension $i$, box upper bound $U_i < \frac{v_1}{v_m}x_{mi}+
-            %~ \frac{v_1}{v_m}\epsilon$ OR lower bound $L_i > \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon$, return False.
-    %~ \item Otherwise, the intersection do not be empty. Updating
-            %~ the Bounding box $\mathcal{BOX}_m = \mathcal{BOX}_{m-1} \bigcap \mathcal{B}_{m}$. For
-            %~ each dimension $i$ in $\mathcal{BOX}_m$, $U_i = min(U_i, \frac{v_1}{v_m}x_{mi}+
-            %~ \frac{v_1}{v_m}\epsilon)$, and $L_i = max(L_i , \frac{v_1}{v_m}x_{mi}-\frac{v_1}{v_m}\epsilon)$. Return True.
-%~ \end{enumerate}
+\begin{algorithm}
+\begin{algorithmic}[1]
+\Input
+   \Desc{$S$}{Set of intersecting balls}
+   \Desc{$B$}{Bounding box of the intersection of balls in $S$}
+   \Desc{$\mathcal{B}_j$}{New ball to check}
+\EndInput
+\Output
+   \Desc{$S$}{Updated set of intersecting balls}
+   \Desc{$B$}{Updated bounding box}
+   \Desc{$T$}{True if all the balls in S and $\mathcal{B}_j$ intersect}
+\EndOutput
 
-%~ According the Implement, the infinity norm boils down to apply 1D LTC algorithm in each dimension respectively.
-Since, the intersection would be rectangle in 2D and cube in 3D, the corresponding max errors are $\frac{\epsilon}{\sqrt{2}}$ and $\frac{\epsilon}{\sqrt{3}}$.
-As we mentioned in Section 2, the infinity norm is more 'tolerant' than Euclidean norm.
-The max error between original data and reconstructed data certainly not greater than $\frac{\epsilon}{\sqrt{n}}$ where $n$ is dimension of data.
+\If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \cap \mathcal{B}_i = \O$}
+\State \Return ($S$, False)
+\EndIf
+\If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \subset \mathcal{B}_i$}
+\State Remove $\mathcal{B}_i$ from $B$. Add $\mathcal{B}_j$ to $B$.
+\State \Return ($S$, $B$, True)
+\EndIf
+\If{$\mathcal{B}_j \cap B = \O$}
+\State \Return ($S$, $B$, False)
+\EndIf
+\State $B$ = box($\mathcal{B}_j$) $\ \bigcap\ $ B 
+\State $S$ = $S \ \bigcup \  \{\mathcal{B}_j\}$
+\State $x$ = find\_bisection($S$, $B$)
+\If{$x$ == Null}
+\State \Return ($S$, $B$, False)
+\Else
+\State \Return ($S$, $B$, True)
+\EndIf
+\end{algorithmic}
+\caption{Intersection test for Euclidean n-balls.}
+\label{algo:euclidean}
+\end{algorithm}
 
-%~ \todo{maybe need a graphic}
-
-%~ \subsection{Multidimensional LTC with Euclidean distance}
-%~ In Euclidea norm, the representation of intersection is
-%~ volume. There is no specific model to record repersentation
-%~ with updating, so a list to save all balls $\mathcal{B}_j, 1\leqslant{j}\leqslant{m}$
-%~ is needed. In order to test weather a set of balls intersect,
-%~ the Helly's theorem could work, but the complexity of
-%~ this method is too high to work with embeded, low-power
-%~ systems which has limited CPU and RAM resource. So we
-%~ implement Euclidean norm by using a method which based
-%~ on plane sweep and binary search.
-Assume the list of balls $S_{m-1}$ contains balls from $\mathcal{B}_1$ to $\mathcal{B}_{m-1}$, and an temporary data point $output$ used for updated origin $(\tau^k, \xi^k)$.
-From the formula (1) in Section 3, the $(\mathcal{B}_j)_{j \in \llbracket 1, {m-1} \rrbracket}$ is a sequence of decreasing radius, so the larger balls that includes new coming ball $\mathcal{B}_{m-1}$ could be reomved from list $S_{m-1}$ so that reducing processing complexity of method.
-Therefore the list $S_{m-1}$ may not includes $m-1$ balls.
-Assume each $\Hat{\mathcal{B}} \in S$ which has corresponding center $\Hat{z}$ and radius $\Hat{\epsilon}$.
-%~ Let origin $(u^k_0, y^k_0) = (\tau_k, \xi_k)$, and for each data $(u_m^k, y_m^k)$ with diminsion $n$, defines $(v_m, z_m) = (u_m^k - \tau^k, y_m^k - \xi^k)$ where $z_m = \{ x_{mi} \mid 1\leqslant{i}\leqslant{n}\}$.
-The $\mathcal{B}_{m}$ should be one n-ball with center $\frac{v_1}{v_j}z_m$ and radius $\frac{v_1}{v_j}\epsilon$.
-The method is written in Algorithm~\ref{algo:isThereIntersection}.
-
-%~ \begin{algorithm}
-    %~ \begin{flushleft}
-        %~ \textbf{Input:} $S$, $\mathcal{B}_m$, $output$ \\
-        %~ \textbf{Output:} $true|false$\\
-    %~ \end{flushleft}
-    %~ \begin{algorithmic}[1]
-        %~ \State d = n \Comment{dimension index}
-        %~ \State $max_d = \frac{v_1}{v_m}(x_d + \epsilon)$
-        %~ \State $min_d = \frac{v_1}{v_m}(x_d - \epsilon)$
-        %~ \ForAll{$\Hat{\mathcal{B}}$ \textbf{in} $S$}
-            %~ \If{$\Hat{\mathcal{B}} \bigcap \mathcal{B}_m = $ \O }
-                %~ \State \textbf{return} false
-            %~ \ElsIf{$\mathcal{B}_m \bigcap \Hat{\mathcal{B}}  = \mathcal{B}_m $}
-                %~ \State remove $\Hat{\mathcal{B}}$ from $S$
-                %~ \State \textbf{continue}\\
-            %~ $max_d = \min(max_d, \Hat{x_d} + \Hat{\epsilon}$)\\
-            %~ $min_d = \max(min_d, \Hat{x_d} - \Hat{\epsilon}$)
-            %~ \EndIf
-        %~ \EndFor
-        %~ \State $\textbf{add } \mathcal{B}_m \textbf{ into } S$
-        %~ \If{$max_d < min_d$}
-            %~ \State \textbf{return} false
-        %~ \EndIf
-        %~ \State temp\_output = output \Comment{used for next operation}
-        %~ \If{Recursive$(min_d, max_d, n, p\_cp)$}
-            %~ \State $output = temp\_output$
-            %~ \State \textbf{return} true
-        %~ \Else
-            %~ \State \textbf{return} false
-        %~ \EndIf
-    %~ \end{algorithmic}
-    %~ \caption{isThereIntersection}
-    %~ \label{algo:isThereIntersection}
-%~ \end{algorithm}
-
-%~ In the method, selecting dimension(n as default in our method) to calculate max point value and min point value of all n-balls in this dimension.
-If the max value bigger than min value, then there is no intersection.
-After that.
-In Recursive function Algorithm~\ref{algo:recursive}, using binary search select
-%~ median $mid_d$ of $max_d$ and $min_d$ in order to find bound range of dimension d-1 ($max_{d-1}$, $min_{d-1}$) over the plane $x_d = max_d$.
-If bound range of dimension $d-1$ is not empty, continue calling function \textbf{Recursive}($min_{d-1}$, $min_{d-1}$, $d-1$, $temp\_output$).
-Recursively calling this function, until getting result.
-%~ \todo{add recursive pseudo-code}
-
-%~ In 2-dimension Euclidean norm, the complexity of this algorithm is $O(n)+O(n\log\epsilon) = O(n\log\epsilon)$.
-In 3-dimension, It needs $O(\log^2\epsilon)$ to determine $mid\_3, mid\_2$, and $O(n)$ to traverse all balls in list and calculate bounding range of dimension d=1.
-So 3-dimensional method need $O(n \log^2\epsilon)$ totally.
-If we extend this idea for n-dimension, the complexiy of this method is $O(n \log^{n}\epsilon)$ where n is the number of dimension.
-
-%~ \begin{algorithm}
-    %~ \begin{flushleft}
-        %~ \textbf{function} Recursive$(left, right, j, p)$  -- $j$ means $j_th$ dimension
-    %~ \end{flushleft}
-    %~ \begin{algorithmic}[1]
-        %~ \While{$left \leqslant right$}
-            %~ \State $mid \gets (left + right)/2$
-            %~ \State $max \gets +\infty$
-            %~ \State $min \gets -\infty$
-            %~ \For{$i=1$ \textbf{to} $tmp\_list.length$}
-                %~ \State $P_1$ and $P_2$ are intersection points of $tmp\_list[i]$ and line $d_{j}=mid$, $(P1.d_{j-1}\geqslant P2.d_{j-1})$
-                %~ \If{$P_1.d_{j-1} < max$}
-                    %~ \State $max \gets p_1.d_{j-1}$
-                    %~ \State $max\_index \gets i$
-                %~ \EndIf
-                %~ \If{$P_2.d_{j-1} > min$}
-                    %~ \State $min \gets p_2.d_{j-1}$
-                    %~ \State $min\_index \gets i$
-                %~ \EndIf
-            %~ \EndFor
-            %~ \If{$max >= min$}
-                %~ \State $p.d_j \gets mid$
-                %~ \If{Recursive$(min, max, j-1, p)$}
-                    %~ \State \textbf{return} true
-                %~ \EndIf
-            %~ \EndIf
-            %~ \State Assume $P_d$ is the intersection between common chord of two objects $tmp\_list[max\_index]$, $tmp\_list[min\_index]$ and their line of centers.
-            %~ \If{$P_d.d_j < mid$}
-                %~ \State $right \gets mid-1$
-            %~ \ElsIf{$P_d.d_j > mid$}
-                %~ \State $left \gets mid+1$
-            %~ \EndIf
-
-        %~ \EndWhile
-        %~ \Return false
-    %~ \end{algorithmic}
-%~ \end{algorithm}
+Our code is available at 
+\url{https://github.com/big-data-lab-team/stream-summarization} under
+MIT license.
 
@@
 
-\todo{(Put a picture of Neblina in a box worn 
-on the wrist)}
+%\todo{(Put a picture of Neblina in a box worn 
+%on the wrist)}
 
@@
 \begin{subfigure}{2\columnwidth}
-\includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-x.pdf}
-\includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-y.pdf}
-\includegraphics[width=0.33\columnwidth]{figures/5-time-bicep-curl-plot-z.pdf}
+\includegraphics[width=0.3\columnwidth]{figures/5-time-bicep-curl-plot-x.pdf}
+\includegraphics[width=0.3\columnwidth]{figures/5-time-bicep-curl-plot-y.pdf}
+\includegraphics[width=0.3\columnwidth]{figures/5-time-bicep-curl-plot-z.pdf}
 \caption{Short biceps curl$^a$}
@@
 \begin{subfigure}{2\columnwidth}
-\includegraphics[width=0.33\columnwidth]{figures/Mohammad-bicep-curl-plot-x.pdf}
-\includegraphics[width=0.33\columnwidth]{figures/Mohammad-bicep-curl-plot-y.pdf}
-\includegraphics[width=0.33\columnwidth]{figures/Mohammad-bicep-curl-plot-z.pdf}
+\includegraphics[width=0.3\columnwidth]{figures/Mohammad-bicep-curl-plot-x.pdf}
+\includegraphics[width=0.3\columnwidth]{figures/Mohammad-bicep-curl-plot-y.pdf}
+\includegraphics[width=0.3\columnwidth]{figures/Mohammad-bicep-curl-plot-z.pdf}
 \caption{Long biceps curl}
@@
 smallest $\epsilon$, to 26.4~ms for the most complex time series and
-largest $\epsilon$.Figure~\ref{fig:memory} shows the memory consumption 
-of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear
-at the end of long compressed ranges where the signal was $\epsilon$-closed
-to the linear approximation.
+largest $\epsilon$.
+%~ Figure~\ref{fig:memory} shows the memory consumption 
+%~ of the 3D Euclidean implementation for $\epsilon$=48.8~mg: peaks appear
+%~ at the end of long compressed ranges where the signal was $\epsilon$-closed
+%~ to the linear approximation.
 
@@
 \begin{subfigure}{2\columnwidth}
-\includegraphics[width=0.33\columnwidth]{./figures/walking-1000-x.pdf}
-\includegraphics[width=0.33\columnwidth]{./figures/walking-1000-y.pdf}
-\includegraphics[width=0.33\columnwidth]{./figures/walking-1000-z.pdf}
+\includegraphics[width=0.3\columnwidth]{./figures/walking-1000-x.pdf}
+\includegraphics[width=0.3\columnwidth]{./figures/walking-1000-y.pdf}
+\includegraphics[width=0.3\columnwidth]{./figures/walking-1000-z.pdf}
 \caption{Walking}
@@
 \begin{subfigure}{2\columnwidth}
-\includegraphics[width=0.33\columnwidth]{./figures/running-1000-x.pdf}
-\includegraphics[width=0.33\columnwidth]{./figures/running-1000-y.pdf}
-\includegraphics[width=0.33\columnwidth]{./figures/running-1000-z.pdf}
+\includegraphics[width=0.3\columnwidth]{./figures/running-1000-x.pdf}
+\includegraphics[width=0.3\columnwidth]{./figures/running-1000-y.pdf}
+\includegraphics[width=0.3\columnwidth]{./figures/running-1000-z.pdf}
 \caption{Running}
@@
 
-\begin{figure}
-\includegraphics[width=\columnwidth]{./figures/memory-mohammad.pdf}
-\caption{Memory usage of 3D Euclidean implementation, long biceps curl time series, $\epsilon$=48.8~mg.}
-\label{fig:memory}
-\end{figure}
+%~ \begin{figure}
+%~ \includegraphics[width=\columnwidth]{./figures/memory-mohammad.pdf}
+%~ \caption{Memory usage of 3D Euclidean implementation, long biceps curl time series, $\epsilon$=48.8~mg.}
+%~ \label{fig:memory}
+%~ \end{figure}
 
@@
 
-We measured the energy consumption of Neblina
-for different values of $\epsilon$ and norms, to quantify the
-added-value of LTC for this system.
+%~ We measured the energy consumption of Neblina
+%~ for different values of $\epsilon$ and norms, to quantify the
+%~ added-value of LTC for this system.
 
-We acquired two 3D accelerometer time series at 200Hz corresponding to
+We acquired two 3D accelerometer time series at 200~Hz corresponding to
 common human activities: walking and running (see Figure~\ref{fig:datasets-2}). In both cases, the

### 2018-10-17 paper.tex
Now fits in 6 pages

@@
 \includegraphics[width=\columnwidth]{ltc.pdf}
-\caption{Illustration of the LTC algorithm and notations used. Blue 
+\caption{Illustration of the LTC algorithm. Blue 
 dots are received points, red dots are transmitted points. Dashed lines 
-represent the high line and the low line at times when a point is 
+represent the high and low lines when a point is 
 transmitted.\vspace*{-0.3cm}}
@@
 \end{figure}
+
 \todo{show $\xi$ in the Figure}
+\todo{Fix Omid's comment in the Figure}
 
@@
 LTC approximates the data stream
-by a piece-wise linear function of time, ensuring that the error at
-every time-point is bounded by parameter $\epsilon$.
+by a piece-wise linear function of time, with an error bounded by parameter $\epsilon$.
 
@@
 \end{equation*}
-We define $\mathcal{B}_j$ as the ball of $\mathbb{R}^n$ of center $\frac{v_1}{v_j}z_j$ and of radius
+Let $\mathcal{B}_j$ be the ball of $\mathbb{R}^n$ of center $\frac{v_1}{v_j}z_j$ and radius
 $\frac{v_1}{v_j}\epsilon$:
@@
 
-We formulate the \emph{LTC property} as follows:
+We define the \emph{LTC property} as follows:
 \begin{equation*}
@@
 is a rectangular cuboid which is straightforward to update by
-intersection with an n-ball, since the n-ball is a rectangular cuboid too.
+intersection with an n-ball.
 For the Euclidean norm, the representation is a volume with no particular property,
@@
 impact on the compression error and ratio. To appreciate this effect,
-let us consider the comparison between the infinity norm and the
+let us compare the infinity norm and the
 Euclidean norm in dimension 2. By comparing the unit disk to a
@@
 the Euclidean norm. Unsurprisingly, the
-infinity norm is more 'tolerant' than the Euclidean norm.
+infinity norm is more `tolerant' than the Euclidean norm.
 
-It should also be noted that using the infinity norm in dimension $n$ 
+It should also be noted that using the infinity norm in $\mathbb{R}^n$ 
 boils down to the use of the 1D LTC algorithm independently in each 
@@
 iterations of the \texttt{while} loop in 
-Algorithm~\ref{algo:general-ltc}. The implementation only requires 
-constant memory and reduced CPU time to update the cuboid with the 
-n-ball associated with the new data point at each iteration.
+Algorithm~\ref{algo:general-ltc}. The implementation works with
+constant memory and requires limited CPU time.
 
-With the Euclidean norm, the intersection test is more complex, as 
-mentioned previously. We keep in memory a growing set $S$ of balls and 
-the bounding box $B$ of their intersection. Then, when a new point 
-arrives, we consider the associated ball $\mathcal{B}_j$ and our 
-intersection test works as in Algorithm~\ref{algo:euclidean}. 
-\texttt{box} is a function that returns the bounding box of an n-ball. 
-\texttt{find\_bisection(S, B)} searches for a point in all the elements 
-in S, using plane sweep and bisection initialized by the bounds of B.
+With the Euclidean norm, the intersection test is more complex. We keep 
+in memory a growing set $S$ of balls and the bounding box $B$ of their 
+intersection. Then, when a new point arrives, we consider the 
+associated ball $\mathcal{B}_j$ and our intersection test works as in 
+Algorithm~\ref{algo:euclidean}. \texttt{box} is a function that returns 
+the bounding box of an n-ball. \texttt{find\_bisection(S, B)} searches 
+for a point in all the elements in S, using plane sweep and bisection 
+initialized by the bounds of B. Our code is available at 
+\url{https://github.com/big-data-lab-team/stream-summarization} under 
+MIT license.
 
@@
 
-Our code is available at 
-\url{https://github.com/big-data-lab-team/stream-summarization} under
-MIT license.
-
 \section{Experiments and Results}
@@
 
-In this experiment, we validated the behavior of our LTC extension on a 
+We validated the behavior of our LTC extension on a 
 PC using data acquired with Neblina. We collected two 3D 
@@
 smallest $\epsilon$, to 26.4~ms for the most complex time series and
-largest $\epsilon$.
+largest~$\epsilon$.
 %~ Figure~\ref{fig:memory} shows the memory consumption 
@@
 \paragraph{2D vs 3D}
-For a given $\epsilon$ of 48.8~mg and a given time series, the compression 
+For a given $\epsilon$, the compression 
 ratios are always higher in 2D than in 3D. It makes sense since the
@@
 consumes 1.4 times more memory than 2D (1.6 times on average for
-Euclidean norm), and processing time is 1.3 longer on average (1.18 on
+Euclidean norm), and processing time is 1.3 longer (1.18 on
 average for Euclidean norm).
@@
 \end{subfigure}
-\caption{Time series used in Experiment 2}
+\caption{Time series used in Experiment 2 \vspace*{-0.3cm}}
 \label{fig:datasets-2}
@@
 
-We acquired two 3D accelerometer time series at 200~Hz corresponding to
-common human activities: walking and running (see Figure~\ref{fig:datasets-2}). In both cases, the
-subject was wearing Neblina on their right wrist.
-We collected 1,000 data points for each activity, corresponding to
-5 seconds of activity.
+We acquired two 3D accelerometer time series at 200~Hz for two 
+activities: walking and running (see Figure~\ref{fig:datasets-2}). In 
+both cases, the subject was wearing Neblina on their right wrist. We 
+collected 1,000 data points for each activity, corresponding to 5 
+seconds of activity.
 
 We measured energy consumption associated with the transmission of
-these time series, for different norms and $\epsilon$ values. To do so,
-we `replayed' the time series by loading them as a byte array in
-Neblina, and we measured the current every 500~ms.
+these time series by
+`replaying' the time series after loading them as a byte array in
+Neblina. We measured the current every 500~ms.
 
@@
 \section*{Acknowledgement}
-This work was funded by a Strategic Project Grant of the Natural 
+This work was funded by the Natural 
 Sciences and Engineering Research Council of Canada. We thank Hosein 
-Nourani for providing the data used in Experiment 1.
+Nourani for providing data for Experiment 1.
 

### 2018-10-17 scripts/ltc-plot.py
Fixed notation issue noted by Omid

@@ -79,11 +79,13 @@ for i in range(2, n):
     plt.plot([trans_x, x[i-1]], [trans_y, highpoint], '--', color=(0.1, 0.1, 0.1, 0.5))
     trans_x = x[i-1]
     trans_y = (lowpoint+highpoint)/2
+    j = 1
     k = k + 1
-    j = 0
-    plot_point(trans_x, trans_y, epsilon, j, k, True)
+    plot_point(trans_x, trans_y, epsilon, 0, k, True)
     xis.append((lowpoint+highpoint)/2)
     taus.append(i-1)
+   
+
 
     # Update variables
     lowpoint = y[i] - epsilon

### 2018-10-18 paper.tex
Fixed notation issue noted by Omid
Some fixes following Bo's comments

@@
 \todo{show $\xi$ in the Figure}
-\todo{Fix Omid's comment in the Figure}
 
@@
 \State k = 0 ; j = 1
-\State (lp, hp) = ($y^1_1 - \epsilon$, $y^1_1 + \epsilon$) \Comment{low and high points}
+\State (lp, hp) = ($y^0_1 - \epsilon$, $y^0_1 + \epsilon$) \Comment{low and high points}
 
@@
     \State new\_hp = max($y^k_j+\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, hp)))
-    \If{new\_lp $<$ new\_hp} \Comment{Keep compressing}
+    \If{new\_lp $\leq$ new\_hp} \Comment{Keep compressing}
         \State (lp, hp) = (new\_lp, new\_hp)
@@
     \State k += 1
-    \State j = 0
+    \State j = 1
 \EndWhile
@@
 \EndIf
+\If{$\mathcal{B}_j \cap B = \O$}
+\State \Return ($S$, $B$, False)
+\EndIf
 \If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \subset \mathcal{B}_i$}
 \State Remove $\mathcal{B}_i$ from $B$. Add $\mathcal{B}_j$ to $B$.
-\State \Return ($S$, $B$, True)
-\EndIf
-\If{$\mathcal{B}_j \cap B = \O$}
-\State \Return ($S$, $B$, False)
 \EndIf

### 2018-10-18 paper.tex
Various fixes

@@
 
-\author{Bo Li$^1$, Omid Sarbishei$^2$, Tristan Glatard$^1$\\
+\author{Bo Li$^1$, Omid Sarbishei$^2$, Hosein Nourani$^1$, Tristan Glatard$^1$\\
   $^1$ Department of Computer Science and Software Engineering, Concordia University, Montreal, QC, Canada \\
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{ltc.pdf}
+\includegraphics[width=\columnwidth]{./figures/ltc.pdf}
 \caption{Illustration of the LTC algorithm. Blue 
@@
 \end{figure}
-
-\todo{show $\xi$ in the Figure}
 
@@
 
-\todo{Check algorithms (reimplement)}
+\todo{Check algorithms}
 
@@
 \section*{Acknowledgement}
-This work was funded by the Natural 
-Sciences and Engineering Research Council of Canada. We thank Hosein 
-Nourani for providing data for Experiment 1.
+This work was funded by a Strategic Project Grant of the Natural 
+Sciences and Engineering Research Council of Canada.
 

### 2018-10-18 scripts/ltc-plot.py

@@ -50,6 +50,7 @@ plot_point(x[1], y[1], epsilon, 1, k, False)
 
 xis = [x[0]]
 taus = [0] 
+xis = []
 for i in range(2, n):
     j += 1
 
@@ -82,10 +83,8 @@ for i in range(2, n):
     j = 1
     k = k + 1
     plot_point(trans_x, trans_y, epsilon, 0, k, True)
-    xis.append((lowpoint+highpoint)/2)
-    taus.append(i-1)
-   
-
+    taus.append(trans_x)
+    xis.append(trans_y)
 
     # Update variables
     lowpoint = y[i] - epsilon
@@ -102,7 +101,19 @@ for i in range(0, n):
 plt.xticks(range(0, n), xticks, fontsize='x-small')
 
 yticks = []
-for i in range(0, n):
-    yticks.append('$x_{}$'.format(i))
-plt.yticks(y, yticks, fontsize='x-small')
-plt.savefig('ltc.pdf', dpi=3000)
+values = sorted(y + xis)
+i = 0
+k = 1
+for v in values:
+    if v == 0:
+        yticks.append('$\\xi_0 = x_{}$'.format(i))
+        i += 1
+        continue
+    if v in y:
+        yticks.append('$x_{}$'.format(i))
+        i += 1
+    else:
+        yticks.append('$\\xi_{}$'.format(k))
+        k += 1
+plt.yticks(values, yticks, fontsize='x-small')
+plt.savefig('./figures/ltc.pdf', dpi=3000)

### 2018-10-18 paper.tex
A few fixes

@@
 compression methods that provide the highest compression rate for the 
-lowest CPU and memory consumption. As such, it is very well suited to 
+lowest CPU and memory consumption. As such, it is well suited to 
 compress data streams in energy-constrained systems such as connected 
@@
 accelerometers and gyroscopes usually measure variables along 
-3 directions related by the actual movement of the sensor. In this 
+3 directions. In this 
 paper, we investigate the extension of LTC to 
@@
 in spaces of dimension 2D+t and 3D+t. We evaluate our implementation on 
-3D acceleration streams acquired during human activities. 
+3D acceleration streams of human activities. 
 Results show that the 3D implementation of LTC can save up to 20\% in 
@@
 be launched worldwide by 2025\footnote{\url{ 
-https://www.statista.com/statistics/471264/iot-number-of-connected-devices-worldwide}} 
+https://www.statista.com/statistics/471264/iot-number-of-connected-devices-worldwide}}.
 Power consumption is amongst the biggest challenges targeting connected 
@@
 auto-regression methods~\cite{lu2010optimized} are not well-suited for 
-energy-constrained systems, due to the limited memory available on 
+connected objects, due to the limited memory available on 
 these systems (typically a few KB), and the energy consumption 
-associated with CPU usage. On such systems, compression algorithms need 
+associated with CPU usage. Instead, compression algorithms need 
 to find a trade-off between reducing network communications and 
@@
 specifically for energy-constrained systems, initially sensor networks. 
-It approximates data points by a piecewise linear function that 
+It approximates data points by a piece-wise linear function that 
 guarantees an upper bound on the reconstruction error, and a reduced 
@@
 norm-independent expression of it. We implement our extension on 
-Motsai's Neblina module, and we test it on 3D acceleration streams 
+Motsai's Neblina module\footnote{\url{ https://motsai.com/products/neblina}}, and we test it on 3D acceleration streams 
 acquired during human exercises, namely biceps curling, walking and 
@@
 Section~\ref{sec:results} reports on experiments to validate our 
-implementation, and evaluates the impact of n-dimensional LTC on 
+implementation, and evaluate the impact of n-dimensional LTC on 
 energy consumption of connected objects.
@@
 \EndOutput
-\State tr = $(u^0_0, y^0_0)$ \Comment{last transmitted point}
+\State tr = $(u^0_0, y^0_0)$ \Comment{Last transmitted point}
 \State k = 0 ; j = 1
-\State (lp, hp) = ($y^0_1 - \epsilon$, $y^0_1 + \epsilon$) \Comment{low and high points}
+\State (lp, hp) = ($y^0_1 - \epsilon$, $y^0_1 + \epsilon$) \Comment{Low and high points}
 
@@
     \EndIf
-    \State tr = $(u^k_j, (lp+hp)/2)$
+    \State tr = $(u^k_{j-1}, (lp+hp)/2)$
     \Comment{Transmit point}
@@
 $z$ such that $(v_1, z)$ is between the high line and the low line
-verify the property. Line 9 in Algorithm~\ref{algo:ltc} guarantees that
+verify the property. Line 13 in Algorithm~\ref{algo:ltc} guarantees that
 such a point exists.
@@
 
-\State tr = ($\tau, \xi$) = ($u^0_0, y^0_0$)
+\State tr = ($\tau, \xi$) = ($u^0_0, y^0_0$) \Comment{Last transmitted point}
 \State k = 0 ; j = 0
@@
     \State ($v_j, z_j$) = ($u_j^k - \tau, y_j^k - \xi$)
-    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} \neq \O$}
+    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} \neq \O$} \Comment{Keep compressing}
         \State \textbf{continue}
     \EndIf
-    \State Pick $z$ in $\bigcap_{l=1}^{j-1}{\mathcal{B}_j}$
+    \State Pick $z$ in $\bigcap_{l=1}^{j-1}{\mathcal{B}_j}$ \Comment{Transmit point}
     \State tr = ($\tau$, $\xi$) = ($u^k_{j-1}, z$)
     \State k += 1
-    \State j = 0
+    \State j = 1
 \EndWhile
 \end{algorithmic}
-\caption{Generalized LTC}
+\caption{Generalized LTC.}
 \label{algo:general-ltc}
 \end{algorithm}
-
-\todo{Check algorithms}
 
@@
 \noindent This theorem leads to an algorithm of complexity ${m \choose n+1}$ which is
-not usable in resource-constrained environment.
+not usable in resource-constrained environments.
 
@@
 the Euclidean norm. Unsurprisingly, the
-infinity norm is more `tolerant' than the Euclidean norm.
+infinity norm is more tolerant than the Euclidean norm.
 
@@
 
-To implement LTC with the infinity norm, we maintain a cuboid 
+To implement LTC in nD with the infinity norm, we maintain a cuboid 
 representation of $\cap_{l=1}^j{\mathcal{B}_l}$ throughout the 
@@
 \If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \cap \mathcal{B}_i = \O$}
-\State \Return ($S$, False)
+\State \Return ($S$, False) \Comment{Some balls don't intersect}
 \EndIf
-\If{$\mathcal{B}_j \cap B = \O$}
+\If{$\mathcal{B}_j \cap B = \O$} \Comment{Ball is outside bounding box}
 \State \Return ($S$, $B$, False) 
 \EndIf
-\If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \subset \mathcal{B}_i$}
+\If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \subset \mathcal{B}_i$} \Comment{Remove inclusions}
 \State Remove $\mathcal{B}_i$ from $B$. Add $\mathcal{B}_j$ to $B$.
 \EndIf
-\State $B$ = box($\mathcal{B}_j$) $\ \bigcap\ $ B 
+\State $B$ = box($\mathcal{B}_j$) $\ \bigcap\ $ $B$
 \State $S$ = $S \ \bigcup \  \{\mathcal{B}_j\}$
-\State $x$ = find\_bisection($S$, $B$)
+\State $x$ = find\_bisection($S$, $B$) \Comment{This can take some time}
 \If{$x$ == Null}
@@
 We conducted two experiments using Motsai's Neblina 
-module\footnote{\url{ https://motsai.com/products/neblina}}, a system 
+module, a system 
 with a Nordic Semiconductor nRF52832 micro-controller, 64~KB of RAM, 
@@
 pattern recognition~\cite{sarbishei2016accuracy}. Neblina has a 
-battery of 100mAh; its average consumption is 2.52~mA when using 
-accelerometer and gyroscope sensors at 200~Hz but without radio 
+battery of 100mAh; at 200~Hz, its average consumption is 2.52~mA when using 
+accelerometer and gyroscope sensors but without radio 
 transmission, and 3.47~mA with radio transmission, leading to an 
@@
 accelerometer time series, a short one and a longer one, acquired 
-on two different subjects performing biceps curl, with a 50Hz sampling rate (see 
+on two different subjects performing biceps curl, with a 50~Hz sampling rate (see 
 Figure~\ref{fig:datasets-1}). In both cases, the 
@@
 laptop computer with 16~GB of RAM, an Intel i5-3210M CPU @ 2.50GHz 
-× 4, and Linux Fedora 27. We measured memory consumption using 
+$\times$ 4, and Linux Fedora 27. We measured memory consumption using 
 Valgrind's massif 
@@
 \paragraph{Infinity vs Euclidean norms}
-Compared to the infinity norm, the average ratio between the compression ratios obtained
+The average ratio between the compression ratios obtained
 with the infinity and Euclidean norm is 1.08 for 2D data, and 1.20
@@
 these time series by
-`replaying' the time series after loading them as a byte array in
+``replaying" the time series after loading them as a byte array in
 Neblina. We measured the current every 500~ms.
@@
 higher for the walking activity than for running. For a realistic error
-of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm was
-close to 20\%, which is substantial.
+of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm is
+close to 20\% for the walking activity, which is substantial.
 
@@
 
-Our future work focuses on this latter issue. Our current 
-implementation of LTC with Euclidean norm relies on Helly's theorem, 
-which only provides an algorithm of complexity ${m \choose n+1}$ to 
-compress $m$ points in 
+Our future work focuses on this latter issue. We plan to start from 
+Helly's theorem, which only provides an algorithm of complexity ${m 
+\choose n+1}$ to compress $m$ points in 
 dimension $n$. We note that Helly's theorem holds for arbitrary convex 
@@
 
-The choice of an appropriate norm should not be underestimated. This problem 
-is specific to multi-dimensional streams, since all common norms are 
-identical in 1D. Some situations might be better described with the 
-Euclidean norm than with the infinity norm, such as the ones involving 
-position or movement measures. Using the infinity norm instead of the 
-Euclidean would lead to important error differences, proportional to 
-$\sqrt{n}$ in dimension $n$. A better algorithm to detect the 
-intersection of n-balls in our context would improve the efficiency of 
+The choice of an appropriate norm should not be underestimated. Some 
+situations might be better described with the Euclidean norm than with 
+the infinity norm, such as the ones involving position or movement 
+measures. Using the infinity norm instead of the Euclidean would lead 
+to important error differences, proportional to $\sqrt{n}$ in dimension 
+$n$. A better algorithm to detect the intersection of n-balls in our 
+context would improve the efficiency of 
 LTC in dimension $n$ for arbitrary norms. Investigating other norms, in 

### 2018-10-18 paper.tex
Fixed a few typos

@@
 https://www.statista.com/statistics/471264/iot-number-of-connected-devices-worldwide}}.
-Power consumption is amongst the biggest challenges targeting connected 
+Power consumption is among the biggest challenges targeting connected 
 objects, particularly in the industrial domains, where several sensing 
@@
 
-We note that the formulation of LTC in~\cite{schoellhammer2004lightweight} relies on
-the intersection of \emph{convex cones} in dimension $n+1$. For $n=1$, it
-corresponds to the intersection of triangles, which can efficiently be
-computed by maintaining boundary lines, as detailed previously. In higher dimension, however, cone intersections are not so
-straighforward, due to the fact that the intersection between cones
-may not be a cone.
+We note that the formulation of LTC 
+in~\cite{schoellhammer2004lightweight} relies on the intersection of 
+\emph{convex cones} in dimension $n+1$. For $n=1$, it corresponds to 
+the intersection of triangles, which can efficiently be computed by 
+maintaining boundary lines, as detailed previously. In higher 
+dimension, however, cone intersections are not so straightforward, due 
+to the fact that the intersection between cones may not be a cone.
 
@@
 \end{equation*}
-Let $\mathcal{B}_j$ be the ball of $\mathbb{R}^n$ of center $\frac{v_1}{v_j}z_j$ and radius
+Let $\mathcal{B}_j$ be the ball of $\mathbb{R}^n$ of centre $\frac{v_1}{v_j}z_j$ and radius
 $\frac{v_1}{v_j}\epsilon$:
@@
 
-We validated the behavior of our LTC extension on a 
-PC using data acquired with Neblina. We collected two 3D 
-accelerometer time series, a short one and a longer one, acquired 
-on two different subjects performing biceps curl, with a 50~Hz sampling rate (see 
-Figure~\ref{fig:datasets-1}). In both cases, the 
-subject was wearing Neblina on their right wrist. It should be noted that the longer dataset also has 
-a higher amplitude, most likely due to differences between subjects.
+We validated the behaviour of our LTC extension on a PC using data 
+acquired with Neblina. We collected two 3D accelerometer time-series, a 
+short one and a longer one, acquired on two different subjects 
+performing biceps curl, with a 50~Hz sampling rate (see 
+Figure~\ref{fig:datasets-1}). In both cases, the subject was wearing 
+Neblina on their right wrist. It should be noted that the longer 
+time-series also has a higher amplitude, perhaps due to differences between 
+subjects.
 
@@
 \end{subfigure}
-\caption{Time series used in Experiment 1\\
+\caption{Time-series used in Experiment 1\\
 {\footnotesize $^a$ Average of az data is -7.81g. It was shifted to 0 so that the graphs can all use the same y scale.}}
@@
 
-We compressed the time series with various values of $\epsilon$, using 
+We compressed the time-series with various values of $\epsilon$, using 
 our 2D (x and y) and 3D (x, y and z) implementations of LTC. On 
@@
 maximum measured error remains lower than $\epsilon$ in all cases. The 
-maximum is reached most of the time on these time series.
+maximum is reached most of the time on these time-series.
 
@@
 intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory
-for the Long time series in 3D with $\epsilon$=48.8~mg. More importantly,
-the amount of required memory increases for more complex time series
+for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
+the amount of required memory increases for more complex time-series
 (Long vs Short), and it also increases with larger
 values of $\epsilon$. Similar observations are made for the processing
-time, with values ranging from 0.2~ms for the simplest time series and
-smallest $\epsilon$, to 26.4~ms for the most complex time series and
+time, with values ranging from 0.2~ms for the simplest time-series and
+smallest $\epsilon$, to 26.4~ms for the most complex time-series and
 largest~$\epsilon$.
@@
 %~ \includegraphics[width=\columnwidth]{./figures/memory-mohammad.pdf}
-%~ \caption{Memory usage of 3D Euclidean implementation, long biceps curl time series, $\epsilon$=48.8~mg.}
+%~ \caption{Memory usage of 3D Euclidean implementation, long biceps curl time-series, $\epsilon$=48.8~mg.}
 %~ \label{fig:memory}
@@
 
-We acquired two 3D accelerometer time series at 200~Hz for two 
+We acquired two 3D accelerometer time-series at 200~Hz for two 
 activities: walking and running (see Figure~\ref{fig:datasets-2}). In 
@@
 We measured energy consumption associated with the transmission of
-these time series by
-``replaying" the time series after loading them as a byte array in
+these time-series by
+``replaying" the time-series after loading them as a byte array in
 Neblina. We measured the current every 500~ms.
@@
 efficient implementation of LTC with the Euclidean norm. Our current 
-idea is to search for a point expressed as a function of the ball centers that would 
+idea is to search for a point expressed as a function of the ball centres that would 
 necessarily belong to the ball intersection when it is not empty; such 
-a point, if it exists, necessarily converges to the center of the last 
+a point, if it exists, necessarily converges to the centre of the last 
 ball in the sequence as $n$ increases, as the radius of the last ball 

### 2018-10-18 paper.tex
Final touches

@@
 \usepackage{amsthm}
+\usepackage{wrapfig}
+\usepackage{multicol}
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
 
+\begin{wrapfigure}{R}{3cm}
+\includegraphics[width=3cm]{figures/neblina-wrist.png}
+\caption{Setup with Neblina.}
+\label{fig:neblina-wrist}
+\end{wrapfigure}
 We conducted two experiments using Motsai's Neblina 
@@
 Figure~\ref{fig:datasets-1}). In both cases, the subject was wearing 
-Neblina on their right wrist. It should be noted that the longer 
+Neblina on their wrist, as in Figure~\ref{fig:neblina-wrist}. It should be noted that the longer 
 time-series also has a higher amplitude, perhaps due to differences between 
@@
 
-%~ We measured the energy consumption of Neblina
-%~ for different values of $\epsilon$ and norms, to quantify the
-%~ added-value of LTC for this system.
-
 We acquired two 3D accelerometer time-series at 200~Hz for two 
 activities: walking and running (see Figure~\ref{fig:datasets-2}). In 
-both cases, the subject was wearing Neblina on their right wrist. We 
-collected 1,000 data points for each activity, corresponding to 5 
-seconds of activity.
+both cases, the subject was wearing Neblina on their wrist as in 
+Experiment 1. We collected 1,000 data points for each activity, 
+corresponding to 5 seconds of activity.
 

### 2018-10-18 paper.tex
Final final touches

@@
 \usepackage{multicol}
+\usepackage{flushend}
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
   $^1$ Department of Computer Science and Software Engineering, Concordia University, Montreal, QC, Canada \\
-  $^2$  Research and Development Department, Motsai Research, Saint Bruno, QC, Canada}
+  $^2$  Research and Development Department, Motsai Research, Saint Bruno, QC, Canada \vspace*{0.9cm}}
 \maketitle
@@
 
-\begin{figure}
+\begin{figure}[b]
 \includegraphics[width=\columnwidth]{./figures/ltc.pdf}

### 2018-11-10 paper.tex
Corrections following reviewers' comments

@@
 \usepackage{flushend}
+
+\newlength{\bibitemsep}\setlength{\bibitemsep}{.2\baselineskip plus .05\baselineskip minus .05\baselineskip}
+\newlength{\bibparskip}\setlength{\bibparskip}{1pt}
+\let\oldthebibliography\thebibliography
+\renewcommand\thebibliography[1]{%
+  \oldthebibliography{#1}%
+  \setlength{\parskip}{\bibitemsep}%
+  \setlength{\itemsep}{\bibparskip}%
+}
+
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
 
+\setlength{\textfloatsep}{0pt}
 \begin{figure}[b]
+\centering
 \includegraphics[width=\columnwidth]{./figures/ltc.pdf}
@@
     \State new\_lp = max($y^k_j-\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, lp)))
-    \State new\_hp = max($y^k_j+\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, hp)))
+    \State new\_hp = min($y^k_j+\epsilon$, line($u^k_j$, tr, ($u^k_{j-1}$, hp)))
     \If{new\_lp $\leq$ new\_hp} \Comment{Keep compressing}
         \State (lp, hp) = (new\_lp, new\_hp)
-        \State \textbf{continue}
-    \EndIf
+    \Else
         \State tr = $(u^k_{j-1}, (lp+hp)/2)$
         \Comment{Transmit point}
-    \State (lp, hp) = ($y^k_j-\epsilon$, $y^k_j+\epsilon$)
         \State k += 1
         \State j = 1
+        \State (lp, hp) = ($y^k_j-\epsilon$, $y^k_j+\epsilon$)
+    \EndIf
 \EndWhile
@@
 \end{equation*}
+Note that $v_1$ is defined as soon as one point is received after the last
+transmission.
 
@@
     \State ($v_j, z_j$) = ($u_j^k - \tau, y_j^k - \xi$)
-    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} \neq \O$} \Comment{Keep compressing}
-        \State \textbf{continue}
-    \EndIf
+    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} = \O$}
         \State Pick $z$ in $\bigcap_{l=1}^{j-1}{\mathcal{B}_j}$ \Comment{Transmit point}
@@
         \State j = 1
+    \EndIf
 \EndWhile
@@
 dimension, since a data point will be transmitted as soon as the linear 
-approximation doesn't hold in any of the dimensions.
+approximation doesn't hold in any of the dimensions. For the Euclidean 
+norm, however, the multidimensional and multiple unidimensional 
+versions are different: the multiple unidimensional version 
+behaves as the infinity norm, but the multidimensional version is more 
+stringent, leading to a reduced compression rate and error.
+
+To choose between the multidimensional implementation and multiple 
+unidimensional ones, we recommend to check whether the desired 
+error bound is expressed independently for every sensor, or as an aggregate error between them.
+The multidimensional version is
+more appropriate for multidimensional sensors, for instance 3D 
+accelerometers or 3D gyroscopes, and the multiple unidimensional 
+version to be more suitable for multiple independent sensors, for 
+instance a temperature and a pressure sensor.
+%~ For instance, in case of a 3D accelerometer, if the error 
+%~ is expressed simply as 
+%~ ``10~mg", then the multidimensional version should be chosen because it 
+%~ will guarantee that the norm of the 3D acceleration vector will be 
+%~ reconstructed with an error less than 10~mg. Conversely, if the error is 
+%~ specified as ``10~mg in x, 
+%~ 10~mg in y and 10~mg in z", then the multiple unidimensional version 
+%~ should be used.
 
@@
 To implement LTC in nD with the infinity norm, we maintain a cuboid 
-representation of $\cap_{l=1}^j{\mathcal{B}_l}$ throughout the 
+representation of $\cap_{l=1}^j{\mathcal{B}_l}$ across the 
 iterations of the \texttt{while} loop in 
@@
 
+\If{$\mathcal{B}_j \cap B = \O$} \Comment{Ball is outside bounding box}
+\State \Return ($S$, $B$, False) 
+\EndIf
 \If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \cap \mathcal{B}_i = \O$}
 \State \Return ($S$, False) \Comment{Some balls don't intersect}
-\EndIf
-\If{$\mathcal{B}_j \cap B = \O$} \Comment{Ball is outside bounding box}
-\State \Return ($S$, $B$, False) 
 \EndIf
@@
 
-\begin{wrapfigure}{R}{3cm}
-\includegraphics[width=3cm]{figures/neblina-wrist.png}
-\caption{Setup with Neblina.}
-\label{fig:neblina-wrist}
-\end{wrapfigure}
 We conducted two experiments using Motsai's Neblina 
@@
 %on the wrist)}
-
+\begin{wrapfigure}{R}{3cm}
+\includegraphics[width=3cm]{figures/neblina-wrist.png}
+\caption{Setup with Neblina.}
+\label{fig:neblina-wrist}
+\end{wrapfigure}
 We validated the behaviour of our LTC extension on a PC using data 
@@
 \begin{figure*}
-\begin{subfigure}{2\columnwidth}
+\centering
+\begin{subfigure}{1.85\columnwidth}
+\centering
 \includegraphics[width=0.3\columnwidth]{figures/5-time-bicep-curl-plot-x.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{2\columnwidth}
+
+{\footnotesize $^a$ Average 
+of az data is -7.81mg. It was shifted to 0 so that the graphs can all 
+use the same y scale.}
+
+\begin{subfigure}{1.85\columnwidth}
+\centering
 \includegraphics[width=0.3\columnwidth]{figures/Mohammad-bicep-curl-plot-x.pdf}
@@
 \end{subfigure}
-\caption{Time-series used in Experiment 1\\
-{\footnotesize $^a$ Average of az data is -7.81g. It was shifted to 0 so that the graphs can all use the same y scale.}}
+
+\caption{Time-series used in Experiment 1}
 \label{fig:datasets-1}
@@
 Valgrind's massif 
-tool~\cite{nethercote2006building}\footnote{\url{http://valgrind.org}}, 
+tool~\cite{nethercote2006building}, 
 and processing time using \texttt{gettimeofday()} from the GNU C 
@@
 for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
-the amount of required memory increases for more complex time-series
-(Long vs Short), and it also increases with larger
+the amount of required memory increases for longer time-series, and it also increases with larger
 values of $\epsilon$. Similar observations are made for the processing
@@
 \begin{figure*}
-\begin{subfigure}{2\columnwidth}
+\centering
+\begin{subfigure}{1.85\columnwidth}
+\centering
 \includegraphics[width=0.3\columnwidth]{./figures/walking-1000-x.pdf}
@@
 \end{subfigure}
-\begin{subfigure}{2\columnwidth}
+\begin{subfigure}{1.85\columnwidth}
+\centering
 \includegraphics[width=0.3\columnwidth]{./figures/running-1000-x.pdf}
@@
 
+%~ We also measured the compression latency on Neblina for this experiment.
+%~ The maximal measured latency was 7.56~ms, obtained for the Euclidean distance 
+%~ on the walk data, finish this if the correct values are avail.
+
 \section{Conclusion}
@@
 We conclude from our experiments that the proposed extension to LTC is 
-well suited to reduce energy consumption in connected objects. The implementation 
-behaves better with the infinity norm than with the Euclidean one, due 
-to the time complexity of the current algorithm to detect the intersection 
-between n-balls for the Euclidean norm.
+well suited to reduce energy consumption in connected objects. The 
+implementation behaves better with the infinity norm than with the 
+Euclidean one, due to the time complexity of the current algorithm to 
+detect the intersection between n-balls for the Euclidean norm.
 
@@
 \section*{Acknowledgement}
-This work was funded by a Strategic Project Grant of the Natural 
+This work was funded by the Natural 
 Sciences and Engineering Research Council of Canada.

### 2018-11-12 paper.tex
changle long series data set and update table1 and values in Expeirment1

--- 2018-10-18 paper.tex
@@
 \usepackage{amsthm}
-\usepackage{wrapfig}
-\usepackage{multicol}
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
 
-\author{Bo Li$^1$, Omid Sarbishei$^2$, Hosein Nourani$^1$, Tristan Glatard$^1$\\
+\author{Bo Li$^1$, Omid Sarbishei$^2$, Tristan Glatard$^1$\\
   $^1$ Department of Computer Science and Software Engineering, Concordia University, Montreal, QC, Canada \\
@@
 compression methods that provide the highest compression rate for the 
-lowest CPU and memory consumption. As such, it is well suited to 
+lowest CPU and memory consumption. As such, it is very well suited to 
 compress data streams in energy-constrained systems such as connected 
@@
 accelerometers and gyroscopes usually measure variables along 
-3 directions. In this 
+3 directions related by the actual movement of the sensor. In this 
 paper, we investigate the extension of LTC to 
@@
 in spaces of dimension 2D+t and 3D+t. We evaluate our implementation on 
-3D acceleration streams of human activities. 
+3D acceleration streams acquired during human activities. 
 Results show that the 3D implementation of LTC can save up to 20\% in 
@@
 be launched worldwide by 2025\footnote{\url{ 
-https://www.statista.com/statistics/471264/iot-number-of-connected-devices-worldwide}}.
-Power consumption is among the biggest challenges targeting connected 
+https://www.statista.com/statistics/471264/iot-number-of-connected-devices-worldwide}} 
+Power consumption is amongst the biggest challenges targeting connected 
 objects, particularly in the industrial domains, where several sensing 
@@
 auto-regression methods~\cite{lu2010optimized} are not well-suited for 
-connected objects, due to the limited memory available on 
+energy-constrained systems, due to the limited memory available on 
 these systems (typically a few KB), and the energy consumption 
-associated with CPU usage. Instead, compression algorithms need 
+associated with CPU usage. On such systems, compression algorithms need 
 to find a trade-off between reducing network communications and 
@@
 specifically for energy-constrained systems, initially sensor networks. 
-It approximates data points by a piece-wise linear function that 
+It approximates data points by a piecewise linear function that 
 guarantees an upper bound on the reconstruction error, and a reduced 
@@
 norm-independent expression of it. We implement our extension on 
-Motsai's Neblina module\footnote{\url{ https://motsai.com/products/neblina}}, and we test it on 3D acceleration streams 
+Motsai's Neblina module, and we test it on 3D acceleration streams 
 acquired during human exercises, namely biceps curling, walking and 
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{./figures/ltc.pdf}
+\includegraphics[width=\columnwidth]{ltc.pdf}
 \caption{Illustration of the LTC algorithm. Blue 
@@
 \end{figure}
+
+\todo{show $\xi$ in the Figure}
 
@@
 Section~\ref{sec:results} reports on experiments to validate our 
-implementation, and evaluate the impact of n-dimensional LTC on 
+implementation, and evaluates the impact of n-dimensional LTC on 
 energy consumption of connected objects.
@@
 \EndOutput
-\State tr = $(u^0_0, y^0_0)$ \Comment{Last transmitted point}
+\State tr = $(u^0_0, y^0_0)$ \Comment{last transmitted point}
 \State k = 0 ; j = 1
-\State (lp, hp) = ($y^0_1 - \epsilon$, $y^0_1 + \epsilon$) \Comment{Low and high points}
+\State (lp, hp) = ($y^0_1 - \epsilon$, $y^0_1 + \epsilon$) \Comment{low and high points}
 
@@
     \EndIf
-    \State tr = $(u^k_{j-1}, (lp+hp)/2)$
+    \State tr = $(u^k_j, (lp+hp)/2)$
     \Comment{Transmit point}
@@
 
-We note that the formulation of LTC 
-in~\cite{schoellhammer2004lightweight} relies on the intersection of 
-\emph{convex cones} in dimension $n+1$. For $n=1$, it corresponds to 
-the intersection of triangles, which can efficiently be computed by 
-maintaining boundary lines, as detailed previously. In higher 
-dimension, however, cone intersections are not so straightforward, due 
-to the fact that the intersection between cones may not be a cone.
+We note that the formulation of LTC in~\cite{schoellhammer2004lightweight} relies on
+the intersection of \emph{convex cones} in dimension $n+1$. For $n=1$, it
+corresponds to the intersection of triangles, which can efficiently be
+computed by maintaining boundary lines, as detailed previously. In higher dimension, however, cone intersections are not so
+straighforward, due to the fact that the intersection between cones
+may not be a cone.
 
@@
 \end{equation*}
-Let $\mathcal{B}_j$ be the ball of $\mathbb{R}^n$ of centre $\frac{v_1}{v_j}z_j$ and radius
+Let $\mathcal{B}_j$ be the ball of $\mathbb{R}^n$ of center $\frac{v_1}{v_j}z_j$ and radius
 $\frac{v_1}{v_j}\epsilon$:
@@
 $z$ such that $(v_1, z)$ is between the high line and the low line
-verify the property. Line 13 in Algorithm~\ref{algo:ltc} guarantees that
+verify the property. Line 9 in Algorithm~\ref{algo:ltc} guarantees that
 such a point exists.
@@
 
-\State tr = ($\tau, \xi$) = ($u^0_0, y^0_0$) \Comment{Last transmitted point}
+\State tr = ($\tau, \xi$) = ($u^0_0, y^0_0$)
 \State k = 0 ; j = 0
@@
     \State ($v_j, z_j$) = ($u_j^k - \tau, y_j^k - \xi$)
-    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} \neq \O$} \Comment{Keep compressing}
+    \If{$\bigcap_{l=1}^j{\mathcal{B}_l} \neq \O$}
         \State \textbf{continue}
     \EndIf
-    \State Pick $z$ in $\bigcap_{l=1}^{j-1}{\mathcal{B}_j}$ \Comment{Transmit point}
+    \State Pick $z$ in $\bigcap_{l=1}^{j-1}{\mathcal{B}_j}$
     \State tr = ($\tau$, $\xi$) = ($u^k_{j-1}, z$)
     \State k += 1
-    \State j = 1
+    \State j = 0
 \EndWhile
 \end{algorithmic}
-\caption{Generalized LTC.}
+\caption{Generalized LTC}
 \label{algo:general-ltc}
 \end{algorithm}
+
+\todo{Check algorithms (reimplement)}
 
@@
 \noindent This theorem leads to an algorithm of complexity ${m \choose n+1}$ which is
-not usable in resource-constrained environments.
+not usable in resource-constrained environment.
 
@@
 the Euclidean norm. Unsurprisingly, the
-infinity norm is more tolerant than the Euclidean norm.
+infinity norm is more `tolerant' than the Euclidean norm.
 
@@
 
-To implement LTC in nD with the infinity norm, we maintain a cuboid 
+To implement LTC with the infinity norm, we maintain a cuboid 
 representation of $\cap_{l=1}^j{\mathcal{B}_l}$ throughout the 
@@
 \If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \cap \mathcal{B}_i = \O$}
-\State \Return ($S$, False) \Comment{Some balls don't intersect}
+\State \Return ($S$, False)
 \EndIf
-\If{$\mathcal{B}_j \cap B = \O$} \Comment{Ball is outside bounding box}
+\If{$\mathcal{B}_j \cap B = \O$}
 \State \Return ($S$, $B$, False)
 \EndIf
-\If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \subset \mathcal{B}_i$} \Comment{Remove inclusions}
+\If{$\exists\ \mathcal{B}_i \in S$ s.t. $\mathcal{B}_j \subset \mathcal{B}_i$}
 \State Remove $\mathcal{B}_i$ from $B$. Add $\mathcal{B}_j$ to $B$.
 \EndIf
-\State $B$ = box($\mathcal{B}_j$) $\ \bigcap\ $ $B$
+\State $B$ = box($\mathcal{B}_j$) $\ \bigcap\ $ B 
 \State $S$ = $S \ \bigcup \  \{\mathcal{B}_j\}$
-\State $x$ = find\_bisection($S$, $B$) \Comment{This can take some time}
+\State $x$ = find\_bisection($S$, $B$)
 \If{$x$ == Null}
@@
 
-\begin{wrapfigure}{R}{3cm}
-\includegraphics[width=3cm]{figures/neblina-wrist.png}
-\caption{Setup with Neblina.}
-\label{fig:neblina-wrist}
-\end{wrapfigure}
 We conducted two experiments using Motsai's Neblina 
-module, a system 
+module\footnote{\url{ https://motsai.com/products/neblina}}, a system 
 with a Nordic Semiconductor nRF52832 micro-controller, 64~KB of RAM, 
@@
 pattern recognition~\cite{sarbishei2016accuracy}. Neblina has a 
-battery of 100mAh; at 200~Hz, its average consumption is 2.52~mA when using 
-accelerometer and gyroscope sensors but without radio 
+battery of 100mAh; its average consumption is 2.52~mA when using 
+accelerometer and gyroscope sensors at 200~Hz but without radio 
 transmission, and 3.47~mA with radio transmission, leading to an 
@@
 
-We validated the behaviour of our LTC extension on a PC using data 
-acquired with Neblina. We collected two 3D accelerometer time-series, a 
-short one and a longer one, acquired on two different subjects 
-performing biceps curl, with a 50~Hz sampling rate (see 
-Figure~\ref{fig:datasets-1}). In both cases, the subject was wearing 
-Neblina on their wrist, as in Figure~\ref{fig:neblina-wrist}. It should be noted that the longer 
-time-series also has a higher amplitude, perhaps due to differences between 
-subjects.
+We validated the behavior of our LTC extension on a 
+PC using data acquired with Neblina. We collected two 3D 
+accelerometer time series, a short one and a longer one, acquired 
+on two different subjects performing biceps curl, with a 50Hz sampling rate (see 
+Figure~\ref{fig:datasets-1}). In both cases, the 
+subject was wearing Neblina on their right wrist. It should be noted that the longer dataset also has 
+a higher amplitude, most likely due to differences between subjects.
 
@@
 \end{subfigure}
-\caption{Time-series used in Experiment 1\\
+\caption{Time series used in Experiment 1\\
 {\footnotesize $^a$ Average of az data is -7.81g. It was shifted to 0 so that the graphs can all use the same y scale.}}
@@
 
-We compressed the time-series with various values of $\epsilon$, using 
+We compressed the time series with various values of $\epsilon$, using 
 our 2D (x and y) and 3D (x, y and z) implementations of LTC. On 
@@
 laptop computer with 16~GB of RAM, an Intel i5-3210M CPU @ 2.50GHz 
-$\times$ 4, and Linux Fedora 27. We measured memory consumption using 
+× 4, and Linux Fedora 27. We measured memory consumption using 
 Valgrind's massif 
@@
 maximum measured error remains lower than $\epsilon$ in all cases. The 
-maximum is reached most of the time on these time-series.
+maximum is reached most of the time on these time series.
 
 \paragraph{Infinity vs Euclidean norms}
-The average ratio between the compression ratios obtained
+Compared to the infinity norm, the average ratio between the compression ratios obtained
 with the infinity and Euclidean norm is 1.08 for 2D data, and 1.20
@@
 infinity norm requires a constant amount of 80~B, used to store the
-intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory
-for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
-the amount of required memory increases for more complex time-series
+intersection of n-balls. The Euclidean norm, however, uses up to 4.7~KB of memory
+for the Long time series in 3D with $\epsilon$=48.8~mg. More importantly,
+the amount of required memory increases for more complex time series
 (Long vs Short), and it also increases with larger
 values of $\epsilon$. Similar observations are made for the processing
-time, with values ranging from 0.2~ms for the simplest time-series and
-smallest $\epsilon$, to 26.4~ms for the most complex time-series and
+time, with values ranging from 0.2~ms for the simplest time series and
+smallest $\epsilon$, to 41.3~ms for the most complex time series and
 largest~$\epsilon$.
@@
 consumption is higher in 3D than in 2D: for the infinity norm, 3D
-consumes 1.4 times more memory than 2D (1.6 times on average for
-Euclidean norm), and processing time is 1.3 longer (1.18 on
+consumes 1.4 times more memory than 2D (1.3 times on average for
+Euclidean norm), and processing time is 1.2 longer (1.13 on
 average for Euclidean norm).
@@
     Max error  (mg)            & 48.8        & 34.5       & 48.8        & 34.5             \\
-    Compression ratio (\%)     & 60.17       & 51.59      & 57.75       & 48.86           \\
-    Peak memory  (B)           & 80          & 80         & 2100        & 2500             \\
-    Processing time (ms)       & 5.70        & 4.85       & 20.04       & 19.28           \\ \hline
+    Compression ratio (\%)     & 77.46       & 70.98      & 75.77       & 68.81           \\
+    Peak memory  (B)           & 80          & 80         & 2512        & 2608             \\
+    Processing time (ms)       & 6.06        & 5.84       & 33.84       & 31.07           \\ \hline
     \end{tabular}
@@
     Max error  (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
-    Compression ratio (\%)         & 51.13       & 37.17      & 46.05    & 32.63   \\
-    Peak memory (B)                & 112         & 112        & 4900     & 3000    \\
-    Processing time (ms)           & 8.50        & 7.07       & 26.41    & 21.26   \\ \hline
+    Compression ratio (\%)         & 71.23       & 58.11      & 67.35    & 53.24   \\
+    Peak memory (B)                & 112         & 112        & 4752     & 3856    \\
+    Processing time (ms)           & 7.87        & 7.22       & 41.29    & 39.04   \\ \hline
     \end{tabular}
@@
 %~ \includegraphics[width=\columnwidth]{./figures/memory-mohammad.pdf}
-%~ \caption{Memory usage of 3D Euclidean implementation, long biceps curl time-series, $\epsilon$=48.8~mg.}
+%~ \caption{Memory usage of 3D Euclidean implementation, long biceps curl time series, $\epsilon$=48.8~mg.}
 %~ \label{fig:memory}
@@
 
-We acquired two 3D accelerometer time-series at 200~Hz for two 
+%~ We measured the energy consumption of Neblina
+%~ for different values of $\epsilon$ and norms, to quantify the
+%~ added-value of LTC for this system.
+
+We acquired two 3D accelerometer time series at 200~Hz for two 
 activities: walking and running (see Figure~\ref{fig:datasets-2}). In 
-both cases, the subject was wearing Neblina on their wrist as in 
-Experiment 1. We collected 1,000 data points for each activity, 
-corresponding to 5 seconds of activity.
+both cases, the subject was wearing Neblina on their right wrist. We 
+collected 1,000 data points for each activity, corresponding to 5 
+seconds of activity.
 
 We measured energy consumption associated with the transmission of
-these time-series by
-``replaying" the time-series after loading them as a byte array in
+these time series by
+`replaying' the time series after loading them as a byte array in
 Neblina. We measured the current every 500~ms.
@@
 higher for the walking activity than for running. For a realistic error
-of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm is
-close to 20\% for the walking activity, which is substantial.
+of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm was
+close to 20\%, which is substantial.
 
@@
 
-Our future work focuses on this latter issue. We plan to start from 
-Helly's theorem, which only provides an algorithm of complexity ${m 
-\choose n+1}$ to compress $m$ points in 
+Our future work focuses on this latter issue. Our current 
+implementation of LTC with Euclidean norm relies on Helly's theorem, 
+which only provides an algorithm of complexity ${m \choose n+1}$ to 
+compress $m$ points in 
 dimension $n$. We note that Helly's theorem holds for arbitrary convex 
@@
 efficient implementation of LTC with the Euclidean norm. Our current 
-idea is to search for a point expressed as a function of the ball centres that would 
+idea is to search for a point expressed as a function of the ball centers that would 
 necessarily belong to the ball intersection when it is not empty; such 
-a point, if it exists, necessarily converges to the centre of the last 
+a point, if it exists, necessarily converges to the center of the last 
 ball in the sequence as $n$ increases, as the radius of the last ball 
@@
 
-The choice of an appropriate norm should not be underestimated. Some 
-situations might be better described with the Euclidean norm than with 
-the infinity norm, such as the ones involving position or movement 
-measures. Using the infinity norm instead of the Euclidean would lead 
-to important error differences, proportional to $\sqrt{n}$ in dimension 
-$n$. A better algorithm to detect the intersection of n-balls in our 
-context would improve the efficiency of 
+The choice of an appropriate norm should not be underestimated. This problem 
+is specific to multi-dimensional streams, since all common norms are 
+identical in 1D. Some situations might be better described with the 
+Euclidean norm than with the infinity norm, such as the ones involving 
+position or movement measures. Using the infinity norm instead of the 
+Euclidean would lead to important error differences, proportional to 
+$\sqrt{n}$ in dimension $n$. A better algorithm to detect the 
+intersection of n-balls in our context would improve the efficiency of 
 LTC in dimension $n$ for arbitrary norms. Investigating other norms, in 
@@
 \section*{Acknowledgement}
-This work was funded by a Strategic Project Grant of the Natural 
-Sciences and Engineering Research Council of Canada.
+This work was funded by the Natural 
+Sciences and Engineering Research Council of Canada. We thank Hosein 
+Nourani for providing data for Experiment 1.
 

### 2018-11-12 paper.tex

--- 2018-11-10 paper.tex
@@
 infinity norm requires a constant amount of 80~B, used to store the
-intersection of n-balls. The Euclidean norm, however, uses up to 4.9~KB of memory
-for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
-the amount of required memory increases for longer time-series, and it also increases with larger
+intersection of n-balls. The Euclidean norm, however, uses up to 4.7~KB of memory
+for the Long time series in 3D with $\epsilon$=48.8~mg. More importantly,
+the amount of required memory increases for more complex time series
+(Long vs Short), and it also increases with larger
 values of $\epsilon$. Similar observations are made for the processing
-time, with values ranging from 0.2~ms for the simplest time-series and
-smallest $\epsilon$, to 26.4~ms for the most complex time-series and
+time, with values ranging from 0.2~ms for the simplest time series and
+smallest $\epsilon$, to 41.3~ms for the most complex time series and
 largest~$\epsilon$.

### 2018-11-13 paper.tex
change figure script and tex

@@
 intersection of n-balls. The Euclidean norm, however, uses up to 4.7~KB of memory
-for the Long time series in 3D with $\epsilon$=48.8~mg. More importantly,
-the amount of required memory increases for more complex time series
+for the Long time-series in 3D with $\epsilon$=48.8~mg. More importantly,
+the amount of required memory increases for more complex time-series
 (Long vs Short), and it also increases with larger
 values of $\epsilon$. Similar observations are made for the processing
-time, with values ranging from 0.2~ms for the simplest time series and
-smallest $\epsilon$, to 41.3~ms for the most complex time series and
+time, with values ranging from 0.2~ms for the simplest time-series and
+smallest $\epsilon$, to 41.3~ms for the most complex time-series and
 largest~$\epsilon$.

### 2018-11-14 paper.tex
change figure script and tex
update G range of short bicep data

@@
     $\epsilon$  (mg)          & 48.8         & 34.5       & 48.8       & 34.5 \\
-    Max error   (mg)          & 48.8         & 34.5       & 48.6       & 34.4 \\
-    Compression ratio (\%)    & 29.03        & 20.88      & 25.12      & 19.57\\
-    Peak memory   (B)         & 80           & 80         & 432        & 240  \\
-    Processing time (ms)      & 0.103        & 0.082      & 0.220s     & 0.200\\ \hline
+    Max error   (mg)          & 48.8         & 34.4       & 48.8       & 34.5 \\
+    Compression ratio (\%)    & 79.77        & 72.59      & 77.49      & 70.96\\
+    Peak memory   (B)         & 80           & 80         & 688        & 688  \\
+    Processing time (ms)      & 0.101        & 0.094      & 0.456      & 0.406\\ \hline
     \end{tabular}
@@
     $\epsilon$ (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
-    Max error  (mg)        & 48.8          & 28.0          & 48.8   & 27.8   \\
-    Compression ratio (\%) & 23.00         & 12.89         & 18.43  & 9.95   \\
-    Peak memory (B)        & 112           & 112           & 384    & 256    \\
-    Processing time (ms)   & 0.119         & 0.094         & 0.230  & 0.200  \\ \hline
+    Max error  (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
+    Compression ratio (\%) & 78.14         & 66.39         & 74.39  & 63.13   \\
+    Peak memory (B)        & 112           & 112           & 1744   & 784    \\
+    Processing time (ms)   & 0.147         & 0.134         & 0.731  & 0.514  \\ \hline
     \end{tabular}

### 2018-11-18 paper.tex
add latency table and add few sentance

@@
 The average ratio between the compression ratios obtained
-with the infinity and Euclidean norm is 1.08 for 2D data, and 1.20
+with the infinity and Euclidean norm is 1.08(1.04) for 2D data, and 1.20(1.14)
 for 3D data. These ratios are lower than the theoretical values of
@@
 values of $\epsilon$. Similar observations are made for the processing
-time, with values ranging from 0.2~ms for the simplest time-series and
+time, with values ranging from 0.2(0.4)~ms for the simplest time-series and
 smallest $\epsilon$, to 41.3~ms for the most complex time-series and
@@
 consumption is higher in 3D than in 2D: for the infinity norm, 3D
-consumes 1.4 times more memory than 2D (1.3 times on average for
-Euclidean norm), and processing time is 1.2 longer (1.13 on
+consumes 1.4 times more memory than 2D (1.3(1.8) times on average for
+Euclidean norm), and processing time is 1.2(1.4) longer (1.13(1.3) on
 average for Euclidean norm).
@@
 of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm is
-close to 20\% for the walking activity, which is substantial.
-
+close to 20\% for the walking activity, which is substantial. We also
+measured processing times of both infinity norm and Euclidean norm in
+Neblina.The result is reported in Table~\ref{table:result-latency}.
+In Neblina, the processing time of different data are similar in Infinity
+norm. In Euclidean norm, the processing time is longer, and it uses more 
+time when the data is more smooth.
 \begin{table}[]
@@
 
+\begin{table}[]
+    \begin{tabular}{l|l|l|l|l}
+    \hline
+    \rowcolor{headcolor}
+                                 & \multicolumn{2}{l}{Infinity Norm} & \multicolumn{2}{l}{Euclidean Norm} \\\hline
+    Data set                     & walking         & running         & walking          & running \\
+    Max processing Time (μs)     & 60              & 60              & 1530             & 840     \\
+    average processing Time (μs) & 30.57           & 30.040          & 144.6            & 64.34   \\       
+    \hline
+    \end{tabular}
+    \caption{Processing time from Experiment 2}
+    \label{table:result-latency}
+\end{table}
 %~ and the battery usage 

### 2018-11-20 paper.tex
some change

@@
 The average ratio between the compression ratios obtained
-with the infinity and Euclidean norm is 1.08(1.04) for 2D data, and 1.20(1.14)
+with the infinity and Euclidean norm is 1.04 for 2D data, and 1.14
 for 3D data. These ratios are lower than the theoretical values of
@@
 values of $\epsilon$. Similar observations are made for the processing
-time, with values ranging from 0.2(0.4)~ms for the simplest time-series and
+time, with values ranging from 0.4~ms for the simplest time-series and
 smallest $\epsilon$, to 41.3~ms for the most complex time-series and
@@
 consumption is higher in 3D than in 2D: for the infinity norm, 3D
-consumes 1.4 times more memory than 2D (1.3(1.8) times on average for
-Euclidean norm), and processing time is 1.2(1.4) longer (1.13(1.3) on
+consumes 1.4 times more memory than 2D (1.8 times on average for
+Euclidean norm), and processing time is 1.4 longer (1.3 on
 average for Euclidean norm).
@@
 In Neblina, the processing time of different data are similar in Infinity
-norm. In Euclidean norm, the processing time is longer, and it uses more 
-time when the data is more smooth.
+norm. In Euclidean norm, the processing time is longer, and data with slight changes using more processing time with comparing result of walking data and running data.
 \begin{table}[]

### 2018-11-21 paper.tex
Fixed the presentation of latency results

@@
     \rowcolor{headcolor}
-                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
+                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\
+    \rowcolor{headcolor}
     $\epsilon$  (mg)          & 48.8         & 34.5       & 48.8       & 34.5 \\
+    \hline
     Max error   (mg)          & 48.8         & 34.4       & 48.8       & 34.5 \\
@@
     \rowcolor{headcolor}
-                   & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
+                   & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\
+    \rowcolor{headcolor}
     $\epsilon$ (mg)            & 48.8        & 34.5       & 48.8        & 34.5    \\
+    \hline
     Max error  (mg)            & 48.8        & 34.5       & 48.8        & 34.5             \\
@@
     \rowcolor{headcolor}
-                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
+                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\
+    \rowcolor{headcolor}
     $\epsilon$ (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
+    \hline
     Max error  (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
@@
     \rowcolor{headcolor}
-                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
+                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\
+    \rowcolor{headcolor}
     $\epsilon$ (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
+    \hline
     Max error  (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
@@
 We measured energy consumption associated with the transmission of 
-these time-series by
-``replaying" the time-series after loading them as a byte array in
-Neblina. We measured the current every 500~ms.
+these time-series by ``replaying" the time-series after loading them as 
+a byte array in Neblina. We measured the current every 500~ms. We also 
+measured the max and average latency resulting from compression in the 
+data stream.
 
@@
  reduction in energy consumption behaves as the compression ratio: it 
- increases with $\epsilon$,
-it is higher for the infinity norm than for the Euclidean, and it is
-higher for the walking activity than for running. For a realistic error
-of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm is
-close to 20\% for the walking activity, which is substantial. We also
-measured processing times of both infinity norm and Euclidean norm in
-Neblina.The result is reported in Table~\ref{table:result-latency}.
-In Neblina, the processing time of different data are similar in Infinity
-norm. In Euclidean norm, the processing time is longer, and data with slight changes using more processing time with comparing result of walking data and running data.
+ increases with $\epsilon$, it is higher for the infinity norm than for 
+ the Euclidean, and it is higher for the walking activity than for 
+ running. For a realistic error of $\epsilon$=9.8~mg, the ratio of 
+ saved energy with the infinity norm is close to 20\% for the walking 
+ activity, which is substantial. Latency is higher for walking 
+ than for running, and it is also higher for the Euclidean norm than 
+ for the infinity norm. In all cases, the latency remains lower 
+ than the 5-ms tolerable latency at 200~Hz, which demonstrates the 
+ feasibility of 3D LTC compression.
+
 \begin{table}[]
@@
    \rowcolor{headcolor}
-                          & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
+                          & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\
+   \rowcolor{headcolor}
    $\epsilon$ (mg)             & 48.8    & 9.8      & 4.9   & 48.8   & 9.8   & 4.9   \\
+   \hline
    Max error (mg)              & 48.8    & 9.8      & 4.9   & 48.8   & 9.8   & 4.9   \\
@@
    Average (mA)                & 2.64    & 2.79     & 3.02  & 3.10   & 3.02  & 3.13  \\
-   Saved energy (\%)              & 23.9    & 19.7  & 13.0  &  10.7   & 13.0   & 9.7\\
+   Saved energy (\%)           & 23.9    & 19.7     & 13.0  &  10.7  & 13.0  & 9.7   \\
+   Max latency ($\mu$s)& 60      & --       & --    & 1530   & --    & --    \\
+   Average latency ($\mu$s) & 31 & --       & --    & 145    & --    & --    \\    
    \hline
@@
 
-                     & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
+                     & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\
+    \rowcolor{headcolor}
    $\epsilon$ (mg)        & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9    \\
+   \hline
    Max error (mg)         & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9   \\
@@
    Saved energy (\%)      & 17.0    & 7.2    & 2.5   & 14.9   & 4.3   & 2.2\\
+   Max latency ($\mu$s)& 60      & --       & --    & 840   & --    & --    \\
+   Average latency ($\mu$s) & 30 & --       & --    & 64    & --    & --    \\    
    \hline
@@
 \end{table}
-
-\begin{table}[]
-    \begin{tabular}{l|l|l|l|l}
-    \hline
-    \rowcolor{headcolor}
-                                 & \multicolumn{2}{l}{Infinity Norm} & \multicolumn{2}{l}{Euclidean Norm} \\\hline
-    Data set                     & walking         & running         & walking          & running \\
-    Max processing Time (μs)     & 60              & 60              & 1530             & 840     \\
-    average processing Time (μs) & 30.57           & 30.040          & 144.6            & 64.34   \\       
-    \hline
-    \end{tabular}
-    \caption{Processing time from Experiment 2}
-    \label{table:result-latency}
-\end{table}
-%~ and the battery usage 
-%~ would not change too much, because it contains others fusion method 
-%~ which will running when turning on the Neblina. In 50Hz sensor sampling 
-%~ rate, the average usage electric current for transmit accelerometer 
-%~ data is 2.0mA. It means Neblina could transmit accelerometer data 
-%~ constantly in 100/2.0=50 hours. when Neblina does not move, the average 
-%~ usage electric current using Infinity norm compression is 1.95mA.
-
- %~ It 
-%~ just extend Neblina work life about 1.28 hours. But in 200Hz sampling 
-%~ rate. The electric before and after compression are 3.5 and 2.9 
-%~ respectively. The running time of Neblina would be extended about 5.9 
-%~ hours.
-
-%~ We also measured the compression latency on Neblina for this experiment.
-%~ The maximal measured latency was 7.56~ms, obtained for the Euclidean distance 
-%~ on the walk data, finish this if the correct values are avail.
 

### 2018-11-21 paper.tex
Fixed typos

@@
 accelerometers or 3D gyroscopes, and the multiple unidimensional 
-version to be more suitable for multiple independent sensors, for 
+version is more suitable for multiple independent sensors, for 
 instance a temperature and a pressure sensor.
@@
 Figure~\ref{fig:datasets-1}). In both cases, the subject was wearing 
-Neblina on their wrist, as in Figure~\ref{fig:neblina-wrist}. It should be noted that the longer 
+Neblina on their wrist, as in Figure~\ref{fig:neblina-wrist}. It should be noted that the longest
 time-series also has a higher amplitude, perhaps due to differences between 

### 2018-11-21 paper.tex
fix numbers

--- 2018-11-20 paper.tex
@@
 The average ratio between the compression ratios obtained
-with the infinity and Euclidean norm is 1.04 for 2D data, and 1.14
+with the infinity and Euclidean norm is 1.03 for 2D data, and 1.06
 for 3D data. These ratios are lower than the theoretical values of
@@
 consumes 1.4 times more memory than 2D (1.8 times on average for
-Euclidean norm), and processing time is 1.4 longer (1.3 on
+Euclidean norm), and processing time is 1.35 longer (1.34 on
 average for Euclidean norm).

### 2018-11-21 paper.tex
Now fits in 6 pages

--- 2018-11-21 paper.tex
@@
 a byte array in Neblina. We measured the current every 500~ms. We also 
-measured the max and average latency resulting from compression in the 
-data stream.
+measured the max and average latency resulting from compression.
 
@@
 to important error differences, proportional to $\sqrt{n}$ in dimension 
-$n$. A better algorithm to detect the intersection of n-balls in our 
-context would improve the efficiency of 
-LTC in dimension $n$ for arbitrary norms. Investigating other norms, in 
+$n$. Investigating other norms, in 
 particular the 1-norm, would be relevant too.
@@
 \bibliography{IEEEabrv,biblio.bib}
+
 \end{document}
